### 2017-08-31 files/paper/paper.tex
update

%% bare_conf.tex
%% V1.4
%% 2012/12/27
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex,
%%                    bare_jrnl_transmag.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[conference]{IEEEtran}
% Add the compsoc option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/tex-archive/info/epslatex/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Do not use the stfloats baselinefloat ability as IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{UGAN: whatever}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Cameron Fabbri}
\IEEEauthorblockA{Information Directorate\\
Air Force Research Laboratory \\
Rome, NY, USA.\\
cameron.fabbri@us.af.mil}
\and
\IEEEauthorblockN{Md Jahidul Muslim}
\IEEEauthorblockA{UMN\\}
\and
\IEEEauthorblockN{Junaed Sattar}
\IEEEauthorblockA{UMN\\
}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Autonomous underwater robots often rely on visual input for decision making. However, due to many factors such as light refraction and
particles in the water, images are often times very noisy. We propose a method using Generative Adversarial Networks (GANs) to denoise
underwater images, and show that these images provide both increased accuracy for an underwater tracking algorithm, as well as a more
visually appealing image.
\end{abstract}

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% no \IEEEPARstart

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

\section{Related Work}

\section{Technical Approach}

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results.}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals/conferences use top floats
% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
% command of the stfloats package.

\section{Conclusion}
The conclusion goes here.

% conference papers do not normally have an appendix

% use section* for acknowledgement
\section*{Acknowledgment}

The authors would like to thank...

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% that's all folks
\end{document}

### 2017-08-31 datasets/underwater_imagenet/count_splits.py
update

@@ -1,0 +1,15 @@
+import glob
+import ntpath
+
+images = glob.glob('test/*.jpg')
+
+classes = []
+
+for i in images:
+   i = ntpath.basename(i).split('.')[0].split('_')[0]
+   classes.append(i)
+
+
+print set(classes)
+
+

### 2017-08-31 delete_gray.py

@@ -14,6 +14,6 @@ for d, s, fList in os.walk(img_dir):
          img = misc.imread(p)
 
          if len(img.shape) < 3:
-            os.remove(p)
+            #os.remove(p)
             print 'deleted',p
 

### 2017-08-31 inception_score.py

@@ -1,0 +1,146 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import tensorflow as tf
+import os.path
+import sys
+import tarfile
+
+import numpy as np
+from six.moves import urllib
+import tensorflow as tf
+import glob
+import scipy.misc
+import math
+import sys
+import scipy.misc as misc
+
+MODEL_DIR = '/tmp/imagenet'
+DATA_URL = 'http://download.tensorflow.org/models/image/imagenet/inception-2015-12-05.tgz'
+softmax = None
+
+
+
+# Call this function with list of images. Each of elements should be a 
+# numpy array with values ranging from 0 to 255.
+def get_inception_score(images, splits=7):
+   assert(type(images) == list)
+   assert(type(images[0]) == np.ndarray)
+   assert(len(images[0].shape) == 3)
+   assert(np.max(images[0]) > 10)
+   assert(np.min(images[0]) >= 0.0)
+   inps = []
+   for img in images:
+      img = img.astype(np.float32)
+      inps.append(np.expand_dims(img, 0))
+   bs = 100
+   with tf.Session() as sess:
+      preds = []
+      n_batches = int(math.ceil(float(len(inps)) / float(bs)))
+      for i in range(n_batches):
+         sys.stdout.write(".")
+         sys.stdout.flush()
+         inp = inps[(i * bs):min((i + 1) * bs, len(inps))]
+         #print(np.asarray(inp).shape)
+         inp = np.concatenate(inp, 0)
+         pred = sess.run(softmax, {'ExpandDims:0': inp})
+         preds.append(pred)
+      preds = np.concatenate(preds, 0)
+      scores = []
+      for i in range(splits):
+         part = preds[(i * preds.shape[0] // splits):((i + 1) * preds.shape[0] // splits), :]
+         kl = part * (np.log(part) - np.log(np.expand_dims(np.mean(part, 0), 0)))
+         kl = np.mean(np.sum(kl, 1))
+         scores.append(np.exp(kl))
+      return np.mean(scores), np.std(scores)
+
+
+
+# This function is called automatically.
+def _init_inception():
+  global softmax
+  if not os.path.exists(MODEL_DIR):
+    os.makedirs(MODEL_DIR)
+  filename = DATA_URL.split('/')[-1]
+  filepath = os.path.join(MODEL_DIR, filename)
[…]

### 2017-09-05 files/paper/paper.tex
update

@@
 % Do not put math or special symbols in the title.
-\title{UGAN: whatever}
+\title{UGAN: Underwater Image Restoration with Generative Adversarial Networks}
 
@@
 
-% no keywords
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
 \IEEEpeerreviewmaketitle
@@
 \section{Introduction}
-% no \IEEEPARstart
-
-\subsection{Subsection Heading Here}
-Subsection text here.
-
-\subsubsection{Subsubsection Heading Here}
-Subsubsection text here.
+Many autonomous underwater robots rely on visual input for decision making due to the nonintrusive, passive, and energy effecient nature of vision.
+Despite these advantages, many underwater environments can be quite noisy due to light refraction, blueish hue, and particles present in the water.
 
@@
 \section{Technical Approach}
+
+\subsection{Subsection Heading Here}
+
+\subsubsection{Subsubsection Heading Here}
+Subsubsection text here.
 
@@
 
-% Note that IEEE does not put floats in the very first column - or typically
-% anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals/conferences use top floats
-% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
-% command of the stfloats package.
-
 \section{Conclusion}
@@
 
-% conference papers do not normally have an appendix
-
-% use section* for acknowledgement
 \section*{Acknowledgment}
 
-The authors would like to thank...
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
 \begin{thebibliography}{1}
-
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+\bibitem{hires}{Johnson‐Roberson, Matthew, et al.
+"High‐Resolution Underwater Robotic Vision‐Based Mapping and Three‐Dimensional Reconstruction for Archaeology." Journal of Field Robotics 34.4 (2017): 625-643.}
 

### 2017-09-05 files/paper/paper.tex
update

@@
 % Do not put math or special symbols in the title.
-\title{UGAN: Underwater Image Restoration with Generative Adversarial Networks}
+\title{UGAN: Underwater Image Restoration using Generative Adversarial Networks}
 
@@
 \begin{abstract}
-Autonomous underwater robots often rely on visual input for decision making. However, due to many factors such as light refraction and
-particles in the water, images are often times very noisy. We propose a method using Generative Adversarial Networks (GANs) to denoise
-underwater images, and show that these images provide both increased accuracy for an underwater tracking algorithm, as well as a more
-visually appealing image.
+Autonomous underwater robots often rely on visual input for decision making due to its non-intrusive and passive nature
+.
+However, due to many factors such as light refraction, particles in the water, and color distortion, images are often times very noisy.
+This paper propose a method using Generative Adversarial Networks (GANs) to denoise underwater images, and show that these images provide both increased accuracy
+for an underwater tracking algorithm, as well as a more visually appealing image. Furthermore, we show how recently
+proposed methods are able to generate a dataset for the purpose of underwater image reconstruction.
 \end{abstract}
@@
 \section{Introduction}
-Many autonomous underwater robots rely on visual input for decision making due to the nonintrusive, passive, and energy effecient nature of vision.
-Despite these advantages, many underwater environments can be quite noisy due to light refraction, blueish hue, and particles present in the water.
+Vision is a commonly used sensor in autonomous underwater robots due to its non-intrusive, passive, and energy
+effecient nature. Despite these advantages, many underwater environments can be quite noisy due to light
+refraction, blue or green hues, and particles present in the water. Much of this noise comes from color distortion,
+where images have green or blue haze which may cause difficulty in tasks such as segmentation, tracking, or
+classification. Algorithms that have been shown to work well on images not underwater may fail due to their
+indirect or direct use of color. While there have been many very successful recent approaches towards colorization
+\cite{col1,col2,col3,pix2pix}, all are focused on the task of grayscale to color.
 
@@
 
-\section{Technical Approach}
+\section{Method}
 
-\subsection{Subsection Heading Here}
+\subsection{Generative Adversarial Networks}
 
-\subsubsection{Subsubsection Heading Here}
-Subsubsection text here.
+\subsection{Objective}
 
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation Results.}
-%\label{fig_sim}
-%\end{figure}
+\subsection{Network Architectures}
 
-% Note that IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
+\subsubsection{Generator}
 
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-
-% An example of a floating table. Note that, for IEEE style tables, the 
-% \caption command should come BEFORE the table. Table text will default to
-% \footnotesize as IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
+\subsubsection{Discriminator}
 
 \section{Conclusion}
-The conclusion goes here.
 
@@
 
+\bibitem{col1}{Zhang, Richard, Phillip Isola, and Alexei A. Efros. "Colorful image colorization." European Conference on Computer Vision. Springer International Publishing, 2016.}
+
+\bibitem{col2}{Cheng, Zezhou, Qingxiong Yang, and Bin Sheng. "Deep colorization." Proceedings of the IEEE International Conference on Computer Vision. 2015.}
+
+\bibitem{col3}{Iizuka, Satoshi, Edgar Simo-Serra, and Hiroshi Ishikawa.
+"Let there be color!: joint end-to-end learning of global and local image priors for automatic image colorization with simultaneous classification." ACM Transactions on Graphics (TOG) 35.4 (2016): 110.}
+
+\bibitem{pix2pix}{Isola, Phillip, et al. "Image-to-image translation with conditional adversarial networks." arXiv preprint arXiv:1611.07004 (2016).}
+
+\bibitem{watergan}{Li, Jie, et al. "WaterGAN: Unsupervised Generative Network to Enable Real-time Color Correction of Monocular Underwater Images." arXiv preprint arXiv:1702.07392 (2017).}
+
 \end{thebibliography}

### 2017-09-05 temp.py

@@ -3,7 +3,7 @@ from shutil import move
 import os
 import glob
 
-
+exit()
 test = glob.glob('testB/*.jpg')
 
 for t in test:

### 2017-09-05 files/paper/paper.tex
update

@@
 
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
-% not currently provide for hyperlinked citations.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/tex-archive/info/epslatex/
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-%\usepackage[cmex10]{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Do not use the stfloats baselinefloat ability as IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/
-
 % *** PDF, URL AND HYPERLINK PACKAGES ***
 %
-%\usepackage{url}
+\usepackage{url}
 % url.sty was written by Donald Arseneau. It provides better support for
@@
 
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
 % correct bad hyphenation here
@@
 \begin{document}
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
-% Do not put math or special symbols in the title.
+
 \title{UGAN: Underwater Image Restoration using Generative Adversarial Networks}
 
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
 \author{\IEEEauthorblockN{Cameron Fabbri}
@@
 }}
-
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
 
@@
 %\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
 
@@
 indirect or direct use of color. While there have been many very successful recent approaches towards colorization
-\cite{col1,col2,col3,pix2pix}, all are focused on the task of grayscale to color.
+\cite{bao2017cvae}, all are focused on the task of grayscale to color.
 
@@
 
-\begin{thebibliography}{1}
-\bibitem{hires}{Johnson‐Roberson, Matthew, et al.
+%
+%\begin{thebibliography}{1}
+%\bibitem{hires}{Johnson‐Roberson, Matthew, et al.
 "High‐Resolution Underwater Robotic Vision‐Based Mapping and Three‐Dimensional Reconstruction for Archaeology." Journal of Field Robotics 34.4 (2017): 625-643.}
+%
+%\bibitem{col1}{Zhang, Richard, Phillip Isola, and Alexei A. Efros. "Colorful image colorization." European Conference on Computer Vision. Springer International Publishing, 2016.}
 
-\bibitem{col1}{Zhang, Richard, Phillip Isola, and Alexei A. Efros. "Colorful image colorization." European Conference on Computer Vision. Springer International Publishing, 2016.}
+%\bibitem{col2}{Cheng, Zezhou, Qingxiong Yang, and Bin Sheng. "Deep colorization." Proceedings of the IEEE International Conference on Computer Vision. 2015.}
 
-\bibitem{col2}{Cheng, Zezhou, Qingxiong Yang, and Bin Sheng. "Deep colorization." Proceedings of the IEEE International Conference on Computer Vision. 2015.}
-
-\bibitem{col3}{Iizuka, Satoshi, Edgar Simo-Serra, and Hiroshi Ishikawa.
+%\bibitem{col3}{Iizuka, Satoshi, Edgar Simo-Serra, and Hiroshi Ishikawa.
 "Let there be color!: joint end-to-end learning of global and local image priors for automatic image colorization with simultaneous classification." ACM Transactions on Graphics (TOG) 35.4 (2016): 110.}
 
-\bibitem{pix2pix}{Isola, Phillip, et al. "Image-to-image translation with conditional adversarial networks." arXiv preprint arXiv:1611.07004 (2016).}
+%\bibitem{pix2pix}{Isola, Phillip, et al. "Image-to-image translation with conditional adversarial networks." arXiv preprint arXiv:1611.07004 (2016).}
 
-\bibitem{watergan}{Li, Jie, et al. "WaterGAN: Unsupervised Generative Network to Enable Real-time Color Correction of Monocular Underwater Images." arXiv preprint arXiv:1702.07392 (2017).}
+%\bibitem{watergan}{Li, Jie, et al. "WaterGAN: Unsupervised Generative Network to Enable Real-time Color Correction of Monocular Underwater Images." arXiv preprint arXiv:1702.07392 (2017).}
 
-\end{thebibliography}
+%\end{thebibliography}
+
+%\bibliography{/home/fabbric/Research/colorCorrection/files/paper/cambibs}
+\bibliography{cambibs}
+\bibliographystyle{ieeetr}
 

### 2017-09-05 files/paper/_compile.sh

@@ -1,0 +1,4 @@
+rm paper.aux paper.b* paper.log
+pdflatex paper.tex
+bibtex paper.aux
+pdflatex paper.tex

### 2017-09-06 files/paper/paper.tex
update

@@
 
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
+\documentclass[conference]{IEEEtran}
 
-% Note that the a4paper option is mainly intended so that authors in
-% countries using A4 can easily print to A4 and see how their papers will
-% look in print - the typesetting of the document will not typically be
-% affected with changes in paper size (but the bottom and side margins will).
-% Use the testflow package mentioned above to verify correct handling of
-% both paper sizes by the user's LaTeX system.
-%
-% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
-% should be used if it is desired that the figures are to be displayed in
-% draft mode.
-%
-\documentclass[conference]{IEEEtran}
-% Add the compsoc option for Computer Society conferences.
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
+\usepackage{graphicx}
+\graphicspath{{images/}}
 
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
 \usepackage{url}
@@
 Vision is a commonly used sensor in autonomous underwater robots due to its non-intrusive, passive, and energy
-effecient nature. Despite these advantages, many underwater environments can be quite noisy due to light
-refraction, blue or green hues, and particles present in the water. Much of this noise comes from color distortion,
-where images have green or blue haze which may cause difficulty in tasks such as segmentation, tracking, or
-classification. Algorithms that have been shown to work well on images not underwater may fail due to their
-indirect or direct use of color. While there have been many very successful recent approaches towards colorization
-\cite{bao2017cvae}, all are focused on the task of grayscale to color.
+effecient nature. The monitoring of coral reefs \cite{shkurti2012multi}, deep ocean exploration
+\cite{whitcomb2000advances}, and mapping of the seabed are all tasks suitable for autonomous robots because they
+provide safety by taking the risk instead of a human. Despite the advantages vision provides, many underwater
+environments can be quite noisy due to light refraction and particles present in the water. Because red wavelengths are
+quickly absorbed by water, images tend to have a green or blue hue to them. As you go deeper, this worsens as more
+and more red wavelengths are being absorbed. This extremely non-linear distortion has many factors such as the amount
+of light present (overcast vs sunny or depth), particles in the water, time of day, and the camera being used. This may
+cause difficulty in tasks such as segmentation, tracking, or classification due to their indirect or direct use of
+color.
+
+As color and illumination begin to change with the depth, vision based algorithms must be very generalizable in order
+to work within the depth ranges a robot may operate in. Because of the high cost and difficulty of acquiring a
+variety of underwater data, as well as the high amount of noise introduced, many algorithms may perform poorly in
+these different domains. Figure 1 shows the high variability that may occur in underwater vision. A step towards a
+solution to this
+issue is to be able to restore the images such that they appear to be above water, i.e., with colors corrected and
+particles removed. By performing a many to one mapping of these domains from underwater to not underwater (what the
+image would look like in the air), algorithms that have
+
+\begin{figure}[!htb]
+   \begin{center}$
+      \begin{array}{cccc}
+         \includegraphics[width=3in]{figure1}
+      \end{array}$
+   \end{center}
+   \caption{Underwater images showing the vast divesity of noise that can occur, including
+   different hues of green and blue, as well as particles in the water.}
+\end{figure}
+
+\noindent difficulty performing across multiple forms of noise may be able to focus only one clean domain.
+
+Deep neural networks have been shown to be powerful non-linear function approximators, especially in the field of
+vision. Often times, these networks recquire large amounts of data, either labeled or paired with ground truth.
+For the problem of automatically colorizing grayscale images, paired training data is essentially free due to the
+fact that any color image can be converted to black and white. However, underwater images distorted by either color
+or some other visual effect lack ground truth. We use the recently proposed CycleGAN \cite{zhu2017unpaired}, which
+learns to translate an image from domain $X$ to domain $Y$, as a way to generate a paired dataset. By letting $X$ be
+a set of undistorted underwater images, and $Y$ be a set of distorted underwater images, we can generate an image
+that appears to be underwater while retaining ground truth.
 
@@
 
+While there have been many very successful recent approaches towards colorization
+\cite{zhang2016colorful,iizuka2016let}, all are focused on the task of grayscale to color. Color correction and image
+restoration for the underwater domain has been less explored. The work of \cite{torres2005color} used an energy
+minimization formulation using a Markov Random Field.
+
 \section{Method}
+Recent work in generative models, specifically Generative Adversarial
+Networks (GANs), have shown great success in areas such as inpainting \cite{pathak2016context}, style transfer
+\cite{Gatys_2016_CVPR}, and image-to-image translation \cite{isola2016image,zhu2017unpaired}. This is highly due to
+their ability to provide a more meaningful loss than simply the Euclidean distance, which has been shown to produce
+blurry results.
 

### 2017-09-07 _train.sh
update

@@ -1,1 +1,1 @@
-python train.py --DATA=rocks --EPOCHS=100 --NETWORK=pix2pix --IG_WEIGHT=1.0 --L1_WEIGHT=100.0 --BATCH_SIZE=16 --LOSS_METHOD=wgan --LEARNING_RATE=1e-4
+python train.py --DATA=rocks --EPOCHS=1000 --NETWORK=pix2pix --IG_WEIGHT=1.0 --L1_WEIGHT=100.0 --BATCH_SIZE=16 --LOSS_METHOD=wgan --LEARNING_RATE=1e-4

### 2017-09-07 augmented_train.py

@@ -1,0 +1,285 @@
+'''
+
+   Main training file
+
+   The goal is to correct the colors in underwater images.
+   CycleGAN was used to create images that appear to be underwater.
+   Those will be sent into the generator, which will attempt to correct the
+   colors.
+
+'''
+
+import cPickle as pickle
+import tensorflow as tf
+from tqdm import tqdm
+from scipy import misc
+import numpy as np
+import argparse
+import ntpath
+import sys
+import os
+import time
+import glob
+import random
+
+sys.path.insert(0, 'ops/')
+sys.path.insert(0, 'nets/')
+from tf_ops import *
+
+import data_ops
+
+if __name__ == '__main__':
+   parser = argparse.ArgumentParser()
+   parser.add_argument('--PixS',          required=False,default=0,type=int,help='Pixel shuffle')
+   parser.add_argument('--DATA',          required=False,default='underwater_imagenet',type=str,help='Dataset to use')
+   parser.add_argument('--EPOCHS',        required=False,default=1000,type=int,help='Number of epochs for GAN')
+   parser.add_argument('--NETWORK',       required=False,default='pix2pix',type=str,help='Network to use')
+   parser.add_argument('--L1_WEIGHT',     required=False,default=100.,type=float,help='Weight for L1 loss')
+   parser.add_argument('--IG_WEIGHT',     required=False,default=1.,type=float,help='Weight for image gradient loss')
+   parser.add_argument('--BATCH_SIZE',    required=False,default=32,type=int,help='Batch size')
+   parser.add_argument('--LOSS_METHOD',   required=False,default='wgan',help='Loss function for GAN')
+   parser.add_argument('--LEARNING_RATE', required=False,default=1e-4,type=float,help='Learning rate')
+   a = parser.parse_args()
+
+   LEARNING_RATE = float(a.LEARNING_RATE)
+   LOSS_METHOD   = a.LOSS_METHOD
+   BATCH_SIZE    = a.BATCH_SIZE
+   L1_WEIGHT     = float(a.L1_WEIGHT)
+   IG_WEIGHT     = float(a.IG_WEIGHT)
+   NETWORK       = a.NETWORK
+   EPOCHS        = a.EPOCHS
[…]

### 2017-09-07 tests/stats.py

@@ -1,0 +1,36 @@
+import scipy.misc as misc
+import math
+import numpy as np
+
+# our image
+image1 = misc.imread('files/paper/images/n01496331_11938_gen_IG_0.0.png').astype('float32')
+image1 = image1/255.0
+
+#cyclegan image
+image2 = misc.imread('files/paper/images/n01496331_11938.png').astype('float32')
+image2 = image2/255.0
+
+# real image
+image3 = misc.imread('files/paper/images/n01496331_11938_real.png').astype('float32')
+image3 = image3/255.0
+
+img1 = image1[50:150, :100, :]
+img2 = image2[50:150, :100, :]
+img3 = image3[50:150, :100, :]
+
+misc.imsave('original.png', image1)
+misc.imsave('ours.png', img1)
+misc.imsave('theirs.png', img2)
+misc.imsave('real.png', img3)
+
+print 'Variance'
+print 'ours:     ',np.var(img1)
+print 'cyclegan: ',np.var(img2)
+print 'real:     ',np.var(img3)
+print
+print 'Mean'
+print 'ours:     ',np.mean(img1)
+print 'cyclegan: ',np.mean(img2)
+print 'real:     ',np.mean(img3)
+
+

### 2017-09-07 utils/delete_gray.py

@@ -1,0 +1,19 @@
+import scipy.misc as misc
+import os
+import fnmatch
+
+img_dir = 'datasets/'
+
+pattern   = '*.jpg'
+image_paths = []
+for d, s, fList in os.walk(img_dir):
+   for filename in fList:
+      if fnmatch.fnmatch(filename, pattern):
+         p = os.path.join(d, filename)
+
+         img = misc.imread(p)
+
+         if len(img.shape) < 3:
+            #os.remove(p)
+            print 'deleted',p
+

### 2017-09-07 utils/temp.py

@@ -1,0 +1,18 @@
+from shutil import move
+
+import os
+import glob
+
+exit()
+test = glob.glob('testB/*.jpg')
+
+for t in test:
+
+   t = t.replace('test','train')
+   os.remove(t)
+   #t = t.split('/')[-1]
+
+   #src  = 'trainB/'+t
+   #dest = 'testB/'+t
+
+   #move(src, dest)

### 2017-09-07 augemented_train.py
updates

@@ -1,285 +1,0 @@
-'''
-
-   Main training file
-
-   The goal is to correct the colors in underwater images.
-   CycleGAN was used to create images that appear to be underwater.
-   Those will be sent into the generator, which will attempt to correct the
-   colors.
-
-'''
-
-import cPickle as pickle
-import tensorflow as tf
-from tqdm import tqdm
-from scipy import misc
-import numpy as np
-import argparse
-import ntpath
-import sys
-import os
-import time
-import glob
-import random
-
-sys.path.insert(0, 'ops/')
-sys.path.insert(0, 'nets/')
-from tf_ops import *
-
-import data_ops
-
-if __name__ == '__main__':
-   parser = argparse.ArgumentParser()
-   parser.add_argument('--PixS',          required=False,default=0,type=int,help='Pixel shuffle')
-   parser.add_argument('--DATA',          required=False,default='underwater_imagenet',type=str,help='Dataset to use')
-   parser.add_argument('--EPOCHS',        required=False,default=1000,type=int,help='Number of epochs for GAN')
-   parser.add_argument('--NETWORK',       required=False,default='pix2pix',type=str,help='Network to use')
-   parser.add_argument('--L1_WEIGHT',     required=False,default=100.,type=float,help='Weight for L1 loss')
-   parser.add_argument('--IG_WEIGHT',     required=False,default=1.,type=float,help='Weight for image gradient loss')
-   parser.add_argument('--BATCH_SIZE',    required=False,default=32,type=int,help='Batch size')
-   parser.add_argument('--LOSS_METHOD',   required=False,default='wgan',help='Loss function for GAN')
-   parser.add_argument('--LEARNING_RATE', required=False,default=1e-4,type=float,help='Learning rate')
-   a = parser.parse_args()
-
-   LEARNING_RATE = float(a.LEARNING_RATE)
-   LOSS_METHOD   = a.LOSS_METHOD
-   BATCH_SIZE    = a.BATCH_SIZE
-   L1_WEIGHT     = float(a.L1_WEIGHT)
-   IG_WEIGHT     = float(a.IG_WEIGHT)
-   NETWORK       = a.NETWORK
-   EPOCHS        = a.EPOCHS
[…]

### 2017-09-07 delete_gray.py
updates

@@ -1,19 +1,0 @@
-import scipy.misc as misc
-import os
-import fnmatch
-
-img_dir = 'datasets/'
-
-pattern   = '*.jpg'
-image_paths = []
-for d, s, fList in os.walk(img_dir):
-   for filename in fList:
-      if fnmatch.fnmatch(filename, pattern):
-         p = os.path.join(d, filename)
-
-         img = misc.imread(p)
-
-         if len(img.shape) < 3:
-            #os.remove(p)
-            print 'deleted',p
-

### 2017-09-07 inception_score.py

@@ -1,146 +1,0 @@
-from __future__ import absolute_import
-from __future__ import division
-from __future__ import print_function
-
-import tensorflow as tf
-import os.path
-import sys
-import tarfile
-
-import numpy as np
-from six.moves import urllib
-import tensorflow as tf
-import glob
-import scipy.misc
-import math
-import sys
-import scipy.misc as misc
-
-MODEL_DIR = '/tmp/imagenet'
-DATA_URL = 'http://download.tensorflow.org/models/image/imagenet/inception-2015-12-05.tgz'
-softmax = None
-
-
-
-# Call this function with list of images. Each of elements should be a 
-# numpy array with values ranging from 0 to 255.
-def get_inception_score(images, splits=7):
-   assert(type(images) == list)
-   assert(type(images[0]) == np.ndarray)
-   assert(len(images[0].shape) == 3)
-   assert(np.max(images[0]) > 10)
-   assert(np.min(images[0]) >= 0.0)
-   inps = []
-   for img in images:
-      img = img.astype(np.float32)
-      inps.append(np.expand_dims(img, 0))
-   bs = 100
-   with tf.Session() as sess:
-      preds = []
-      n_batches = int(math.ceil(float(len(inps)) / float(bs)))
-      for i in range(n_batches):
-         sys.stdout.write(".")
-         sys.stdout.flush()
-         inp = inps[(i * bs):min((i + 1) * bs, len(inps))]
-         #print(np.asarray(inp).shape)
-         inp = np.concatenate(inp, 0)
-         pred = sess.run(softmax, {'ExpandDims:0': inp})
-         preds.append(pred)
-      preds = np.concatenate(preds, 0)
-      scores = []
-      for i in range(splits):
-         part = preds[(i * preds.shape[0] // splits):((i + 1) * preds.shape[0] // splits), :]
-         kl = part * (np.log(part) - np.log(np.expand_dims(np.mean(part, 0), 0)))
-         kl = np.mean(np.sum(kl, 1))
-         scores.append(np.exp(kl))
-      return np.mean(scores), np.std(scores)
-
-
-
-# This function is called automatically.
-def _init_inception():
-  global softmax
-  if not os.path.exists(MODEL_DIR):
-    os.makedirs(MODEL_DIR)
-  filename = DATA_URL.split('/')[-1]
-  filepath = os.path.join(MODEL_DIR, filename)
[…]

### 2017-09-07 stats.py

@@ -1,36 +1,0 @@
-import scipy.misc as misc
-import math
-import numpy as np
-
-# our image
-image1 = misc.imread('files/paper/images/n01496331_11938_gen_IG_0.0.png').astype('float32')
-image1 = image1/255.0
-
-#cyclegan image
-image2 = misc.imread('files/paper/images/n01496331_11938.png').astype('float32')
-image2 = image2/255.0
-
-# real image
-image3 = misc.imread('files/paper/images/n01496331_11938_real.png').astype('float32')
-image3 = image3/255.0
-
-img1 = image1[50:150, :100, :]
-img2 = image2[50:150, :100, :]
-img3 = image3[50:150, :100, :]
-
-misc.imsave('original.png', image1)
-misc.imsave('ours.png', img1)
-misc.imsave('theirs.png', img2)
-misc.imsave('real.png', img3)
-
-print 'Variance'
-print 'ours:     ',np.var(img1)
-print 'cyclegan: ',np.var(img2)
-print 'real:     ',np.var(img3)
-print
-print 'Mean'
-print 'ours:     ',np.mean(img1)
-print 'cyclegan: ',np.mean(img2)
-print 'real:     ',np.mean(img3)
-
-

### 2017-09-07 temp.py

@@ -1,18 +1,0 @@
-from shutil import move
-
-import os
-import glob
-
-exit()
-test = glob.glob('testB/*.jpg')
-
-for t in test:
-
-   t = t.replace('test','train')
-   os.remove(t)
-   #t = t.split('/')[-1]
-
-   #src  = 'trainB/'+t
-   #dest = 'testB/'+t
-
-   #move(src, dest)

### 2017-09-07 files/paper/paper.tex
update
updates

@@
 \begin{abstract}
-Autonomous underwater robots often rely on visual input for decision making due to its non-intrusive and passive nature
-.
+Autonomous underwater robots often rely on visual input for decision making due to its non-intrusive and passive nature.
 However, due to many factors such as light refraction, particles in the water, and color distortion, images are often times very noisy.
@@
 variety of underwater data, as well as the high amount of noise introduced, many algorithms may perform poorly in
-these different domains. Figure 1 shows the high variability that may occur in underwater vision. A step towards a
+these different domains. Figure 1 shows the high variability that may occur in underwater environments. A step towards a
 solution to this
@@
 
-While there have been many very successful recent approaches towards colorization
-\cite{zhang2016colorful,iizuka2016let}, all are focused on the task of grayscale to color. Color correction and image
-restoration for the underwater domain has been less explored. The work of \cite{torres2005color} used an energy
-minimization formulation using a Markov Random Field.
+While there have been many very successful recent approaches towards automatic colorization
+\cite{zhang2016colorful,iizuka2016let}, most are focused on the task of grayscale to color.
+The work of \cite{torres2005color} used an energy minimization formulation using a Markov Random Field. 
+MORE RELATED BLAH. Many use physics based models to directly model the light source and such.
+Most similar to our line of work is the recently proposed WaterGAN \cite{li2017watergan}, which uses
+GANs for color correction of underwater images. As ground truth pairs do not exist for underwater images,
+their first step is to structure a generator to create realistic underwater images. Their generator model
+can be broken down into three stages: 1) Attenuation, which accounts for range-dependent attenuation of light.
+2) Scattering, which models the haze effect caused by photons scattering back towards the image sensor. 3)
+Vingetting, which produces a shading effect on the image corners that can be caused by certain camera lenses.
+Opposed to our work, they use a GAN for generating the underwater images and Euclidean loss for color correction,
+where as we use a GAN for both. Furthermore, they require depth information during the training of WaterGAN,
+whereas we only require two separate image domains.
+
+Recent work in generative models, specifically GANs, have shown great success
+in areas such as inpainting \cite{pathak2016context}, style transfer \cite{Gatys_2016_CVPR}, and image-to-image
+translation \cite{isola2016image,zhu2017unpaired}. This is highly due to their ability to provide a more meaningful
+loss than simply the Euclidean distance, which has been shown to produce blurry results. In our work, we structure
+the problem as paired image-to-image translation, using Generative Adversarial Networks (GANs) as our generative model.
+Much like the work of \cite{isola2016image}, we use image pairs from two domains an input and ground truth.
 
 \section{Method}
-Recent work in generative models, specifically Generative Adversarial
-Networks (GANs), have shown great success in areas such as inpainting \cite{pathak2016context}, style transfer
-\cite{Gatys_2016_CVPR}, and image-to-image translation \cite{isola2016image,zhu2017unpaired}. This is highly due to
-their ability to provide a more meaningful loss than simply the Euclidean distance, which has been shown to produce
-blurry results.
 
@@
 \subsection{Objective}
+Normal GAN objective, then go into WGAN-GP. L1 weight as well.
 
-\subsection{Network Architectures}
+\subsection{Network and Training Details}
+
+L1 weight 100, batch size 32, wgan loss, learning rate 1e-4, IG weight 1.0 and 0.0, 100 epochs
+Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$.
 

### 2017-09-07 tests/edge_detection.py
added edge detection tests

@@ -1,0 +1,72 @@
+import cv2
+import numpy as np
+
+'''
+# original image
+img = cv2.imread('images/n01917289_4982_real.png',0)
+
+# cyclegan image
+cimg = cv2.imread('images/n01917289_4982.png',0)
+
+# our image
+uimg = cv2.imread('images/n01917289_4982_gen_IG_0.0.png',0)
+'''
+
+import glob
+
+# real images
+imgs = []
+
+# cyclegan images
+cimgs = []
+
+# our ugan images
+uimgs = []
+
+images = sorted(glob.glob('images/*.png'))
+for i in images:
+   img = cv2.imread(i)
+
+   if 'real' in i: imgs.append(img)
+   elif 'IG_0.0' in i: uimgs.append(img)
+   elif 'real' not in i and 'IG_1.0' not in i and 'IG_0.0' not in i: cimgs.append(img)
+
+imgs = np.asarray(imgs)
+cimgs = np.asarray(cimgs)
+uimgs = np.asarray(uimgs)
+
+for i,c,u in zip(imgs, cimgs, uimgs):
+
+   # edges of original
+   edges = cv2.Canny(i,100,200)/255.0
+
+   # edges of cyclegan
+   cedges = cv2.Canny(c,100,200)/255.0
+
+   # edges of ugan
+   uedges = cv2.Canny(u,100,200)/255.0
+
+   print 'cyclegan: ',np.linalg.norm(edges-cedges)
+   print 'ugan:     ',np.linalg.norm(edges-uedges)
+   print
+
+   cv2.imwrite('img.png', i)
+   cv2.imwrite('edges.png', 255.0*edges)
+   cv2.imwrite('cedges.png', 255.0*cedges)
+   cv2.imwrite('uedges.png', 255.0*uedges)
+
+   exit()
+
+cv2.imwrite('edges.png', edges)
+cv2.imwrite('cedges.png', cedges)
+cv2.imwrite('uedges.png', uedges)
+
+edges = edges/255.0
+cedges = cedges/255.0
+uedges = uedges/255.0
+
+print np.linalg.norm(edges-cedges)
+print np.linalg.norm(edges-uedges)
+
+
+

### 2017-09-07 tests/edge_detection.py
added edge detection scores

@@ -1,18 +1,8 @@
 import cv2
 import numpy as np
-
-'''
-# original image
-img = cv2.imread('images/n01917289_4982_real.png',0)
-
-# cyclegan image
-cimg = cv2.imread('images/n01917289_4982.png',0)
-
-# our image
-uimg = cv2.imread('images/n01917289_4982_gen_IG_0.0.png',0)
-'''
-
 import glob
+import ntpath
+from tqdm import tqdm
 
 # real images
 imgs = []
@@ -23,50 +13,56 @@ cimgs = []
 # our ugan images
 uimgs = []
 
-images = sorted(glob.glob('images/*.png'))
-for i in images:
-   img = cv2.imread(i)
+# all the image paths
+real_paths   = sorted(glob.glob('test_images/original/*.png'))
+cgan_paths   = sorted(glob.glob('test_images/cgan/*.png'))
+ugan_0_paths = sorted(glob.glob('test_images/ugan_0.0/*.png'))
+ugan_1_paths = sorted(glob.glob('test_images/ugan_1.0/*.png'))
 
-   if 'real' in i: imgs.append(img)
-   elif 'IG_0.0' in i: uimgs.append(img)
-   elif 'real' not in i and 'IG_1.0' not in i and 'IG_0.0' not in i: cimgs.append(img)
+# respective distances in image space of canny edge detection
+cgan_dist   = []
+ugan_0_dist = []
+ugan_1_dist = []
 
-imgs = np.asarray(imgs)
-cimgs = np.asarray(cimgs)
-uimgs = np.asarray(uimgs)
 
-for i,c,u in zip(imgs, cimgs, uimgs):
+# loop through all paths and open images
+for r,c,u0,u1 in tqdm(zip(real_paths, cgan_paths, ugan_0_paths, ugan_1_paths)):
+
+   rimg  = cv2.imread(r)
+   cimg  = cv2.imread(c)
+   u0img = cv2.imread(u0)
+   u1img = cv2.imread(u1)
 
    # edges of original
-   edges = cv2.Canny(i,100,200)/255.0
+   edges = cv2.Canny(rimg,100,200)/255.0
 
    # edges of cyclegan
-   cedges = cv2.Canny(c,100,200)/255.0
+   cedges = cv2.Canny(cimg,100,200)/255.0
 
-   # edges of ugan
[…]

### 2017-09-07 tests/edge_detection.py
update

@@ -24,9 +24,14 @@ cgan_dist   = []
 ugan_0_dist = []
 ugan_1_dist = []
 
-
 # loop through all paths and open images
 for r,c,u0,u1 in tqdm(zip(real_paths, cgan_paths, ugan_0_paths, ugan_1_paths)):
+
+   image_name = ntpath.basename(r)
+
+   #if image_name != 'n01496331_11938.png': continue
+   if image_name != 'n01917289_4078.png': continue
+
 
    rimg  = cv2.imread(r)
    cimg  = cv2.imread(c)
@@ -35,6 +40,7 @@ for r,c,u0,u1 in tqdm(zip(real_paths, cgan_paths, ugan_0_paths, ugan_1_paths)):
 
    # edges of original
    edges = cv2.Canny(rimg,100,200)/255.0
+
 
    # edges of cyclegan
    cedges = cv2.Canny(cimg,100,200)/255.0
@@ -48,11 +54,34 @@ for r,c,u0,u1 in tqdm(zip(real_paths, cgan_paths, ugan_0_paths, ugan_1_paths)):
    cgan_dist.append(np.linalg.norm(edges-cedges))
    ugan_0_dist.append(np.linalg.norm(edges-u0edges))
    ugan_1_dist.append(np.linalg.norm(edges-u1edges))
+   
+   print 'cgan:   ',np.linalg.norm(edges-cedges)
+   print 'ugan_0: ',np.linalg.norm(edges-u0edges)
+   print 'ugan_1: ',np.linalg.norm(edges-u1edges)
+   print
 
-   #print 'cyclegan: ',np.linalg.norm(edges-cedges)
-   #print 'ugan_0:   ',np.linalg.norm(edges-u0edges)
-   #print 'ugan_1:   ',np.linalg.norm(edges-u1edges)
-   #print
+   # save a bunch of images for paper
+   # original images
+   cv2.imwrite('original.png', rimg)
+   cv2.imwrite('cimg.png', cimg)
+   cv2.imwrite('u0img.png', u0img)
+   cv2.imwrite('u1img.png', u1img)
+
+   # edges of original image
+   cv2.imwrite('edges.png', 255.0*edges)
+   
+   # edges of cgan
+   cv2.imwrite('cedges.png', 255.0*cedges)
+
+   # edges of ugan 0.0
+   cv2.imwrite('u0edges.png', 255.0*u0edges)
+   
[…]

### 2017-09-08 tests/edge_detection.py
update

@@ -24,14 +24,25 @@ cgan_dist   = []
 ugan_0_dist = []
 ugan_1_dist = []
 
+save_images = ['n01496331_11763.png', 'n01496331_22079.png', 'n01496331_2629.png', 'n01914609_1607.png', 'n01664065_9210.png', 'n02607072_763.png']
+
+largest = 0
+l_img = ''
+
+save = 0
+
+# just open and close quick to wipe it
+results_file = open('result_images/results.txt', 'w')
+results_file.close()
+results_file = open('result_images/results.txt', 'a')
+results_file.write('image_name,cgan_dist,ugan_0_dist,ugan_1_dist\n')
+
 # loop through all paths and open images
 for r,c,u0,u1 in tqdm(zip(real_paths, cgan_paths, ugan_0_paths, ugan_1_paths)):
 
+   if save == 1 and ntpath.basename(r) not in save_images: continue
+   
    image_name = ntpath.basename(r)
-
-   #if image_name != 'n01496331_11938.png': continue
-   if image_name != 'n01917289_4078.png': continue
-
 
    rimg  = cv2.imread(r)
    cimg  = cv2.imread(c)
@@ -40,7 +51,6 @@ for r,c,u0,u1 in tqdm(zip(real_paths, cgan_paths, ugan_0_paths, ugan_1_paths)):
 
    # edges of original
    edges = cv2.Canny(rimg,100,200)/255.0
-
 
    # edges of cyclegan
    cedges = cv2.Canny(cimg,100,200)/255.0
@@ -51,42 +61,53 @@ for r,c,u0,u1 in tqdm(zip(real_paths, cgan_paths, ugan_0_paths, ugan_1_paths)):
    # edges of ugan 1.0
    u1edges = cv2.Canny(u1img,100,200)/255.0
 
-   cgan_dist.append(np.linalg.norm(edges-cedges))
-   ugan_0_dist.append(np.linalg.norm(edges-u0edges))
-   ugan_1_dist.append(np.linalg.norm(edges-u1edges))
-   
-   print 'cgan:   ',np.linalg.norm(edges-cedges)
-   print 'ugan_0: ',np.linalg.norm(edges-u0edges)
-   print 'ugan_1: ',np.linalg.norm(edges-u1edges)
-   print
+   cgan_dist_   = np.linalg.norm(edges-cedges)
+   ugan_0_dist_ = np.linalg.norm(edges-u0edges)
+   ugan_1_dist_ = np.linalg.norm(edges-u1edges)
 
[…]

### 2017-09-08 files/paper/paper.tex
updates
update

@@
 \section{Method}
+Our approach
 
@@
 \subsubsection{Discriminator}
+
+\section{Experiments}
+
+Here I want to show a number of things. First talk about the datasets used, Imagenet and the diving videos.
+Second, show some general results. Explain how our network is able to do three very important things: 1) Restore an
+image to its natural colors with varying amounts of distortion, i.e. blue hue, green hue, aka not just one type of
+color distortion. 2) The network does not just subtract a certain hue from the entire image. Show how in the clownfish
+image, part of the image has good colors, while part of it doesn't. Our network is able to leave correct colors. Third,
+show that even images taken towards the water's surface, either above or below, are able to be restored correctly.
+
+Third mention that since CycleGAN has a cycle consistent nature, compare their results. Then from there go into how
+ours are better by showing results from Canny Edge Detector.
 

### 2017-09-08 tests/createImages.py
update

@@ -1,0 +1,59 @@
+'''
+
+Script to create a nxm matrix of images
+
+'''
+
+import cv2
+import numpy as np
+import scipy.misc as misc
+from glob import glob
+
+if __name__ == '__main__':
+
+   n = 2 # cols
+   m = 4  # rows
+
+   num_images = n*m
+
+   img_size = (256, 256, 3)
+
+   canvas = 255*np.ones((m*img_size[0]+(10*m)+10, n*img_size[1]+(10*n)+10, 3), dtype=np.uint8)
+   
+   start_x = 10
+   start_y = 10
+
+   x = 0
+   y = 0
+
+   image_paths = sorted(glob('result_images/*.png'))
+
+   count = 0
+   for impath in image_paths:
+
+      print impath
+      if count == 7: break
+      count += 1
+   exit()
+
+   for img in gen_imgs:
+
+      end_x = start_x+256
+      end_y = start_y+256
+      
+      canvas[start_y:end_y, start_x:end_x, :] = img
+
+      if x < n:
+         start_x += 256+10
+         x += 1
+      if x == n:
+         x       = 0
+         start_x = 10
+         start_y = end_y + 10
+         end_y   = start_y+256
+
+   misc.imsave('results.jpg', canvas)
+   #cv2.imwrite('results.jpg', canvas)
+   #cv2.imshow('canvas', canvas)
+   #cv2.waitKey(0)
+   #cv2.destroyAllWindows()

### 2017-09-08 tests/edge_detection.py

@@ -29,7 +29,7 @@ save_images = ['n01496331_11763.png', 'n01496331_22079.png', 'n01496331_2629.png
 largest = 0
 l_img = ''
 
-save = 0
+save = 1
 
 # just open and close quick to wipe it
 results_file = open('result_images/results.txt', 'w')
@@ -42,7 +42,7 @@ for r,c,u0,u1 in tqdm(zip(real_paths, cgan_paths, ugan_0_paths, ugan_1_paths)):
 
    if save == 1 and ntpath.basename(r) not in save_images: continue
    
-   image_name = ntpath.basename(r)
+   image_name = ntpath.basename(r).split('.png')[0]
 
    rimg  = cv2.imread(r)
    cimg  = cv2.imread(c)
@@ -71,9 +71,9 @@ for r,c,u0,u1 in tqdm(zip(real_paths, cgan_paths, ugan_0_paths, ugan_1_paths)):
 
    d = np.linalg.norm(edges-cedges) - np.linalg.norm(edges-u0edges)
 
-   if d > largest:
-      largest = d
-      l_img = image_name
+   #if d > largest:
+   #   largest = d
+   #   l_img = image_name
 
    if save == 1:
 
@@ -91,7 +91,7 @@ for r,c,u0,u1 in tqdm(zip(real_paths, cgan_paths, ugan_0_paths, ugan_1_paths)):
       cv2.imwrite('result_images/'+image_name+'_u1img.png', u1img)
 
       # edges of original image
-      cv2.imwrite('result_images/'+image_name+'_edges.png', 255.0*edges)
+      cv2.imwrite('result_images/'+image_name+'_oedges.png', 255.0*edges)
       
       # edges of cgan
       cv2.imwrite('result_images/'+image_name+'_cedges.png', 255.0*cedges)

### 2017-09-08 tests/createImages.py
update

@@ -19,7 +19,7 @@ if __name__ == '__main__':
    img_size = (256, 256, 3)
 
    canvas = 255*np.ones((m*img_size[0]+(10*m)+10, n*img_size[1]+(10*n)+10, 3), dtype=np.uint8)
-   
+
    start_x = 10
    start_y = 10
 
@@ -52,7 +52,7 @@ if __name__ == '__main__':
          start_y = end_y + 10
          end_y   = start_y+256
 
-   misc.imsave('results.jpg', canvas)
+   misc.imsave('results.png', canvas)
    #cv2.imwrite('results.jpg', canvas)
    #cv2.imshow('canvas', canvas)
    #cv2.waitKey(0)

### 2017-09-08 files/paper/paper.tex
update

@@
 
+%\newcommand\animage{\adjustbox{valign=m,vspace=0pt}{\includegraphics[width=.2\linewidth]{n01496331_15872_original}}}
+
+\usepackage{adjustbox}
 \usepackage{url}
@@
 \section{Introduction}
+TODO - talk about having to go back to the same location if you want to get good/bad pairs of the "same" image.
 Vision is a commonly used sensor in autonomous underwater robots due to its non-intrusive, passive, and energy
@@
 \section{Method}
-Our approach
+In this section we propose our method for color restoration of underwater images. Depending on depth, lighting
+conditions, camera, and location, the amount of distortion an image undergoes can vary.  Because ground truth pairs do
+not exist for distorted underwater images, we use the recently proposed CycleGAN \cite{zhu2017unpaired} to generate
+a paired dataset of images. CycleGAN has shown success in translating an image from domain $X$ to domain $Y$,
+\textit{without} a paired sample. By letting $X$ be a set of underwater images
 
@@
 ours are better by showing results from Canny Edge Detector.
+
+\begin{figure}
+\centering
+\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.5cm}}
+   % TODO 
+   % I couldn't figure out how to get the text centered above the images
+   % Also, the numbers below the images should be centered too, and more
+   % obviously below the row instead of seemlingly above the next one. Those
+   % numbers are the distances in pixel space (normalized between [0,1]) from
+   % the edge image to the original edge image.
+
+   \small{Original} & \small{CycleGAN} & \small{UGAN} & \small{UGAN-P} \\
+
+   \includegraphics[width=0.8in]{n01496331_15872_original} &
+   \includegraphics[width=0.8in]{n01496331_15872_cimg}     &
+   \includegraphics[width=0.8in]{n01496331_15872_u0img}    &
+   \includegraphics[width=0.8in]{n01496331_15872_u1img}    \\ [-1ex]
+   \includegraphics[width=0.8in]{n01496331_15872_oedges}   &
+   \includegraphics[width=0.8in]{n01496331_15872_cedges}   &
+   \includegraphics[width=0.8in]{n01496331_15872_u0edges}  &
+   \includegraphics[width=0.8in]{n01496331_15872_u1edges}  \\
+   0 & \small{125.78} & \small{80.68} & \small{78.49} \\
+
+   \includegraphics[width=0.8in]{n01496331_22079_original} &
+   \includegraphics[width=0.8in]{n01496331_22079_cimg}     & 
+   \includegraphics[width=0.8in]{n01496331_22079_u0img}    &
+   \includegraphics[width=0.8in]{n01496331_22079_u1img}    \\ [-1ex]
+   \includegraphics[width=0.8in]{n01496331_22079_oedges}   &
+   \includegraphics[width=0.8in]{n01496331_22079_cedges}   &
+   \includegraphics[width=0.8in]{n01496331_22079_u0edges}  &
+   \includegraphics[width=0.8in]{n01496331_22079_u1edges}  \\
+   0 & \small{94.57} & \small{38.22} & \small{37.29} \\
+
+   \includegraphics[width=0.8in]{n02607072_4739_original} &
+   \includegraphics[width=0.8in]{n02607072_4739_cimg} &
+   \includegraphics[width=0.8in]{n02607072_4739_u0img} &
+   \includegraphics[width=0.8in]{n02607072_4739_u1img} \\ [-1ex]
+   \includegraphics[width=0.8in]{n02607072_4739_oedges} &
+   \includegraphics[width=0.8in]{n02607072_4739_cedges} &
+   \includegraphics[width=0.8in]{n02607072_4739_u0edges} &
+   \includegraphics[width=0.8in]{n02607072_4739_u1edges} \\
+   0 & \small{100.69} & \small{87.81} & \small{87.95} \\
+
+\end{tabular}
+\caption{Running the Canny Edge Detector on sample images. Both variants of UGAN contain less noise than CycleGAN,
+and are closer in the image space to the original. For each pair, the top row is the input image, and bottom row
+the result of the edge detector.}
+\end{figure}
 

### 2017-09-08 tests/edge_detection.py

@@ -24,7 +24,7 @@ cgan_dist   = []
 ugan_0_dist = []
 ugan_1_dist = []
 
-save_images = ['n01496331_11763.png', 'n01496331_22079.png', 'n01496331_2629.png', 'n01914609_1607.png', 'n01664065_9210.png', 'n02607072_763.png']
+save_images = ['n02607072_4739.png', 'n01496331_15872.png', 'n01496331_22079.png']
 
 largest = 0
 l_img = ''

### 2017-09-08 files/paper/paper.tex
update

@@
 \section{Method}
-In this section we propose our method for color restoration of underwater images. Depending on depth, lighting
-conditions, camera, and location, the amount of distortion an image undergoes can vary.  Because ground truth pairs do
-not exist for distorted underwater images, we use the recently proposed CycleGAN \cite{zhu2017unpaired} to generate
-a paired dataset of images. CycleGAN has shown success in translating an image from domain $X$ to domain $Y$,
-\textit{without} a paired sample. By letting $X$ be a set of underwater images
 
-\subsection{Generative Adversarial Networks}
+\subsection{Dataset Generation}
+In this section we propose our method for color restoration of underwater images. Depth, lighting conditions, camera
+type, and location are all factors that affect the amount of distortion an image undergoes. It is possible that
+underwater images with no distortion exist. We let $I^C$ be an underwater image with no distortion, and $I^D$
+be the same image with distortion. Our goal is to learn the function $f: I^D \rightarrow I^C$. Becasue of the
+difficulty of collecting underwater data, more often than not only $I^D$ or $I^C$ exist.
+
+We use the recently proposed CycleGAN \cite{zhu2017unpaired} to generate $I^D$ from $I^C$, which gives us a paired
+dataset of images. Given two datasets $X$ and $Y$, where $I^C \in X$ and $I^D \in Y$, CycleGAN learns a mapping
+$F: X \rightarrow Y$. Figure 2 shows paired samples generated from CycleGAN. From this paired dataset we train a
+generator $G$ to learn the function $f: I^D \rightarrow I^C$. It should be noted that during our generation of
+training data, CycleGAN simultaneously learns a mapping $G: Y \rightarrow X$, which is equivalent to $f$. In section
+IV we show a comparison with our method.
+
+\subsection{Adversarial Loss}
+We introduce a discriminator $D$ in order to
+
+\begin{figure}
+\centering
+\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.7cm}}
+
+   \includegraphics[width=0.8in]{n01496331_175_B} &
+   \includegraphics[width=0.8in]{n01664065_4022_B} &
+   \includegraphics[width=0.8in]{n01917289_889_B} &
+   \includegraphics[width=0.8in]{n01914609_116_B} \\
+   \includegraphics[width=0.8in]{n01496331_175_A} &
+   \includegraphics[width=0.8in]{n01664065_4022_A} &
+   \includegraphics[width=0.8in]{n01917289_889_A} &
+   \includegraphics[width=0.8in]{n01914609_116_A} \\
+
+\end{tabular}
+\caption{Paired samples of ground truth and distorted images generated by CycleGAN. Top row: Ground truth.
+Bottom row: Generated samples.}
+\end{figure}
 

### 2017-09-10 files/paper/paper.tex
update
updates

@@
 
-\documentclass[conference]{IEEEtran}
+\documentclass[conference,reqno]{IEEEtran}
 
@@
 
-%\newcommand\animage{\adjustbox{valign=m,vspace=0pt}{\includegraphics[width=.2\linewidth]{n01496331_15872_original}}}
-
+\usepackage{amssymb}
+\usepackage{amsmath}
 \usepackage{adjustbox}
@@
 However, due to many factors such as light refraction, particles in the water, and color distortion, images are often times very noisy.
-This paper propose a method using Generative Adversarial Networks (GANs) to denoise underwater images, and show that these images provide both increased accuracy
-for an underwater tracking algorithm, as well as a more visually appealing image. Furthermore, we show how recently
-proposed methods are able to generate a dataset for the purpose of underwater image reconstruction.
+This paper propose a method using Generative Adversarial Networks (GANs) to denoise underwater images, and show that these 
+images provide both increased accuracy for an underwater tracking algorithm, as well as a more visually appealing image.
+Furthermore, we show how recently proposed methods are able to generate a dataset for the purpose of underwater image reconstruction.
 \end{abstract}
@@
 \subsection{Dataset Generation}
-In this section we propose our method for color restoration of underwater images. Depth, lighting conditions, camera
-type, and location are all factors that affect the amount of distortion an image undergoes. It is possible that
-underwater images with no distortion exist. We let $I^C$ be an underwater image with no distortion, and $I^D$
+Here we describe our dataset generation process. Depth, lighting conditions, camera
+model, and location are all factors that affect the amount of distortion an underwater image undergoes. Under certain
+conditions, it is possible that an underwater image may have very little distortion, or none at all.
+We let $I^C$ be an underwater image with no distortion, and $I^D$
 be the same image with distortion. Our goal is to learn the function $f: I^D \rightarrow I^C$. Becasue of the
-difficulty of collecting underwater data, more often than not only $I^D$ or $I^C$ exist.
+difficulty of collecting underwater data, more often than not only $I^D$ or $I^C$ exist, but never both.
 
@@
 $F: X \rightarrow Y$. Figure 2 shows paired samples generated from CycleGAN. From this paired dataset we train a
-generator $G$ to learn the function $f: I^D \rightarrow I^C$. It should be noted that during our generation of
-training data, CycleGAN simultaneously learns a mapping $G: Y \rightarrow X$, which is equivalent to $f$. In section
-IV we show a comparison with our method.
+generator $G$ to learn the function $f: I^D \rightarrow I^C$. It should be noted that during our data generation process,
+CycleGAN simultaneously learns a mapping $G: Y \rightarrow X$, which is similar to $f$. In section IV we show a comparison with our method.
 
-\subsection{Adversarial Loss}
-We introduce a discriminator $D$ in order to
+\subsection{Adversarial Networks}
+GANs are a class of generative models based on game theory in which a generator network competes against an adversary.
+Given an image $I^C$, the generator is trained to produce an image to try and fool the discriminator, which is trained to distinguish be between distorted
+and non-distorted underwater images. In the original GAN formulation, the goal is to solve the minimax problem: \newline
+
+\vspace{4pt}
+
+\begin{equation}
+\begin{aligned}
+   \min\limits_{G}\max\limits_{D} \mathbb{E} & _{I^C \sim p_{train}(I^C)} [logD(I^C)] + \\
+   \mathbb{E} & _{I^D \sim p_{gen}(I^D)}[log(1 - D(G(I^D)))]
+\end{aligned}
+\end{equation}
 

### 2017-09-10 files/paper/paper.tex
updates

@@
 \subsection{Adversarial Networks}
-GANs are a class of generative models based on game theory in which a generator network competes against an adversary.
-Given an image $I^C$, the generator is trained to produce an image to try and fool the discriminator, which is trained to distinguish be between distorted
+GANs \cite{goodfellow2014generative} are a class of generative models based on game theory in which a generator network competes against an adversary.
+Given an image $I^D$, the generator is trained to produce an image to try and fool the discriminator, which is trained to distinguish be between distorted
 and non-distorted underwater images. In the original GAN formulation, the goal is to solve the minimax problem: \newline
@@
    \mathbb{E} & _{I^D \sim p_{gen}(I^D)}[log(1 - D(G(I^D)))]
+\end{aligned}
+\end{equation}
+
+\noindent In this formulation, the discriminator is hypothesized as a classifier with a sigmoid cross entropy loss function,
+which in practice may lead to issues such as the vanish gradient and mode collapse. There have been many recent works which
+hypothesize a different loss function for the discriminator \cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}.
+
+In our work, we adopt the Wasserstein GAN with gradient penalty (WGAN-GP) \cite{gulrajani2017improved}, which instead of
+clipping network weights like in \cite{arjovsky2017wasserstein}, enforces the Lipschitz constraint by enforcing a soft constraint on the
+gradient norm of the discriminator's output with respect to its input. 
+Following \cite{gulrajani2017improved}, the new objective then becomes
+
+\begin{equation}
+\begin{aligned}
+   L = \mathbb{E}_{I^D \sim p_{gen}(I^D)} [D(I^D)] - \mathbb{E} & _{I^C \sim p_{train}(I^C)} [D(I^C)] + \\
+   \lambda \mathbb{E} & _{\hat{x} \sim \mathbb{P}_{\hat{x}}} [(|| \nabla_{\hat{x}} D(\hat{x}||_2 -1)^2 ]
 \end{aligned}
@@
 
-\subsection{Objective}
-Normal GAN objective, then go into WGAN-GP. L1 weight as well.
+\subsection{Image Gradient Difference Loss}
 
@@
 Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$.
-
-\subsubsection{Generator}
-
-\subsubsection{Discriminator}
 

### 2017-09-10 files/paper/paper.tex
updates

@@
 
-\vspace{4pt}
-
-\begin{equation}
-\begin{aligned}
-   \min\limits_{G}\max\limits_{D} \mathbb{E} & _{I^C \sim p_{train}(I^C)} [logD(I^C)] + \\
-   \mathbb{E} & _{I^D \sim p_{gen}(I^D)}[log(1 - D(G(I^D)))]
-\end{aligned}
-\end{equation}
-
-\noindent In this formulation, the discriminator is hypothesized as a classifier with a sigmoid cross entropy loss function,
-which in practice may lead to issues such as the vanish gradient and mode collapse. There have been many recent works which
-hypothesize a different loss function for the discriminator \cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}.
-
-In our work, we adopt the Wasserstein GAN with gradient penalty (WGAN-GP) \cite{gulrajani2017improved}, which instead of
-clipping network weights like in \cite{arjovsky2017wasserstein}, enforces the Lipschitz constraint by enforcing a soft constraint on the
-gradient norm of the discriminator's output with respect to its input. 
-Following \cite{gulrajani2017improved}, the new objective then becomes
-
-\begin{equation}
-\begin{aligned}
-   L = \mathbb{E}_{I^D \sim p_{gen}(I^D)} [D(I^D)] - \mathbb{E} & _{I^C \sim p_{train}(I^C)} [D(I^C)] + \\
-   \lambda \mathbb{E} & _{\hat{x} \sim \mathbb{P}_{\hat{x}}} [(|| \nabla_{\hat{x}} D(\hat{x}||_2 -1)^2 ]
-\end{aligned}
-\end{equation}
-
 \begin{figure}
@@
 
+\begin{equation}
+\begin{aligned}
+   \min\limits_{G}\max\limits_{D} \mathbb{E} & _{I^C \sim p_{train}(I^C)} [logD(I^C)] + \\
+   \mathbb{E} & _{I^D \sim p_{gen}(I^D)}[log(1 - D(G(I^D)))]
+\end{aligned}
+\end{equation}
+
+\noindent Note for simplicity in notation, we will further omit $I^C \sim p_{train}$ and $I^D \sim p_{gen}$. In this formulation, the discriminator
+is hypothesized as a classifier with a sigmoid cross entropy loss function,
+which in practice may lead to issues such as the vanish gradient and mode collapse. There have been many recent works which
+hypothesize a different loss function for the discriminator \cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}.
+We focus on the Wasserstein GAN (WGAN) \cite{arjovsky2017wasserstein} formulation, which proposes to use the Earth-Mover or \textit{Wasserstein-1}
+distance $W$ by constructing a value function using the Kantorovich-Rubinstein duality \cite{villani2008optimal}. In this formulation, $W$ is
+approximated given a set of $k$-Lipschitz functions $f$ modeled as neural networks. To ensure $f$ is $k$-Lipschitz, the weights of the discriminator
+are clipped to some range $[-c, c]$. In our work, we adopt the Wasserstein GAN with gradient penalty (WGAN-GP) \cite{gulrajani2017improved}, which instead of
+clipping network weights like in \cite{arjovsky2017wasserstein}, ensures the Lipschitz constraint by enforcing a soft constraint on the
+gradient norm of the discriminator's output with respect to its input. Following \cite{gulrajani2017improved}, the new objective then becomes
+
+\begin{equation}
+\begin{aligned}
+   \mathcal{L}_{WGAN} = \mathbb{E} [D(I^C)] - \mathbb{E} & [D(G(I^D))] + \\
+   \lambda \mathbb{E} & _{\hat{x} \sim \mathbb{P}_{\hat{x}}} [(|| \nabla_{\hat{x}} D(\hat{x})||_2 -1)^2 ],
+\end{aligned}
+\end{equation}
+
+%\begin{equation}
+%\begin{aligned}
+%   \mathcal{L}_{GAN} = \mathbb{E}_{I^D \sim p_{gen}(I^D)} [D(I^D)] - \mathbb{E} & _{I^C \sim p_{train}(I^C)} [D(I^C)] + \\
+%   \lambda \mathbb{E} & _{\hat{x} \sim \mathbb{P}_{\hat{x}}} [(|| \nabla_{\hat{x}} D(\hat{x})||_2 -1)^2 ].
+%\end{aligned}
+%\end{equation}
+
+\noindent where $\mathbb{P}_{\hat{x}}$ is defined as samples along straight lines between pairs of points coming from the true data distribution
+and the generator distribution, and $\lambda$ is a weighing factor. In order to give $G$ some sense of ground truth, we also consider the $L1$
+loss
+
+\begin{equation}
+   \mathcal{L}_{L1} = \mathbb{E} [ || I^C - G(I^D) ||_1 ].
+\end{equation}
+%\begin{equation}
+%   \mathcal{L}_{L1} = \mathbb{E}_{I^D \sim p_{gen}, I^C \sim p_{train}} [ || I^C - G(I^D) ||_1 ].
+%\end{equation}
+
+\noindent Combining these, we get our final objective function for our network, which we call Underwater GAN (UGAN),
+
+\begin{equation}
+   \begin{aligned}
+      \mathcal{L}_{UGAN} = \mathcal{L}_{WGAN} + \mathcal{L}_{L1}.
+   \end{aligned}
+\end{equation}
+
 \subsection{Image Gradient Difference Loss}
+Often times generative models produce blurry images. We explore a strategy to sharpen these predictions by
+directly penalizing the differences of image gradient predictions in the generator, as proposed by \cite{mathieu2015deep}.
+Given a ground truth image $I^C$, predicted image $I^P = G(I^C)$, and $\alpha \geq 1$, the Gradient Difference Loss (GDL) is given by
 
-\subsection{Network and Training Details}
+\begin{equation}
+   \begin{aligned}
+      \mathcal{L}_{GDL}(I^C, I^P) = \\ \sum\limits_{i,j} || & I^C_{i,j} - I^C_{i-1,j}| - | I^P_{i,j} - I^P_{i-1,j}||^{\alpha} + \\
+      || & I^C_{i,j-1} - I^C_{i,j}| - | I^P_{i,j-1} - I^P_{i,j}||^{\alpha},
+   \end{aligned}
+\end{equation}
 
+\noindent In our experiments, we denote our network as UGAN-D when considering the GDL, which can be expressed as
+
+\begin{equation}
+   \begin{aligned}
+      \mathcal{L}_{UGAN-D} = \mathcal{L}_{WGAN} + \mathcal{L}_{L1} + \mathcal{L}_{GDL}.
+   \end{aligned}
+\end{equation}
+
+\subsection{Network Architecture and Training Details}
+We use a similar architecture as \cite{isola2016image}. Due to the Our generator is a U-Net
 L1 weight 100, batch size 32, wgan loss, learning rate 1e-4, IG weight 1.0 and 0.0, 100 epochs

### 2017-09-10 files/paper/paper.tex
updates

@@
 \subsection{Adversarial Networks}
-GANs \cite{goodfellow2014generative} are a class of generative models based on game theory in which a generator network competes against an adversary.
-Given an image $I^D$, the generator is trained to produce an image to try and fool the discriminator, which is trained to distinguish be between distorted
-and non-distorted underwater images. In the original GAN formulation, the goal is to solve the minimax problem: \newline
+GANs \cite{goodfellow2014generative} are a class of generative models based on game theory in which a generator
+network competes against an adversary. Conditioned on an image $I^D$, the generator is trained to produce an \
+image to try and fool the discriminator, which is trained to distinguish be between distorted and non-distorted
+underwater images. In the original GAN formulation, the goal is to solve the minimax problem: \newline
 
@@
 clipping network weights like in \cite{arjovsky2017wasserstein}, ensures the Lipschitz constraint by enforcing a soft constraint on the
-gradient norm of the discriminator's output with respect to its input. Following \cite{gulrajani2017improved}, the new objective then becomes
+gradient norm of the discriminator's output with respect to its input. Following \cite{gulrajani2017improved}, our new objective then becomes
 
@@
 \begin{aligned}
-   \mathcal{L}_{WGAN} = \mathbb{E} [D(I^C)] - \mathbb{E} & [D(G(I^D))] + \\
+   \mathcal{L}_{WGAN}(G,D) = \mathbb{E} [D(I^C)] - \mathbb{E} & [D(G(I^D))] + \\
    \lambda \mathbb{E} & _{\hat{x} \sim \mathbb{P}_{\hat{x}}} [(|| \nabla_{\hat{x}} D(\hat{x})||_2 -1)^2 ],
@@
    \begin{aligned}
-      \mathcal{L}_{UGAN} = \mathcal{L}_{WGAN} + \mathcal{L}_{L1}.
+      \mathcal{L}_{UGAN}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + \mathcal{L}_{L1}(G).
    \end{aligned}
@@
 
-\noindent In our experiments, we denote our network as UGAN-D when considering the GDL, which can be expressed as
+\noindent In our experiments, we denote our network as UGAN-P when considering the GDL, which can be expressed as
 
@@
    \begin{aligned}
-      \mathcal{L}_{UGAN-D} = \mathcal{L}_{WGAN} + \mathcal{L}_{L1} + \mathcal{L}_{GDL}.
+      \mathcal{L}_{UGAN}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + \mathcal{L}_{L1}(G) + \mathcal{L}_{GDL}
    \end{aligned}
@@
 \subsection{Network Architecture and Training Details}
-We use a similar architecture as \cite{isola2016image}. Due to the Our generator is a U-Net
+We use an encoder-decoder network similar to the work of \cite{isola2016image}, in which our generator is
+structured as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.
+
+``U-Net''
+
 L1 weight 100, batch size 32, wgan loss, learning rate 1e-4, IG weight 1.0 and 0.0, 100 epochs

### 2017-09-10 files/paper/paper.tex
updates

@@
 structured as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.
+Encoder-decoder networks continuously downsample (encode) the input to a lower dimensional embedding, in which this embedding is then
+upsampled (decode) to reconstruct the image. The advantage of using a ``U-Net'' comes from explicitly preserving spatial
+dependencies produced by the encoder, as opposed to relying on the embedding to contain all of the information. This
+is done by the addition of ``skip connections'', which concatenate the activations produced from a convolution
+layer $i$ in the encoder to the input of a transpose convolution layer $n-i+1$ in the decoder, where $n$ is the
+total number of layers in the network.
 
-``U-Net''
+Our generator network can be viewed as two subnetworks, an encoder and a decoder. Each convolutional layer in the encoder and decoder
+has a kernel size of 4 and stride 2. Following \cite{radford2015unsupervised}, we use Batch Normalization \cite{pmlr-v37-ioffe15}
+except for the last layer of the decoder.
 
+\footnote{Code is available at https://github.com/cameronfabbri/Underwater-Color-Correction}
 L1 weight 100, batch size 32, wgan loss, learning rate 1e-4, IG weight 1.0 and 0.0, 100 epochs

### 2017-09-11 nets/original_pix2pix.py
need to be more careful...

@@ -42,35 +42,51 @@ def netG(x, PixS, LOSS_METHOD):
    print 'enc_conv8:',enc_conv8
    print
 
-   dec_conv1 = tcl.convolution2d_transpose(enc_conv8, 512, 4, 2, activation_fn=tf.nn.relu, normalizer_fn=tcl.batch_norm, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_dec_conv1')
+   dec_conv1 = tcl.convolution2d_transpose(enc_conv8, 512, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_dec_conv1')
+   if LOSS_METHOD != 'wgan': dec_conv1 = tcl.batch_norm(dec_conv1)
+   dec_conv1 = relu(dec_conv1)
    dec_conv1 = tf.concat([dec_conv1, enc_conv7], axis=3)
    print 'dec_conv1:',dec_conv1
 
-   dec_conv2 = tcl.convolution2d_transpose(dec_conv1, 512, 4, 2, activation_fn=tf.nn.relu, normalizer_fn=tcl.batch_norm,  weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_dec_conv2')
+   dec_conv2 = tcl.convolution2d_transpose(dec_conv1, 512, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_dec_conv2')
+   if LOSS_METHOD != 'wgan': dec_conv2 = tcl.batch_norm(dec_conv2)
+   dec_conv2 = relu(dec_conv2)
    dec_conv2 = tf.concat([dec_conv2, enc_conv6], axis=3)
    print 'dec_conv2:',dec_conv2
    
-   dec_conv3 = tcl.convolution2d_transpose(dec_conv2, 512, 4, 2, activation_fn=tf.nn.relu, normalizer_fn=tcl.batch_norm, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_dec_conv3')
+   dec_conv3 = tcl.convolution2d_transpose(dec_conv2, 512, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_dec_conv3')
+   if LOSS_METHOD != 'wgan': dec_conv3 = tcl.batch_norm(dec_conv3)
[…]

### 2017-09-11 nets/pix2pix.py
aoeuaoentudbaonethud

@@ -97,20 +97,19 @@ def netD(x, LOSS_METHOD, reuse=False):
       if LOSS_METHOD != 'wgan': conv3 = tcl.batch_norm(conv3)
       conv3 = lrelu(conv3)
       
-      conv4 = tcl.conv2d(conv3, 512, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='d_conv4')
+      conv4 = tcl.conv2d(conv3, 512, 4, 1, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='d_conv4')
       if LOSS_METHOD != 'wgan': conv4 = tcl.batch_norm(conv4)
       conv4 = lrelu(conv4)
       
       conv5 = tcl.conv2d(conv4, 1, 1, 1, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='d_conv5')
       if LOSS_METHOD != 'wgan': conv5 = tcl.batch_norm(conv5)
 
-      print x
-      print conv1
-      print conv2
-      print conv3
-      print conv4
-      print conv5
-      exit()
+      print 'x:',x
+      print 'conv1:',conv1
+      print 'conv2:',conv2
+      print 'conv3:',conv3
+      print 'conv4:',conv4
+      print 'conv5:',conv5
       return conv5
 
 

### 2017-09-11 _train.sh
update

@@ -1,1 +1,1 @@
-python train.py --DATA=rocks --EPOCHS=1000 --NETWORK=pix2pix --IG_WEIGHT=1.0 --L1_WEIGHT=100.0 --BATCH_SIZE=16 --LOSS_METHOD=wgan --LEARNING_RATE=1e-4
+python train.py --DATA=underwater_imagenet --EPOCHS=100 --NETWORK=pix2pix --IG_WEIGHT=0.0 --L1_WEIGHT=100.0 --BATCH_SIZE=32 --LOSS_METHOD=wgan --LEARNING_RATE=1e-4

### 2017-09-11 nets/pix2pix.py
added layer norm option

@@ -5,7 +5,7 @@ import sys
 sys.path.insert(0, 'ops/')
 from tf_ops import *
 
-def netG(x, PixS, LOSS_METHOD):
+def netG(x, LOSS_METHOD):
       
    enc_conv1 = tcl.conv2d(x, 64, 4, 2, activation_fn=tf.identity, normalizer_fn=tcl.batch_norm, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_enc_conv1')
    enc_conv1 = lrelu(enc_conv1)
@@ -76,33 +76,36 @@ def netG(x, PixS, LOSS_METHOD):
    return dec_conv8
 
 
-def netD(x, LOSS_METHOD, reuse=False):
+def netD(x, LAYER_NORM, LOSS_METHOD, reuse=False):
    print
    print 'netD'
-   
+
    sc = tf.get_variable_scope()
    with tf.variable_scope(sc, reuse=reuse):
 
       conv1 = tcl.conv2d(x, 64, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='d_conv1')
-      if LOSS_METHOD != 'wgan':
-         print 'Using batch norm in D'
-         conv1 = tcl.batch_norm(conv1)
+      if LOSS_METHOD != 'wgan': conv1 = tcl.batch_norm(conv1)
+      elif LOSS_METHOD == 'wgan' and LAYER_NORM: conv1 = tcl.layer_norm(conv1)
       conv1 = lrelu(conv1)
       
       conv2 = tcl.conv2d(conv1, 128, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='d_conv2')
       if LOSS_METHOD != 'wgan': conv2 = tcl.batch_norm(conv2)
+      elif LOSS_METHOD == 'wgan' and LAYER_NORM: conv2 = tcl.layer_norm(conv2)
       conv2 = lrelu(conv2)
       
       conv3 = tcl.conv2d(conv2, 256, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='d_conv3')
       if LOSS_METHOD != 'wgan': conv3 = tcl.batch_norm(conv3)
+      elif LOSS_METHOD == 'wgan' and LAYER_NORM: conv3 = tcl.layer_norm(conv3)
       conv3 = lrelu(conv3)
[…]

### 2017-09-11 train.py

@@ -29,7 +29,7 @@ import data_ops
 
 if __name__ == '__main__':
    parser = argparse.ArgumentParser()
-   parser.add_argument('--PixS',          required=False,default=0,type=int,help='Pixel shuffle')
+   parser.add_argument('--LAYER_NORM',    required=False,default=0,type=int,help='Pixel shuffle')
    parser.add_argument('--DATA',          required=False,default='rocks',type=str,help='Dataset to use')
    parser.add_argument('--EPOCHS',        required=False,default=4,type=int,help='Number of epochs for GAN')
    parser.add_argument('--NETWORK',       required=False,default='pix2pix',type=str,help='Network to use')
@@ -48,11 +48,11 @@ if __name__ == '__main__':
    NETWORK       = a.NETWORK
    EPOCHS        = a.EPOCHS
    DATA          = a.DATA
-   PixS          = bool(a.PixS)
+   LAYER_NORM          = bool(a.LAYER_NORM)
    
    EXPERIMENT_DIR  = 'checkpoints/LOSS_METHOD_'+LOSS_METHOD\
                      +'/NETWORK_'+NETWORK\
-                     +'/PixS_'+str(PixS)\
+                     +'/LAYER_NORM_'+str(LAYER_NORM)\
                      +'/L1_WEIGHT_'+str(L1_WEIGHT)\
                      +'/IG_WEIGHT_'+str(IG_WEIGHT)\
                      +'/DATA_'+DATA+'/'\
@@ -77,7 +77,7 @@ if __name__ == '__main__':
    exp_info['NETWORK']       = NETWORK
    exp_info['EPOCHS']        = EPOCHS
    exp_info['DATA']          = DATA
-   exp_info['PixS']            = PixS
+   exp_info['LAYER_NORM']            = LAYER_NORM
    exp_pkl = open(EXPERIMENT_DIR+'info.pkl', 'wb')
    data = pickle.dumps(exp_info)
    exp_pkl.write(data)
@@ -92,7 +92,7 @@ if __name__ == '__main__':
    print 'NETWORK:       ',NETWORK
    print 'EPOCHS:        ',EPOCHS
    print 'DATA:          ',DATA
-   print 'PixS:          ',PixS
+   print 'LAYER_NORM:    ',LAYER_NORM
    print
 
    if NETWORK == 'pix2pix': from pix2pix import *
[…]

### 2017-09-11 nets/pix2pix.py
update

@@ -113,7 +113,6 @@ def netD(x, LAYER_NORM, LOSS_METHOD, reuse=False):
       print 'conv3:',conv3
       print 'conv4:',conv4
       print 'conv5:',conv5
-      exit()
       return conv5
 
 

### 2017-09-11 files/paper/paper.tex
updates

--- 2017-09-10 files/paper/paper.tex
@@
 \noindent where $\mathbb{P}_{\hat{x}}$ is defined as samples along straight lines between pairs of points coming from the true data distribution
-and the generator distribution, and $\lambda$ is a weighing factor. In order to give $G$ some sense of ground truth, we also consider the $L1$
-loss
+and the generator distribution, and $\lambda$ is a weighing factor. In order to give $G$ some sense of ground truth, as well as capture low level
+frequencies in the image, we also consider the $L1$ loss
 
@@
 \subsection{Network Architecture and Training Details}
-We use an encoder-decoder network similar to the work of \cite{isola2016image}, in which our generator is
+Our generator network uses an encoder-decoder structure similar to the work of \cite{isola2016image}, which is
 structured as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.
+Encoder-decoder networks downsample (encode) the input via convolutions to a lower dimensional embedding, in which this embedding is then
+upsampled (decode) via transpose convolutions to reconstruct the image. The advantage of using a ``U-Net'' comes from explicitly preserving spatial
+dependencies produced by the encoder, as opposed to relying on the embedding to contain all of the information. This
+is done by the addition of ``skip connections'', which concatenate the activations produced from a convolution
+layer $i$ in the encoder to the input of a transpose convolution layer $n-i+1$ in the decoder, where $n$ is the
+total number of layers in the network. Each convolutional layer in our generator uses kernel size $4 \times 4$ with stride 2.
+Following \cite{radford2015unsupervised}, we use batch normalization \cite{pmlr-v37-ioffe15} throughout except for the last layer of the decoder.
 
-``U-Net''
-
-L1 weight 100, batch size 32, wgan loss, learning rate 1e-4, IG weight 1.0 and 0.0, 100 epochs
-Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$.
+Our discriminator is modeled after that of \cite{radford2015unsupervised}, except no batch normalization is used. This is due
+to the fact that we penalize the norm of the discriminator's gradient with respect to each input individually, which batch
+normalization would invalidate. The authors of \cite{gulrajani2017improved} recommend layer normalization \cite{ba2016layer},
+but we found no significant improvements. RESULTS PENDING
+In all of our experiments, we use $\lambda_{L1} = 100$, batch size of 32, Adam Optimizer \cite{kingma2014adam} with learning rate $1e-4$, and train for 100 epochs.
+Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$. Our implementation was done
+using the Tensorflow library \cite{abadi2016tensorflow}.
+\footnote{Code is available at https://github.com/cameronfabbri/Underwater-Color-Correction}
 

### 2017-09-11 eval.py
fixed eval to include layer norm

@@ -47,11 +47,11 @@ if __name__ == '__main__':
    IG_WEIGHT     = a['IG_WEIGHT']
    NETWORK       = a['NETWORK']
    DATA          = a['DATA']
-   PixS          = a['PixS']
+   LAYER_NORM    = a['LAYER_NORM']
 
    EXPERIMENT_DIR = 'checkpoints/LOSS_METHOD_'+LOSS_METHOD\
                      +'/NETWORK_'+NETWORK\
-                     +'/PixS_'+str(PixS)\
+                     +'/LAYER_NORM_'+str(LAYER_NORM)\
                      +'/L1_WEIGHT_'+str(L1_WEIGHT)\
                      +'/IG_WEIGHT_'+str(IG_WEIGHT)\
                      +'/DATA_'+DATA+'/'\
@@ -70,7 +70,7 @@ if __name__ == '__main__':
    print 'BATCH_SIZE:    ',BATCH_SIZE
    print 'NETWORK:       ',NETWORK
    print 'EPOCHS:        ',EPOCHS
-   print 'PixS:          ',PixS
+   print 'LAYER_NORM:    ',LAYER_NORM
    print
 
    if NETWORK == 'pix2pix': from pix2pix import *
@@ -83,7 +83,7 @@ if __name__ == '__main__':
    image_u = tf.placeholder(tf.float32, shape=(1, 256, 256, 3), name='image_u')
 
    # generated corrected colors
-   gen_image = netG(image_u, PixS, LOSS_METHOD)
+   gen_image = netG(image_u, LOSS_METHOD)
 
    saver = tf.train.Saver(max_to_keep=1)
 

### 2017-09-11 files/paper/paper.tex
update

@@
 \usepackage{graphicx}
-\graphicspath{{images/}}
+\graphicspath{ {images/}{images/figure1/} }
+%\graphicspath{{images/failures/}}
+%\graphicspath{{images/figure1/}}
 
@@
 
-\begin{figure}[!htb]
-   \begin{center}$
-      \begin{array}{cccc}
-         \includegraphics[width=3in]{figure1}
-      \end{array}$
-   \end{center}
-   \caption{Underwater images showing the vast divesity of noise that can occur, including
-   different hues of green and blue, as well as particles in the water.}
+\begin{figure}
+\centering
+\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.7cm}}
+
+   \includegraphics[width=0.8in]{n01496331_7428_f1} &
+   \includegraphics[width=0.8in]{n01496331_16340_f1} &
+   \includegraphics[width=0.8in]{n01914609_5148_f1} &
+   \includegraphics[width=0.8in]{robot_f1} \\
+   \includegraphics[width=0.8in]{n01664065_30279_f1} &
+   \includegraphics[width=0.8in]{n01917289_5711_f1} &
+   \includegraphics[width=0.8in]{n01917289_4087_f1} &
+   \includegraphics[width=0.8in]{n02607072_10395_f1} \\
+
+\end{tabular}
+\caption{Sample underwater images displaying the diversity of distortion that can occur. \textbf{Maybe say something about how
+some images lost all color, but some kept some color for close objects.}}
 \end{figure}

### 2017-09-11 files/paper/paper.tex
update

@@
 
-\noindent Note for simplicity in notation, we will further omit $I^C \sim p_{train}$ and $I^D \sim p_{gen}$. In this formulation, the discriminator
-is hypothesized as a classifier with a sigmoid cross entropy loss function,
-which in practice may lead to issues such as the vanish gradient and mode collapse. There have been many recent works which
-hypothesize a different loss function for the discriminator \cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}.
-We focus on the Wasserstein GAN (WGAN) \cite{arjovsky2017wasserstein} formulation, which proposes to use the Earth-Mover or \textit{Wasserstein-1}
-distance $W$ by constructing a value function using the Kantorovich-Rubinstein duality \cite{villani2008optimal}. In this formulation, $W$ is
-approximated given a set of $k$-Lipschitz functions $f$ modeled as neural networks. To ensure $f$ is $k$-Lipschitz, the weights of the discriminator
-are clipped to some range $[-c, c]$. In our work, we adopt the Wasserstein GAN with gradient penalty (WGAN-GP) \cite{gulrajani2017improved}, which instead of
-clipping network weights like in \cite{arjovsky2017wasserstein}, ensures the Lipschitz constraint by enforcing a soft constraint on the
-gradient norm of the discriminator's output with respect to its input. Following \cite{gulrajani2017improved}, our new objective then becomes
+\noindent Note for simplicity in notation, we will further omit $I^C \sim p_{train}$ and $I^D \sim p_{gen}$. In this
+formulation, the discriminator is hypothesized as a classifier with a sigmoid cross entropy loss function, which in
+practice may lead to issues such as the vanish gradient and mode collapse. There have been many recent works which
+hypothesize a different loss function for the discriminator
+\cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}. We focus on the Wasserstein GAN
+(WGAN) \cite{arjovsky2017wasserstein} formulation, which proposes to use the Earth-Mover or \textit{Wasserstein-1}
+distance $W$ by constructing a value function using the Kantorovich-Rubinstein duality \cite{villani2008optimal}.
+In this formulation, $W$ is approximated given a set of $k$-Lipschitz functions $f$ modeled as neural networks. To
+ensure $f$ is $k$-Lipschitz, the weights of the discriminator are clipped to some range $[-c, c]$. In our work, we
+adopt the Wasserstein GAN with gradient penalty (WGAN-GP) \cite{gulrajani2017improved}, which instead of clipping
+network weights like in \cite{arjovsky2017wasserstein}, ensures the Lipschitz constraint by enforcing a soft
+constraint on the gradient norm of the discriminator's output with respect to its input. Following
+\cite{gulrajani2017improved}, our new objective then becomes
 
@@
 
-\noindent where $\mathbb{P}_{\hat{x}}$ is defined as samples along straight lines between pairs of points coming from the true data distribution
-and the generator distribution, and $\lambda$ is a weighing factor. In order to give $G$ some sense of ground truth, as well as capture low level
-frequencies in the image, we also consider the $L1$ loss
+\noindent where $\mathbb{P}_{\hat{x}}$ is defined as samples along straight lines between pairs of points coming from
+the true data distribution and the generator distribution, and $\lambda$ is a weighing factor. In order to give $G$
+some sense of ground truth, as well as capture low level frequencies in the image, we also consider the $L1$ loss
 
@@
 Often times generative models produce blurry images. We explore a strategy to sharpen these predictions by
-directly penalizing the differences of image gradient predictions in the generator, as proposed by \cite{mathieu2015deep}.
-Given a ground truth image $I^C$, predicted image $I^P = G(I^C)$, and $\alpha \geq 1$, the Gradient Difference Loss (GDL) is given by
+directly penalizing the differences of image gradient predictions in the generator, as proposed by
+\cite{mathieu2015deep}. Given a ground truth image $I^C$, predicted image $I^P = G(I^C)$, and $\alpha \geq 1$, the
+Gradient Difference Loss (GDL) is given by
 
@@
 structured as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.
-Encoder-decoder networks downsample (encode) the input via convolutions to a lower dimensional embedding, in which this embedding is then
-upsampled (decode) via transpose convolutions to reconstruct the image. The advantage of using a ``U-Net'' comes from explicitly preserving spatial
-dependencies produced by the encoder, as opposed to relying on the embedding to contain all of the information. This
-is done by the addition of ``skip connections'', which concatenate the activations produced from a convolution
-layer $i$ in the encoder to the input of a transpose convolution layer $n-i+1$ in the decoder, where $n$ is the
-total number of layers in the network. Each convolutional layer in our generator uses kernel size $4 \times 4$ with stride 2.
-Following \cite{radford2015unsupervised}, we use batch normalization \cite{pmlr-v37-ioffe15} throughout except for the last layer of the decoder.
+Encoder-decoder networks downsample (encode) the input via convolutions to a lower dimensional embedding, in which
+this embedding is then upsampled (decode) via transpose convolutions to reconstruct the image. The advantage of using
+a ``U-Net'' comes from explicitly preserving spatial dependencies produced by the encoder, as opposed to relying on the
+embedding to contain all of the information. This is done by the addition of ``skip connections'', which concatenate
+the activations produced from a convolution layer $i$ in the encoder to the input of a transpose convolution layer
+$n-i+1$ in the decoder, where $n$ is the total number of layers in the network. Each convolutional layer in our
+generator uses kernel size $4 \times 4$ with stride 2. Following \cite{radford2015unsupervised}, we use batch
+normalization \cite{pmlr-v37-ioffe15} throughout except for the last layer of the decoder.
 
-Our discriminator is modeled after that of \cite{radford2015unsupervised}, except no batch normalization is used. This is due
-to the fact that we penalize the norm of the discriminator's gradient with respect to each input individually, which batch
-normalization would invalidate. The authors of \cite{gulrajani2017improved} recommend layer normalization \cite{ba2016layer},
-but we found no significant improvements. RESULTS PENDING
-In all of our experiments, we use $\lambda_{L1} = 100$, batch size of 32, Adam Optimizer \cite{kingma2014adam} with learning rate $1e-4$, and train for 100 epochs.
-Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$. Our implementation was done
-using the Tensorflow library \cite{abadi2016tensorflow}.
+Our discriminator is modeled after that of \cite{radford2015unsupervised}, except no batch normalization is used. This
+is due to the fact that we penalize the norm of the discriminator's gradient with respect to each input individually,
+which batch normalization would invalidate. The authors of \cite{gulrajani2017improved} recommend layer normalization
+\cite{ba2016layer}, but we found no significant improvements. In all of our experiments, we use $\lambda_{L1} = 100$,
+batch size of 32, Adam Optimizer \cite{kingma2014adam} with learning rate $1e-4$, and train for 100 epochs.
+Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$. Our
+implementation was done using the Tensorflow library \cite{abadi2016tensorflow}.
 \footnote{Code is available at https://github.com/cameronfabbri/Underwater-Color-Correction}
@@
 \section{Experiments}
+\subsection{Datasets}
+We used several subsets of Imagenet \cite{deng2009imagenet} for training and evaluation of our methods. We also
+evaluate a tracking algorithm on a diving video taken from Youtube. Subsets of Imagenet containing underwater images
+were selected for the training of CycleGAN, and manually separated into two classes. We let $X$ be the set of
+underwater images with no distortion, and $Y$ be the set of underwater images with distortion. $X$ contained 6143
+images, and $Y$ contained 1817 images. We then trained CycleGAN to learn the mapping $F: X \rightarrow Y$, such that
+images from $X$ appeared to have come from $Y$. Finally, our image pairs for training data were generated by distorting
+all images in $X$ with $F$. Figure 2 shows sample training pairs.
 
+\subsection{Evaluation}
+We trained UGAN and UGAN-P on the image pairs generated by CycleGAN, and evaluated on the images from the test set, $Y$.
+Note that these images do not contain any ground truth, as they are original distorted images from Imagenet. Images for
+training and testing are of size $256 \times 256 \times 3$ and normalized between $[-1, 1]$.
+
+\subsection{Comparison to CycleGAN}
+
+It is important to note that during the process of learning a mapping $F: X \rightarrow Y$, CycleGAN also learns a
+mapping $G: Y \rightarrow X$. Here we show that UGAN and UGAN-P provide superior performance.
 Here I want to show a number of things. First talk about the datasets used, Imagenet and the diving videos.
@@
 ours are better by showing results from Canny Edge Detector.
+
+\subsection{Diver Tracking}
 

### 2017-09-11 svm.py

@@ -1,0 +1,197 @@
+'''
+
+   Testing the features learned by the discriminator.
+
+   This will take the features from the discriminator and attempt to classify
+   images.
+
+'''
+
+import cPickle as pickle
+import tensorflow as tf
+from scipy import misc
+from tqdm import tqdm
+import numpy as np
+import argparse
+import random
+import ntpath
+import sys
+import os
+import time
+import glob
+import cPickle as pickle
+from tqdm import tqdm
+
+sys.path.insert(0, 'ops/')
+sys.path.insert(0, 'nets/')
+from tf_ops import *
+import data_ops
+
+def netD_feature(x, LAYER_NORM, LOSS_METHOD, reuse=False):
+   print
+   print 'netD'
+
+   sc = tf.get_variable_scope()
+   with tf.variable_scope(sc, reuse=reuse):
+
+      conv1 = tcl.conv2d(x, 64, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='d_conv1')
+      if LOSS_METHOD != 'wgan': conv1 = tcl.batch_norm(conv1)
+      elif LOSS_METHOD == 'wgan' and LAYER_NORM: conv1 = tcl.layer_norm(conv1)
+      conv1 = lrelu(conv1)
+      
+      conv2 = tcl.conv2d(conv1, 128, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='d_conv2')
+      if LOSS_METHOD != 'wgan': conv2 = tcl.batch_norm(conv2)
+      elif LOSS_METHOD == 'wgan' and LAYER_NORM: conv2 = tcl.layer_norm(conv2)
+      conv2 = lrelu(conv2)
+      
+      conv3 = tcl.conv2d(conv2, 256, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='d_conv3')
+      if LOSS_METHOD != 'wgan': conv3 = tcl.batch_norm(conv3)
+      elif LOSS_METHOD == 'wgan' and LAYER_NORM: conv3 = tcl.layer_norm(conv3)
+      conv3 = lrelu(conv3)
+      
[…]

### 2017-09-11 tests/edge_detection.py

@@ -24,7 +24,8 @@ cgan_dist   = []
 ugan_0_dist = []
 ugan_1_dist = []
 
-save_images = ['n02607072_4739.png', 'n01496331_15872.png', 'n01496331_22079.png']
+#save_images = ['n02607072_4739.png', 'n01496331_15872.png', 'n01496331_22079.png']
+save_images = ['n01496331_15872.png']
 
 largest = 0
 l_img = ''

### 2017-09-11 files/paper/paper.tex
update

@@
 \and
-\IEEEauthorblockN{Md Jahidul Muslim}
+\IEEEauthorblockN{Md Jahidul Islam}
 \IEEEauthorblockA{UMN\\}
@@
 \subsection{Network Architecture and Training Details}
-Our generator network uses an encoder-decoder structure similar to the work of \cite{isola2016image}, which is
-structured as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.
+Our generator network is a fully convolutional encoder-decoder, similar to the work of \cite{isola2016image}, which is
+designed as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.
 Encoder-decoder networks downsample (encode) the input via convolutions to a lower dimensional embedding, in which
@@
 $n-i+1$ in the decoder, where $n$ is the total number of layers in the network. Each convolutional layer in our
-generator uses kernel size $4 \times 4$ with stride 2. Following \cite{radford2015unsupervised}, we use batch
-normalization \cite{pmlr-v37-ioffe15} throughout except for the last layer of the decoder.
+generator uses kernel size $4 \times 4$ with stride 2. Convolutions in the encoder portion of the network are followed
+by a leaky ReLU activation with slope $0.02$, while transpose convolutions in the encoder are followed by a ReLU
+activation \cite{nair2010rectified}. Excempt from this is the last layer of the decoder, which uses a TanH nonlinearity
+to match the input distribution of $[-1, 1]$. Following \cite{radford2015unsupervised}, we use batch normalization
+\cite{pmlr-v37-ioffe15} throughout the generator, except for the last layer of the decoder.
 

### 2017-09-11 tests/num_classes.py
update

@@ -1,0 +1,16 @@
+import glob
+import ntpath
+
+image_files = glob.glob('test_images/ugan_1.0/*.png')
+
+classes = []
+
+for i in image_files:
+   i = ntpath.basename(i)
+   img = i.split('_')[0]
+
+   classes.append(img)
+
+
+print len(set(classes))
+

### 2017-09-12 nets/pix2pix.py
updates

@@ -42,6 +42,7 @@ def netG(x, LOSS_METHOD):
    print 'enc_conv8:',enc_conv8
    print
 
+   '''
    dec_conv1 = tcl.convolution2d_transpose(enc_conv8, 512, 4, 2, activation_fn=tf.nn.relu, normalizer_fn=tcl.batch_norm, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_dec_conv1')
    dec_conv1 = tf.concat([dec_conv1, enc_conv7], axis=3)
    print 'dec_conv1:',dec_conv1
@@ -71,6 +72,55 @@ def netG(x, LOSS_METHOD):
    print 'dec_conv7:',dec_conv7
    
    dec_conv8 = tcl.convolution2d_transpose(dec_conv7, 3, 4, 2, activation_fn=tf.tanh, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_dec_conv8')
+   print 'dec_conv8', dec_conv8
+   
+   return dec_conv8
+   '''
+   dec_conv1 = tcl.convolution2d_transpose(enc_conv8, 512, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_dec_conv1')
+   if LOSS_METHOD != 'wgan': dec_conv1 = tcl.batch_norm(dec_conv1)
+   dec_conv1 = relu(dec_conv1)
+   dec_conv1 = tf.concat([dec_conv1, enc_conv7], axis=3)
+   print 'dec_conv1:',dec_conv1
+
+   dec_conv2 = tcl.convolution2d_transpose(dec_conv1, 512, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_dec_conv2')
+   if LOSS_METHOD != 'wgan': dec_conv2 = tcl.batch_norm(dec_conv2)
+   dec_conv2 = relu(dec_conv2)
+   dec_conv2 = tf.concat([dec_conv2, enc_conv6], axis=3)
+   print 'dec_conv2:',dec_conv2
+   
+   dec_conv3 = tcl.convolution2d_transpose(dec_conv2, 512, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_dec_conv3')
[…]

### 2017-09-12 eval.py
update

@@ -20,6 +20,7 @@ import ntpath
 import sys
 import os
 import time
+import time
 import glob
 import cPickle as pickle
 from tqdm import tqdm
@@ -154,8 +155,10 @@ if __name__ == '__main__':
       a_img = data_ops.preprocess(a_img)
       batch_images[0, ...] = a_img
 
+      #s = time.time()
       gen_images = np.asarray(sess.run(gen_image, feed_dict={image_u:batch_images}))
-
+      #print time.time()-s
+      #exit()
       for gen, real in zip(gen_images, batch_images):
          #misc.imsave(IMAGES_DIR+str(step)+'_'+str(c)+'_real.png', real)
          #misc.imsave(IMAGES_DIR+str(step)+'_'+str(c)+'_gen.png', gen)

### 2017-09-12 train.py
adding more models to keep

@@ -168,7 +168,7 @@ if __name__ == '__main__':
    G_train_op = tf.train.AdamOptimizer(learning_rate=LEARNING_RATE).minimize(errG, var_list=g_vars, global_step=global_step)
    D_train_op = tf.train.AdamOptimizer(learning_rate=LEARNING_RATE).minimize(errD, var_list=d_vars)
 
-   saver = tf.train.Saver(max_to_keep=1)
+   saver = tf.train.Saver(max_to_keep=2)
 
    init = tf.group(tf.local_variables_initializer(), tf.global_variables_initializer())
    sess = tf.Session()

### 2017-09-12 _train.sh
update

@@ -1,1 +1,1 @@
-python train.py --DATA=underwater_imagenet --EPOCHS=100 --NETWORK=pix2pix --IG_WEIGHT=0.0 --L1_WEIGHT=100.0 --BATCH_SIZE=32 --LOSS_METHOD=wgan --LEARNING_RATE=1e-4
+python train.py --DATA=underwater_imagenet --EPOCHS=100 --NETWORK=pix2pix --L1_WEIGHT=100 --BATCH_SIZE=32 --IG_WEIGHT=0.0 --LEARNING_RATE=1e-4 --LOSS_METHOD=wgan

### 2017-09-12 eval.py
update

@@ -1,11 +1,6 @@
 '''
 
-   Main training file
-
-   The goal is to correct the colors in underwater images.
-   CycleGAN was used to create images that appear to be underwater.
-   Those will be sent into the generator, which will attempt to correct the
-   colors.
+   Evaluation File
 
 '''
 
@@ -58,7 +53,6 @@ if __name__ == '__main__':
                      +'/DATA_'+DATA+'/'\
 
    IMAGES_DIR     = EXPERIMENT_DIR+'test_images/'
-   #IMAGES_DIR     = EXPERIMENT_DIR+'diving1/'
 
    print
    print 'Creating',IMAGES_DIR
@@ -114,34 +108,8 @@ if __name__ == '__main__':
 
    print 'num test:',num_test
 
-   '''
-   while True:
-
-      idx = np.random.choice(np.arange(num_test), BATCH_SIZE, replace=False)
-      batch_paths = test_paths[idx]
-      
-      batch_images = np.empty((BATCH_SIZE, 256, 256, 3), dtype=np.float32)
-
-      i = 0
-      print 'Loading batch...'
-      for a in tqdm(batch_paths):
-         a_img = misc.imread(a).astype('float32')
-         a_img = misc.imresize(a_img, (256, 256, 3))
-         a_img = data_ops.preprocess(a_img)
-         batch_images[i, ...] = a_img
-         i += 1
-
-      gen_images = np.asarray(sess.run(gen_image, feed_dict={image_u:batch_images}))
-
-      c = 0
-      for gen, real in zip(gen_images, batch_images):
-         misc.imsave(IMAGES_DIR+str(step)+'_'+str(c)+'_real.png', real)
-         misc.imsave(IMAGES_DIR+str(step)+'_'+str(c)+'_gen.png', gen)
-         c += 1
-      exit()
-   '''
-
    c = 0
+   times = []
    for img_path in tqdm(test_paths):
 
       img_name = ntpath.basename(img_path)
@@ -155,10 +123,12 @@ if __name__ == '__main__':
       a_img = data_ops.preprocess(a_img)
       batch_images[0, ...] = a_img
 
-      #s = time.time()
+      s = time.time()
       gen_images = np.asarray(sess.run(gen_image, feed_dict={image_u:batch_images}))
-      #print time.time()-s
-      #exit()
+      tot = time.time()-s
+      
+      times.append(tot)
+
[…]

### 2017-09-12 tests/createImages.py
update

@@ -1,59 +1,0 @@
-'''
-
-Script to create a nxm matrix of images
-
-'''
-
-import cv2
-import numpy as np
-import scipy.misc as misc
-from glob import glob
-
-if __name__ == '__main__':
-
-   n = 2 # cols
-   m = 4  # rows
-
-   num_images = n*m
-
-   img_size = (256, 256, 3)
-
-   canvas = 255*np.ones((m*img_size[0]+(10*m)+10, n*img_size[1]+(10*n)+10, 3), dtype=np.uint8)
-
-   start_x = 10
-   start_y = 10
-
-   x = 0
-   y = 0
-
-   image_paths = sorted(glob('result_images/*.png'))
-
-   count = 0
-   for impath in image_paths:
-
-      print impath
-      if count == 7: break
-      count += 1
-   exit()
-
-   for img in gen_imgs:
-
-      end_x = start_x+256
-      end_y = start_y+256
-      
-      canvas[start_y:end_y, start_x:end_x, :] = img
-
-      if x < n:
-         start_x += 256+10
-         x += 1
-      if x == n:
-         x       = 0
-         start_x = 10
-         start_y = end_y + 10
-         end_y   = start_y+256
-
-   misc.imsave('results.png', canvas)
-   #cv2.imwrite('results.jpg', canvas)
-   #cv2.imshow('canvas', canvas)
-   #cv2.waitKey(0)
-   #cv2.destroyAllWindows()

### 2017-09-12 tests/inception_score.py

@@ -24,7 +24,7 @@ softmax = None
 
 # Call this function with list of images. Each of elements should be a 
 # numpy array with values ranging from 0 to 255.
-def get_inception_score(images, splits=7):
+def get_inception_score(images, splits=10):
    assert(type(images) == list)
    assert(type(images[0]) == np.ndarray)
    assert(len(images[0].shape) == 3)
@@ -102,17 +102,20 @@ if softmax is None:
   
    # get images
    import glob
-   real_paths  = glob.glob('/home/fabbric/Research/colorCorrection/datasets/underwater_imagenet/test/*.jpg')[:1800]
-   ugan_paths  = glob.glob('/home/fabbric/Research/colorCorrection/checkpoints/LOSS_METHOD_wgan/NETWORK_pix2pix/PixS_False/L1_WEIGHT_100.0/IG_WEIGHT_0.0/DATA_underwater_imagenet/test_images/*gen.png')[:1800]
+   real_paths  = glob.glob('/home/fabbric/Research/ugan/datasets/underwater_imagenet/test/*.jpg')[:1800]
+   ugan0_paths = glob.glob('/home/fabbric/Research/ugan/tests/test_images/ugan_0.0/*.png')[:1800]
+   ugan1_paths = glob.glob('/home/fabbric/Research/ugan/tests/test_images/ugan_1.0/*.png')[:1800]
    cycle_paths = glob.glob('/home/fabbric/Research/CycleGAN-tensorflow/testA/*.png')[:1800]
 
    print(len(real_paths))
-   print(len(ugan_paths))
+   print(len(ugan0_paths))
+   print(len(ugan1_paths))
    print(len(cycle_paths))
    
    cycle_images = []
-   ugan_images = []
-   real_images = []
+   ugan0_images = []
+   ugan1_images = []
+   real_images  = []
 
    for i in real_paths:
       i = misc.imread(i)
@@ -122,15 +125,30 @@ if softmax is None:
    for i in cycle_paths:
       cycle_images.append(misc.imread(i))
    
-   for i in ugan_paths:
-      ugan_images.append(misc.imread(i))
+   for i in ugan0_paths:
+      ugan0_images.append(misc.imread(i))
+   
+   for i in ugan1_paths:
+      ugan1_images.append(misc.imread(i))
 
    _init_inception()
    
-   ugan_mean_scores, ugan_std_scores = get_inception_score(ugan_images)
-   print('Got ugan mean scores')
-   print(ugan_mean_scores)
[…]

### 2017-09-12 tests/old_images/temp.py

@@ -1,0 +1,25 @@
+import numpy as np
+from skimage.measure import compare_ssim as ssim
+from skimage.measure import compare_psnr as psnr
+import scipy.misc as misc
+import scipy.stats.signaltonoise as snr
+
+
+
+real_img  = misc.imread('n01496331_11938_real.png')
+cycle_gan = misc.imread('n01496331_11938.png')
+ours      = misc.imread('n01496331_11938_gen_IG_0.0.png')
+'''
+print ssim(real_img, cycle_gan, multichannel=True)
+print ssim(real_img, ours, multichannel=True)
+print
+print psnr(real_img, cycle_gan)
+print psnr(real_img, ours)
+'''
+
+#print np.linalg.norm(np.fft.fftn(real_img))
+#print np.linalg.norm(np.fft.fftn(cycle_gan))
+#print np.linalg.norm(np.fft.fftn(ours))
+
+print snr(cycle_gan)
+

### 2017-09-12 tests/zoom.py
update

@@ -1,0 +1,17 @@
+'''
+
+   Script to zoom in on parts of an image and save out
+
+'''
+
+import scipy.misc as misc
+import numpy as np
+import sys
+
+
+img = misc.imread(sys.argv[1])
+
+crop = img[200:250, 200:250, :]
+
+misc.imsave('crop.png', crop)
+

### 2017-09-12 tests/ren.sh
update

@@ -1,0 +1,11 @@
+# eval.py spits out images called n*_gen.png and n*_real.png
+# This script renames them to scrap the real and gen in the test images folder
+
+
+rm test_images/ugan_0.0/*real*
+rm test_images/ugan_1.0/*real*
+
+rename 's/_gen//' test_images/ugan_0.0/*
+rename 's/_gen//' test_images/ugan_1.0/*
+
+

### 2017-09-12 tests/zoom.py

@@ -9,9 +9,34 @@ import numpy as np
 import sys
 
 
-img = misc.imread(sys.argv[1])
+img = 'n01496331_15872.png'
 
-crop = img[200:250, 200:250, :]
+root = 'test_images/'
 
-misc.imsave('crop.png', crop)
+dirs = ['cgan/', 'original/', 'ugan_0.0/', 'ugan_1.0/']
 
+for d in dirs:
+   img = misc.imread(root+d+img)
+
+   y1 = 160
+   y2 = 200
+   x1 = 210
+   x2 = 250
+
+
+   # row, column (y, x), (0,0) at top left
+   crop = img[y1:y2, x1:x2, :]
+
+   crop = misc.imresize(crop, (64, 64))
+   misc.imsave('crop1.png', crop)
+   # draw box around cropped area
+   # left
+   img[y1:y2, x1, :] = [255, 0, 0]
+   # top
+   img[y1, x1:x2, :] = [255, 0, 0]
+   # bottom
+   img[y2, x1:x2, :] = [255, 0, 0]
+   # right
+   img[y1:y2, x2, :] = [255, 0, 0]
+
+   misc.imsave('og.png', img)

### 2017-09-12 tests/zoom.py
update

@@ -9,20 +9,19 @@ import numpy as np
 import sys
 
 
-img = 'n01496331_15872.png'
-
+img  = 'n01496331_15872.png'
+name = img.split('.')[0]
 root = 'test_images/'
-
 dirs = ['cgan/', 'original/', 'ugan_0.0/', 'ugan_1.0/']
 
 for d in dirs:
+
    img = misc.imread(root+d+img)
 
    y1 = 160
    y2 = 200
    x1 = 210
    x2 = 250
-
 
    # row, column (y, x), (0,0) at top left
    crop = img[y1:y2, x1:x2, :]

### 2017-09-12 tests/zoom.py
update

@@ -16,7 +16,7 @@ dirs = ['cgan/', 'original/', 'ugan_0.0/', 'ugan_1.0/']
 
 for d in dirs:
 
-   img = misc.imread(root+d+img)
+   image = misc.imread(root+d+img)
 
    y1 = 160
    y2 = 200
@@ -24,18 +24,18 @@ for d in dirs:
    x2 = 250
 
    # row, column (y, x), (0,0) at top left
-   crop = img[y1:y2, x1:x2, :]
+   crop = image[y1:y2, x1:x2, :]
 
    crop = misc.imresize(crop, (64, 64))
-   misc.imsave('crop1.png', crop)
+   misc.imsave(name+'_'+d.split('/')[0]+'_crop.png', crop)
    # draw box around cropped area
    # left
-   img[y1:y2, x1, :] = [255, 0, 0]
+   image[y1:y2, x1, :] = [255, 0, 0]
    # top
-   img[y1, x1:x2, :] = [255, 0, 0]
+   image[y1, x1:x2, :] = [255, 0, 0]
    # bottom
-   img[y2, x1:x2, :] = [255, 0, 0]
+   image[y2, x1:x2, :] = [255, 0, 0]
    # right
-   img[y1:y2, x2, :] = [255, 0, 0]
+   image[y1:y2, x2, :] = [255, 0, 0]
 
-   misc.imsave('og.png', img)
+   misc.imsave(name+'_'+d.split('/')[0]+'.png', image)

### 2017-09-12 files/paper/paper.tex
update

@@
 Encoder-decoder networks downsample (encode) the input via convolutions to a lower dimensional embedding, in which
-this embedding is then upsampled (decode) via transpose convolutions to reconstruct the image. The advantage of using
+this embedding is then upsampled (decode) via transpose convolutions to reconstruct an image. The advantage of using
 a ``U-Net'' comes from explicitly preserving spatial dependencies produced by the encoder, as opposed to relying on the
@@
 generator uses kernel size $4 \times 4$ with stride 2. Convolutions in the encoder portion of the network are followed
-by a leaky ReLU activation with slope $0.02$, while transpose convolutions in the encoder are followed by a ReLU
-activation \cite{nair2010rectified}. Excempt from this is the last layer of the decoder, which uses a TanH nonlinearity
-to match the input distribution of $[-1, 1]$. Following \cite{radford2015unsupervised}, we use batch normalization
-\cite{pmlr-v37-ioffe15} throughout the generator, except for the last layer of the decoder.
+by batch normalization \cite{pmlr-v37-ioffe15} and a leaky ReLU activation with slope $0.02$, while transpose
+convolutions in the decoder are followed by a ReLU activation \cite{nair2010rectified} (no batch norm in the decoder).
+Exempt from this is the last
+layer of the decoder, which uses a TanH nonlinearity to match the input distribution of $[-1, 1]$. 
+%Batch normalization \cite{pmlr-v37-ioffe15} is used in the encoder portion
+%of the generator, but not in the decoder.
+%Following \cite{radford2015unsupervised}, we use batch normalization
+%\cite{pmlr-v37-ioffe15} throughout the generator, except for the last layer of the decoder.
 
@@
 \cite{ba2016layer}, but we found no significant improvements. In all of our experiments, we use $\lambda_{L1} = 100$,
-batch size of 32, Adam Optimizer \cite{kingma2014adam} with learning rate $1e-4$, and train for 100 epochs.
-Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$. Our
-implementation was done using the Tensorflow library \cite{abadi2016tensorflow}.
+$\lambda_{GP} = 10$, batch size of 32, Adam Optimizer \cite{kingma2014adam} with learning rate $1e-4$, and train for 100 epochs.
+Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$.
+For UGAN-P, we set $\lambda_{IG} = 1.0$.
+Our implementation was done using the Tensorflow library \cite{abadi2016tensorflow}.
 \footnote{Code is available at https://github.com/cameronfabbri/Underwater-Color-Correction}
@@
 \subsection{Evaluation}
-We trained UGAN and UGAN-P on the image pairs generated by CycleGAN, and evaluated on the images from the test set, $Y$.
-Note that these images do not contain any ground truth, as they are original distorted images from Imagenet. Images for
-training and testing are of size $256 \times 256 \times 3$ and normalized between $[-1, 1]$.
+We trained UGAN and UGAN-P on the image pairs generated by CycleGAN, and evaluated entirely on the images from the
+test set, $Y$. Note that these images do not contain any ground truth, as they are original distorted images from
+Imagenet. Images for training and testing are of size $256 \times 256 \times 3$ and normalized between $[-1, 1]$.
+
+%\footnote{Code for inception score can be found at https://github.com/openai/improved-gan}
+%\begin{center}
+%\begin{tabular}{c c c c c c}
+%Samples & real & ugan & ugan-p & cyclegan \\ \hline
+%Model & True Images & UGAN & UGAN-P & CycleGAN \\ \hline
+%Score $\pm$ std. & $5.69 \pm 0.23$ & $6.18 \pm 0.35$ & $6.30 \pm 0.32$ & $6.37 \pm 0.43$ \\ \hline
+%\end{tabular}
+%\end{center}
 

### 2017-09-12 eval.py

@@ -132,8 +132,8 @@ if __name__ == '__main__':
       for gen, real in zip(gen_images, batch_images):
          #misc.imsave(IMAGES_DIR+str(step)+'_'+str(c)+'_real.png', real)
          #misc.imsave(IMAGES_DIR+str(step)+'_'+str(c)+'_gen.png', gen)
-         misc.imsave(IMAGES_DIR+img_name+'_real.jpg', real)
-         misc.imsave(IMAGES_DIR+img_name+'_gen.jpg', gen)
+         misc.imsave(IMAGES_DIR+img_name+'_real.png', real)
+         misc.imsave(IMAGES_DIR+img_name+'_gen.png', gen)
 
          c += 1
 

### 2017-09-12 tests/zoom.py
zoom file is finished, just waiting on data

@@ -18,16 +18,15 @@ for d in dirs:
 
    image = misc.imread(root+d+img)
 
+   #########################################################
    y1 = 160
    y2 = 200
    x1 = 210
    x2 = 250
-
    # row, column (y, x), (0,0) at top left
    crop = image[y1:y2, x1:x2, :]
-
    crop = misc.imresize(crop, (64, 64))
-   misc.imsave(name+'_'+d.split('/')[0]+'_crop.png', crop)
+   misc.imsave(name+'_'+d.split('/')[0]+'_crop_1.png', crop)
    # draw box around cropped area
    # left
    image[y1:y2, x1, :] = [255, 0, 0]
@@ -38,4 +37,33 @@ for d in dirs:
    # right
    image[y1:y2, x2, :] = [255, 0, 0]
 
+
+   #########################################################
+   y1 = 225
+   y2 = 245
+   x1 = 80
+   x2 = 100
+   crop = image[y1:y2, x1:x2, :]
+   crop = misc.imresize(crop, (64, 64))
+   misc.imsave(name+'_'+d.split('/')[0]+'_crop_2.png', crop)
+   image[y1:y2, x1, :] = [0, 0, 255]
+   image[y1, x1:x2, :] = [0, 0, 255]
+   image[y2, x1:x2, :] = [0, 0, 255]
+   image[y1:y2, x2, :] = [0, 0, 255]
+   
+   
+   #########################################################
+   y1 = 118
+   y2 = 128
+   x1 = 40
+   x2 = 50
+   crop = image[y1:y2, x1:x2, :]
+   crop = misc.imresize(crop, (64, 64))
+   misc.imsave(name+'_'+d.split('/')[0]+'_crop_3.png', crop)
+   image[y1:y2, x1, :] = [0, 255, 0]
+   image[y1, x1:x2, :] = [0, 255, 0]
+   image[y2, x1:x2, :] = [0, 255, 0]
+   image[y1:y2, x2, :] = [0, 255, 0]
    misc.imsave(name+'_'+d.split('/')[0]+'.png', image)
+
+

### 2017-09-12 files/paper/paper.tex
update

@@
 \section{Introduction}
-TODO - talk about having to go back to the same location if you want to get good/bad pairs of the "same" image.
+TODO - talk about having to go back to the same location if you want to get good/bad pairs of the ``same'' image.
 Vision is a commonly used sensor in autonomous underwater robots due to its non-intrusive, passive, and energy
@@
 
-   \includegraphics[width=0.8in]{n01496331_175_B} &
-   \includegraphics[width=0.8in]{n01664065_4022_B} &
-   \includegraphics[width=0.8in]{n01917289_889_B} &
-   \includegraphics[width=0.8in]{n01914609_116_B} \\
-   \includegraphics[width=0.8in]{n01496331_175_A} &
-   \includegraphics[width=0.8in]{n01664065_4022_A} &
-   \includegraphics[width=0.8in]{n01917289_889_A} &
-   \includegraphics[width=0.8in]{n01914609_116_A} \\
+   \includegraphics[width=0.8in]{n01496331_873_X} &
+   \includegraphics[width=0.8in]{n01664065_4022_X} &
+   \includegraphics[width=0.8in]{n01917289_889_X} &
+   \includegraphics[width=0.8in]{n01914609_116_X} \\
+   \includegraphics[width=0.8in]{n01496331_873_Y} &
+   \includegraphics[width=0.8in]{n01664065_4022_Y} &
+   \includegraphics[width=0.8in]{n01917289_889_Y} &
+   \includegraphics[width=0.8in]{n01914609_116_Y} \\
 
@@
    \mathcal{L}_{WGAN}(G,D) = \mathbb{E} [D(I^C)] - \mathbb{E} & [D(G(I^D))] + \\
-   \lambda \mathbb{E} & _{\hat{x} \sim \mathbb{P}_{\hat{x}}} [(|| \nabla_{\hat{x}} D(\hat{x})||_2 -1)^2 ],
+   \lambda_{GP} \mathbb{E} & _{\hat{x} \sim \mathbb{P}_{\hat{x}}} [(|| \nabla_{\hat{x}} D(\hat{x})||_2 -1)^2 ],
 \end{aligned}
@@
 \noindent where $\mathbb{P}_{\hat{x}}$ is defined as samples along straight lines between pairs of points coming from
-the true data distribution and the generator distribution, and $\lambda$ is a weighing factor. In order to give $G$
+the true data distribution and the generator distribution, and $\lambda_{GP}$ is a weighing factor. In order to give $G$
 some sense of ground truth, as well as capture low level frequencies in the image, we also consider the $L1$ loss
@@
    \begin{aligned}
-      \mathcal{L}_{UGAN}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + \mathcal{L}_{L1}(G).
+      \mathcal{L}_{UGAN}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + \lambda_{1} \mathcal{L}_{L1}(G).
    \end{aligned}
@@
    \begin{aligned}
-      \mathcal{L}_{UGAN}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + \mathcal{L}_{L1}(G) + \mathcal{L}_{GDL}
+      \mathcal{L}_{UGAN}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + \lambda_{1} \mathcal{L}_{L1}(G) +  \lambda_{2} \mathcal{L}_{GDL}
    \end{aligned}
@@
 which batch normalization would invalidate. The authors of \cite{gulrajani2017improved} recommend layer normalization
-\cite{ba2016layer}, but we found no significant improvements. In all of our experiments, we use $\lambda_{L1} = 100$,
+\cite{ba2016layer}, but we found no significant improvements. In all of our experiments, we use $\lambda_{1} = 100$,
 $\lambda_{GP} = 10$, batch size of 32, Adam Optimizer \cite{kingma2014adam} with learning rate $1e-4$, and train for 100 epochs.
 Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$.
-For UGAN-P, we set $\lambda_{IG} = 1.0$.
+For UGAN-P, we set $\lambda_{2} = 1.0$.
 Our implementation was done using the Tensorflow library \cite{abadi2016tensorflow}.
@@
 
-%\footnote{Code for inception score can be found at https://github.com/openai/improved-gan}
+While many of the distorted images in the test set contain a blue or green hue, that is not always the case. In certain
+environments, it is possible that objects close to the camera are undistorted with correct colors, while the background
+of the image contains distortion. In these cases, we would like the network to only correct parts of the image that
+appear distorted. Figure X shows a sample of such an image, which implies it does not simply subtract a variable
+amount of green or blue from the entire image.
+
+% Directly from the first paper on the inception score: We find that it’s important to evaluate the metric on a large
+% enough number of samples (i.e. 50k) as part of this metric measures diversity.
+% % Therefore we should not include it I think
+% \footnote{Code for inception score can be found at https://github.com/openai/improved-gan}
 %\begin{center}
@@
 \subsection{Comparison to CycleGAN}
-
+\textbf{note also this is on cyclegan's training set - retraining now with a test set in mind....should be quick.}
 It is important to note that during the process of learning a mapping $F: X \rightarrow Y$, CycleGAN also learns a
 mapping $G: Y \rightarrow X$. Here we show that UGAN and UGAN-P provide superior performance.
-Here I want to show a number of things. First talk about the datasets used, Imagenet and the diving videos.
 Second, show some general results. Explain how our network is able to do three very important things: 1) Restore an
@@
 
-   \includegraphics[width=0.8in]{n01496331_15872_original} &
-   \includegraphics[width=0.8in]{n01496331_15872_cimg}     &
-   \includegraphics[width=0.8in]{n01496331_15872_u0img}    &
-   \includegraphics[width=0.8in]{n01496331_15872_u1img}    \\ [-1ex]
-   \includegraphics[width=0.8in]{n01496331_15872_oedges}   &
-   \includegraphics[width=0.8in]{n01496331_15872_cedges}   &
-   \includegraphics[width=0.8in]{n01496331_15872_u0edges}  &
-   \includegraphics[width=0.8in]{n01496331_15872_u1edges}  \\
+%   \includegraphics[width=0.8in]{n01496331_15872_original} &
+%   \includegraphics[width=0.8in]{n01496331_15872_cimg}     &
+%   \includegraphics[width=0.8in]{n01496331_15872_u0img}    &
+%   \includegraphics[width=0.8in]{n01496331_15872_u1img}    \\ [-1ex]
+%   \includegraphics[width=0.8in]{n01496331_15872_oedges}   &
+%   \includegraphics[width=0.8in]{n01496331_15872_cedges}   &
+%   \includegraphics[width=0.8in]{n01496331_15872_u0edges}  &
+%   \includegraphics[width=0.8in]{n01496331_15872_u1edges}  \\
    0 & \small{125.78} & \small{80.68} & \small{78.49} \\
 
-   \includegraphics[width=0.8in]{n01496331_22079_original} &
-   \includegraphics[width=0.8in]{n01496331_22079_cimg}     & 
-   \includegraphics[width=0.8in]{n01496331_22079_u0img}    &
-   \includegraphics[width=0.8in]{n01496331_22079_u1img}    \\ [-1ex]
-   \includegraphics[width=0.8in]{n01496331_22079_oedges}   &
-   \includegraphics[width=0.8in]{n01496331_22079_cedges}   &
-   \includegraphics[width=0.8in]{n01496331_22079_u0edges}  &
-   \includegraphics[width=0.8in]{n01496331_22079_u1edges}  \\
+%   \includegraphics[width=0.8in]{n01496331_22079_original} &
+%   \includegraphics[width=0.8in]{n01496331_22079_cimg}     & 
+%   \includegraphics[width=0.8in]{n01496331_22079_u0img}    &
+%   \includegraphics[width=0.8in]{n01496331_22079_u1img}    \\ [-1ex]
+%   \includegraphics[width=0.8in]{n01496331_22079_oedges}   &
+%   \includegraphics[width=0.8in]{n01496331_22079_cedges}   &
+%   \includegraphics[width=0.8in]{n01496331_22079_u0edges}  &
+%   \includegraphics[width=0.8in]{n01496331_22079_u1edges}  \\
    0 & \small{94.57} & \small{38.22} & \small{37.29} \\
 
-   \includegraphics[width=0.8in]{n02607072_4739_original} &
-   \includegraphics[width=0.8in]{n02607072_4739_cimg} &
-   \includegraphics[width=0.8in]{n02607072_4739_u0img} &
-   \includegraphics[width=0.8in]{n02607072_4739_u1img} \\ [-1ex]
-   \includegraphics[width=0.8in]{n02607072_4739_oedges} &
-   \includegraphics[width=0.8in]{n02607072_4739_cedges} &
-   \includegraphics[width=0.8in]{n02607072_4739_u0edges} &
-   \includegraphics[width=0.8in]{n02607072_4739_u1edges} \\
+%   \includegraphics[width=0.8in]{n02607072_4739_original} &
+%   \includegraphics[width=0.8in]{n02607072_4739_cimg} &
+%   \includegraphics[width=0.8in]{n02607072_4739_u0img} &
+%   \includegraphics[width=0.8in]{n02607072_4739_u1img} \\ [-1ex]
+%   \includegraphics[width=0.8in]{n02607072_4739_oedges} &
+%   \includegraphics[width=0.8in]{n02607072_4739_cedges} &
+%   \includegraphics[width=0.8in]{n02607072_4739_u0edges} &
+%   \includegraphics[width=0.8in]{n02607072_4739_u1edges} \\
    0 & \small{100.69} & \small{87.81} & \small{87.95} \\
@@
 
-%
-%\begin{thebibliography}{1}
-%\bibitem{hires}{Johnson‐Roberson, Matthew, et al.
-"High‐Resolution Underwater Robotic Vision‐Based Mapping and Three‐Dimensional Reconstruction for Archaeology." Journal of Field Robotics 34.4 (2017): 625-643.}
-%
-%\bibitem{col1}{Zhang, Richard, Phillip Isola, and Alexei A. Efros. "Colorful image colorization." European Conference on Computer Vision. Springer International Publishing, 2016.}
-
-%\bibitem{col2}{Cheng, Zezhou, Qingxiong Yang, and Bin Sheng. "Deep colorization." Proceedings of the IEEE International Conference on Computer Vision. 2015.}
-
-%\bibitem{col3}{Iizuka, Satoshi, Edgar Simo-Serra, and Hiroshi Ishikawa.
-"Let there be color!: joint end-to-end learning of global and local image priors for automatic image colorization with simultaneous classification." ACM Transactions on Graphics (TOG) 35.4 (2016): 110.}
-
-%\bibitem{pix2pix}{Isola, Phillip, et al. "Image-to-image translation with conditional adversarial networks." arXiv preprint arXiv:1611.07004 (2016).}
-
-%\bibitem{watergan}{Li, Jie, et al. "WaterGAN: Unsupervised Generative Network to Enable Real-time Color Correction of Monocular Underwater Images." arXiv preprint arXiv:1702.07392 (2017).}
-
-%\end{thebibliography}
-
-%\bibliography{/home/fabbric/Research/colorCorrection/files/paper/cambibs}
 \bibliography{cambibs}
@@
 
-% that's all folks
 \end{document}

### 2017-09-12 tests/zoom.py
update

@@ -26,16 +26,12 @@ for d in dirs:
    # row, column (y, x), (0,0) at top left
    crop = image[y1:y2, x1:x2, :]
    crop = misc.imresize(crop, (64, 64))
-   misc.imsave(name+'_'+d.split('/')[0]+'_crop_1.png', crop)
+   misc.imsave('result_images/'+name+'_'+d.split('/')[0]+'_crop_1.png', crop)
    # draw box around cropped area
-   # left
-   image[y1:y2, x1, :] = [255, 0, 0]
-   # top
-   image[y1, x1:x2, :] = [255, 0, 0]
-   # bottom
-   image[y2, x1:x2, :] = [255, 0, 0]
-   # right
-   image[y1:y2, x2, :] = [255, 0, 0]
+   image[y1:y2, x1, :]   = [255, 0, 0] # left
+   image[y1, x1:x2, :]   = [255, 0, 0] # top
+   image[y1:y2, x2, :]   = [255, 0, 0] # right
+   image[y2, x1:x2+1, :] = [255, 0, 0] # bottom
 
 
    #########################################################
@@ -45,25 +41,39 @@ for d in dirs:
    x2 = 100
    crop = image[y1:y2, x1:x2, :]
    crop = misc.imresize(crop, (64, 64))
-   misc.imsave(name+'_'+d.split('/')[0]+'_crop_2.png', crop)
-   image[y1:y2, x1, :] = [0, 0, 255]
-   image[y1, x1:x2, :] = [0, 0, 255]
-   image[y2, x1:x2, :] = [0, 0, 255]
-   image[y1:y2, x2, :] = [0, 0, 255]
+   misc.imsave('result_images/'+name+'_'+d.split('/')[0]+'_crop_2.png', crop)
+   image[y1:y2, x1, :]   = [0, 0, 255]
+   image[y1, x1:x2, :]   = [0, 0, 255]
+   image[y1:y2, x2, :]   = [0, 0, 255]
+   image[y2, x1:x2+1, :] = [0, 0, 255]
    
    
    #########################################################
-   y1 = 118
-   y2 = 128
-   x1 = 40
-   x2 = 50
+   y1 = 118+30-3
+   y2 = 128+30-3
+   x1 = 40-2
+   x2 = 50-2
    crop = image[y1:y2, x1:x2, :]
    crop = misc.imresize(crop, (64, 64))
[…]

### 2017-09-14 eval_folder.py
update

@@ -1,11 +1,6 @@
 '''
 
-   Main training file
-
-   The goal is to correct the colors in underwater images.
-   CycleGAN was used to create images that appear to be underwater.
-   Those will be sent into the generator, which will attempt to correct the
-   colors.
+   Evaluation File
 
 '''
 
@@ -20,6 +15,7 @@ import ntpath
 import sys
 import os
 import time
+import time
 import glob
 import cPickle as pickle
 from tqdm import tqdm
@@ -32,14 +28,12 @@ import data_ops
 
 if __name__ == '__main__':
 
-   if len(sys.argv) < 3:
-      print 'You must provide an info.pkl file and a diving file'
+   if len(sys.argv) < 2:
+      print 'You must provide an info.pkl file'
       exit()
 
    pkl_file = open(sys.argv[1], 'rb')
    a = pickle.load(pkl_file)
-
-   num_d = str(sys.argv[2])
 
    LEARNING_RATE = a['LEARNING_RATE']
    LOSS_METHOD   = a['LOSS_METHOD']
@@ -58,8 +52,7 @@ if __name__ == '__main__':
                      +'/IG_WEIGHT_'+str(IG_WEIGHT)\
                      +'/DATA_'+DATA+'/'\
 
-   #IMAGES_DIR     = EXPERIMENT_DIR+'test_images/'
-   IMAGES_DIR     = EXPERIMENT_DIR+'diving'+num_d+'/'
+   IMAGES_DIR     = 'tests/test_images/ugan_fl_0.0/'
 
    print
    print 'Creating',IMAGES_DIR
@@ -72,6 +65,7 @@ if __name__ == '__main__':
    print 'BATCH_SIZE:    ',BATCH_SIZE
    print 'NETWORK:       ',NETWORK
    print 'EPOCHS:        ',EPOCHS
+   print 'LAYER_NORM:    ',LAYER_NORM
    print
 
    if NETWORK == 'pix2pix': from pix2pix import *
@@ -105,8 +99,7 @@ if __name__ == '__main__':
    step = int(sess.run(global_step))
 
    # testing paths
-   #test_paths = np.asarray(glob.glob('datasets/'+DATA+'/test/*.jpg'))
-   test_paths = sorted(np.asarray(glob.glob('/mnt/data2/images/underwater/youtube/diving'+num_d+'/*.jpg')))
+   test_paths = np.asarray(glob.glob('tests/test_images/flickr/*.*'))
 
    #random.shuffle(test_paths)
 
[…]

### 2017-09-14 eval_one.py

@@ -1,11 +1,6 @@
 '''
 
-   Main training file
-
-   The goal is to correct the colors in underwater images.
-   CycleGAN was used to create images that appear to be underwater.
-   Those will be sent into the generator, which will attempt to correct the
-   colors.
+   Evaluation File
 
 '''
 
@@ -20,6 +15,7 @@ import ntpath
 import sys
 import os
 import time
+import time
 import glob
 import cPickle as pickle
 from tqdm import tqdm
@@ -33,13 +29,11 @@ import data_ops
 if __name__ == '__main__':
 
    if len(sys.argv) < 3:
-      print 'You must provide an info.pkl file and a diving file'
+      print 'You must provide an info.pkl file and an image'
       exit()
 
    pkl_file = open(sys.argv[1], 'rb')
    a = pickle.load(pkl_file)
-
-   num_d = str(sys.argv[2])
 
    LEARNING_RATE = a['LEARNING_RATE']
    LOSS_METHOD   = a['LOSS_METHOD']
@@ -58,13 +52,7 @@ if __name__ == '__main__':
                      +'/IG_WEIGHT_'+str(IG_WEIGHT)\
                      +'/DATA_'+DATA+'/'\
 
-   #IMAGES_DIR     = EXPERIMENT_DIR+'test_images/'
-   IMAGES_DIR     = EXPERIMENT_DIR+'diving'+num_d+'/'
-
-   print
-   print 'Creating',IMAGES_DIR
-   try: os.makedirs(IMAGES_DIR)
-   except: pass
+   test_image = sys.argv[2]
 
    print
    print 'LEARNING_RATE: ',LEARNING_RATE
@@ -72,6 +60,7 @@ if __name__ == '__main__':
    print 'BATCH_SIZE:    ',BATCH_SIZE
    print 'NETWORK:       ',NETWORK
    print 'EPOCHS:        ',EPOCHS
+   print 'LAYER_NORM:    ',LAYER_NORM
    print
 
    if NETWORK == 'pix2pix': from pix2pix import *
@@ -104,32 +93,19 @@ if __name__ == '__main__':
    
    step = int(sess.run(global_step))
 
-   # testing paths
-   #test_paths = np.asarray(glob.glob('datasets/'+DATA+'/test/*.jpg'))
-   test_paths = sorted(np.asarray(glob.glob('/mnt/data2/images/underwater/youtube/diving'+num_d+'/*.jpg')))
+   img_name = ntpath.basename(test_image)
 
[…]

### 2017-09-14 tests/old_images/temp.py

@@ -1,25 +1,0 @@
-import numpy as np
-from skimage.measure import compare_ssim as ssim
-from skimage.measure import compare_psnr as psnr
-import scipy.misc as misc
-import scipy.stats.signaltonoise as snr
-
-
-
-real_img  = misc.imread('n01496331_11938_real.png')
-cycle_gan = misc.imread('n01496331_11938.png')
-ours      = misc.imread('n01496331_11938_gen_IG_0.0.png')
-'''
-print ssim(real_img, cycle_gan, multichannel=True)
-print ssim(real_img, ours, multichannel=True)
-print
-print psnr(real_img, cycle_gan)
-print psnr(real_img, ours)
-'''
-
-#print np.linalg.norm(np.fft.fftn(real_img))
-#print np.linalg.norm(np.fft.fftn(cycle_gan))
-#print np.linalg.norm(np.fft.fftn(ours))
-
-print snr(cycle_gan)
-

### 2017-09-14 tests/zoom.py

@@ -9,7 +9,8 @@ import numpy as np
 import sys
 
 
-img  = 'n01496331_15872.png'
+#img  = 'n01496331_15872.png'
+img  = 'n01496331_2629.png'
 name = img.split('.')[0]
 root = 'test_images/'
 dirs = ['cgan/', 'original/', 'ugan_0.0/', 'ugan_1.0/']

### 2017-09-14 eval_folder.py
update

@@ -52,7 +52,7 @@ if __name__ == '__main__':
                      +'/IG_WEIGHT_'+str(IG_WEIGHT)\
                      +'/DATA_'+DATA+'/'\
 
-   IMAGES_DIR     = 'tests/test_images/ugan_fl_0.0/'
+   IMAGES_DIR     = 'tests/test_images/ugan_fl_1.0/'
 
    print
    print 'Creating',IMAGES_DIR

### 2017-09-14 tests/ren.sh

@@ -5,7 +5,12 @@
 rm test_images/ugan_0.0/*real*
 rm test_images/ugan_1.0/*real*
 
+rm test_images/ugan_fl_0.0/*real*
+rm test_images/ugan_fl_1.0/*real*
+
 rename 's/_gen//' test_images/ugan_0.0/*
 rename 's/_gen//' test_images/ugan_1.0/*
 
+rename 's/_gen//' test_images/ugan_fl_0.0/*
+rename 's/_gen//' test_images/ugan_fl_1.0/*
 

### 2017-09-14 tests/zoom.py

@@ -2,6 +2,10 @@
 
    Script to zoom in on parts of an image and save out
 
+   This will be used for comparing to CycleGAN images
+
+   Might also be used for comparing local image stats
+
 '''
 
 import scipy.misc as misc
@@ -10,20 +14,36 @@ import sys
 
 
 #img  = 'n01496331_15872.png'
-img  = 'n01496331_2629.png'
+#img  = 'n01496331_2629.png'
+
+# possible one to use - stingray
+#img = '2425754085_bcfa73d160_o.png'
+
+# lots of stuff
+#img = '6959211760_295f0e300e_o.png'
+
+# pretty good fish and corral
+img = '8563897707_0a8be6d5f1_o.png'
+
+# orange coral
+#img = '5538756669_6a5627ea9c_o.png'
+
+#img = '8564948684_dbcf221d1e_o.png'
+
 name = img.split('.')[0]
 root = 'test_images/'
-dirs = ['cgan/', 'original/', 'ugan_0.0/', 'ugan_1.0/']
+#dirs = ['cgan/', 'original/', 'ugan_fl_0.0/', 'ugan__fl_1.0/']
+dirs = ['cgan/', 'flickr/', 'ugan_fl_0.0/', 'ugan_fl_1.0/']
 
 for d in dirs:
 
    image = misc.imread(root+d+img)
 
-   #########################################################
-   y1 = 160
-   y2 = 200
-   x1 = 210
-   x2 = 250
+   ######################################################### red box
+   y1 = 125
+   y2 = 155
+   x1 = 120
+   x2 = 150
    # row, column (y, x), (0,0) at top left
    crop = image[y1:y2, x1:x2, :]
    crop = misc.imresize(crop, (64, 64))
@@ -35,11 +55,11 @@ for d in dirs:
    image[y2, x1:x2+1, :] = [255, 0, 0] # bottom
 
 
-   #########################################################
-   y1 = 225
-   y2 = 245
-   x1 = 80
-   x2 = 100
+   ######################################################### blue box
+   y1 = 170
+   y2 = 200
+   x1 = 60
+   x2 = 90
    crop = image[y1:y2, x1:x2, :]
    crop = misc.imresize(crop, (64, 64))
    misc.imsave('result_images/'+name+'_'+d.split('/')[0]+'_crop_2.png', crop)
@@ -49,11 +69,11 @@ for d in dirs:
    image[y2, x1:x2+1, :] = [0, 0, 255]
[…]

### 2017-09-14 tests/zoom.py
update

@@ -39,6 +39,9 @@ for d in dirs:
 
    image = misc.imread(root+d+img)
 
+   name = d.split('/')[0]   
+
+   # TODO when I am comparing metrics, need to save out crops without the borders
    ######################################################### red box
    y1 = 125
    y2 = 155
@@ -47,7 +50,12 @@ for d in dirs:
    # row, column (y, x), (0,0) at top left
    crop = image[y1:y2, x1:x2, :]
    crop = misc.imresize(crop, (64, 64))
-   misc.imsave('result_images/'+name+'_'+d.split('/')[0]+'_crop_1.png', crop)
+   # coloring the crops to match the boxes
+   crop[0:,0,:]  = [255,0,0] # left
+   crop[0:,63,:] = [255,0,0] # right
+   crop[0,0:,:]  = [255,0,0] # top
+   crop[63,0:,:] = [255,0,0] # bot
+   misc.imsave('result_images/'+name+'_crop1.png', crop)
    # draw box around cropped area
    image[y1:y2, x1, :]   = [255, 0, 0] # left
    image[y1, x1:x2, :]   = [255, 0, 0] # top
@@ -62,7 +70,11 @@ for d in dirs:
    x2 = 90
    crop = image[y1:y2, x1:x2, :]
    crop = misc.imresize(crop, (64, 64))
-   misc.imsave('result_images/'+name+'_'+d.split('/')[0]+'_crop_2.png', crop)
+   crop[0:,0,:]  = [0,0,255] # left
+   crop[0:,63,:] = [0,0,255] # right
+   crop[0,0:,:]  = [0,0,255] # top
+   crop[63,0:,:] = [0,0,255] # bot
+   misc.imsave('result_images/'+name+'_crop_2.png', crop)
    image[y1:y2, x1, :]   = [0, 0, 255]
    image[y1, x1:x2, :]   = [0, 0, 255]
    image[y1:y2, x2, :]   = [0, 0, 255]
@@ -76,7 +88,11 @@ for d in dirs:
    x2 = 105
    crop = image[y1:y2, x1:x2, :]
    crop = misc.imresize(crop, (64, 64))
-   misc.imsave('result_images/'+name+'_'+d.split('/')[0]+'_crop_3.png', crop)
+   crop[0:,0,:]  = [0,255,0] # left
+   crop[0:,63,:] = [0,255,0] # right
[…]

### 2017-09-14 tests/zoom.py
update

@@ -41,6 +41,9 @@ for d in dirs:
 
    name = d.split('/')[0]   
 
+   name = name.replace('ugan_fl_0.0','ugan')
+   name = name.replace('ugan_fl_1.0','uganp')
+
    # TODO when I am comparing metrics, need to save out crops without the borders
    ######################################################### red box
    y1 = 125
@@ -74,7 +77,7 @@ for d in dirs:
    crop[0:,63,:] = [0,0,255] # right
    crop[0,0:,:]  = [0,0,255] # top
    crop[63,0:,:] = [0,0,255] # bot
-   misc.imsave('result_images/'+name+'_crop_2.png', crop)
+   misc.imsave('result_images/'+name+'_crop2.png', crop)
    image[y1:y2, x1, :]   = [0, 0, 255]
    image[y1, x1:x2, :]   = [0, 0, 255]
    image[y1:y2, x2, :]   = [0, 0, 255]
@@ -92,31 +95,34 @@ for d in dirs:
    crop[0:,63,:] = [0,255,0] # right
    crop[0,0:,:]  = [0,255,0] # top
    crop[63,0:,:] = [0,255,0] # bot
-   misc.imsave('result_images/'+name+'_crop_3.png', crop)
+   misc.imsave('result_images/'+name+'_crop3.png', crop)
    image[y1:y2, x1, :]   = [0, 255, 0]
    image[y1, x1:x2, :]   = [0, 255, 0]
    image[y1:y2, x2, :]   = [0, 255, 0]
    image[y2, x1:x2+1, :] = [0, 255, 0]
 
-   ######################################################### yellow box
+   ######################################################### orange box
    y1 = 180
    y2 = 210
    x1 = 175
    x2 = 205
    crop = image[y1:y2, x1:x2, :]
    crop = misc.imresize(crop, (64, 64))
-   crop[0:,0,:]  = [255,255,0] # left
-   crop[0:,63,:] = [255,255,0] # right
-   crop[0,0:,:]  = [255,255,0] # top
-   crop[63,0:,:] = [255,255,0] # bot
-   misc.imsave('result_images/'+name+'_crop_4.png', crop)
-   image[y1:y2, x1, :]   = [255, 255, 0]
-   image[y1, x1:x2, :]   = [255, 255, 0]
-   image[y1:y2, x2, :]   = [255, 255, 0]
[…]

### 2017-09-14 files/paper/paper.tex
update

@@
 \usepackage{graphicx}
-\graphicspath{ {images/}{images/figure1/} }
+\graphicspath{ {images/}{images/figure1/}{images/figure2/}{images/figure3/} }
 %\graphicspath{{images/failures/}}
@@
 
+% TODO definitely need help with formatting, but content is there
+\begin{figure*}
+\centering
+\begin{tabular}{p{4.0cm} p{4.0cm} p{4.0cm} p{4.0cm}}
+
+   \includegraphics[width=1.7in]{flickr_cmp} &
+   \includegraphics[width=1.7in]{cgan_cmp} &
+   \includegraphics[width=1.7in]{ugan_cmp} &
+   \includegraphics[width=1.7in]{uganp_cmp} \\
+
+\end{tabular}
+\end{figure*}
+\begin{figure*}
+\begin{tabular}{p{1.9cm} p{1.9cm} p{1.9cm} p{1.9cm} p{1.9cm} p{1.9cm} p{1.9cm} p{1.9cm} }
+
+   \includegraphics[width=0.8in]{flickr_crop1} &
+   \includegraphics[width=0.8in]{flickr_crop2} &
+   \includegraphics[width=0.8in]{cgan_crop1} &
+   \includegraphics[width=0.8in]{cgan_crop2} &
+   \includegraphics[width=0.8in]{ugan_crop1} &
+   \includegraphics[width=0.8in]{ugan_crop2} &
+   \includegraphics[width=0.8in]{ugan_crop1} &
+   \includegraphics[width=0.8in]{ugan_crop2} \\
+
+   \includegraphics[width=0.8in]{flickr_crop3} &
+   \includegraphics[width=0.8in]{flickr_crop4} &
+   \includegraphics[width=0.8in]{cgan_crop3} &
+   \includegraphics[width=0.8in]{cgan_crop4} &
+   \includegraphics[width=0.8in]{ugan_crop3} &
+   \includegraphics[width=0.8in]{ugan_crop4} &
+   \includegraphics[width=0.8in]{ugan_crop3} &
+   \includegraphics[width=0.8in]{ugan_crop4} \\
+
+\end{tabular}
+\caption{Zooming in on comparisons.}
+\end{figure*}
+
 \subsection{Diver Tracking}
@@
 
-   \small{Original} & \small{CycleGAN} & \small{UGAN} & \small{UGAN-P} \\
+   5 \small{Original} & \small{CycleGAN} & \small{UGAN} & \small{UGAN-P} \\
 
@@
 
+Future work: Getting a better and larger dataset. I think that would help a great deal. Also data augmentation
+after CycleGAN, such as gaussian blurring, noise, particle effect, more lighting effects etc.
+
 \section*{Acknowledgment}

### 2017-09-14 tests/compare_hist.py

@@ -1,0 +1,26 @@
+import cv2
+import numpy as np
+
+
+
+
+flickr = cv2.imread('result_images/flickr_crop4.png')
+cgan   = cv2.imread('result_images/cgan_crop4.png')
+ugan   = cv2.imread('result_images/ugan_crop4.png')
+uganp  = cv2.imread('result_images/uganp_crop4.png')
+
+
+flickr_hist = cv2.calcHist([flickr], [0,1,2], None, [8,8,8], [0,256,0,256,0,256])
+cgan_hist   = cv2.calcHist([cgan],   [0,1,2], None, [8,8,8], [0,256,0,256,0,256])
+ugan_hist   = cv2.calcHist([ugan],   [0,1,2], None, [8,8,8], [0,256,0,256,0,256])
+uganp_hist  = cv2.calcHist([uganp],  [0,1,2], None, [8,8,8], [0,256,0,256,0,256])
+
+a = cv2.compareHist(flickr_hist, cgan_hist,  cv2.HISTCMP_BHATTACHARYYA)
+b = cv2.compareHist(flickr_hist, ugan_hist,  cv2.HISTCMP_BHATTACHARYYA)
+c = cv2.compareHist(flickr_hist, uganp_hist, cv2.HISTCMP_BHATTACHARYYA)
+
+print a
+print b
+print c
+
+

### 2017-09-14 tests/zoom.py

@@ -53,6 +53,8 @@ for d in dirs:
    # row, column (y, x), (0,0) at top left
    crop = image[y1:y2, x1:x2, :]
    crop = misc.imresize(crop, (64, 64))
+   # save out before coloring edges
+   misc.imsave('result_images/'+name+'_crop1_og.png', crop)
    # coloring the crops to match the boxes
    crop[0:,0,:]  = [255,0,0] # left
    crop[0:,63,:] = [255,0,0] # right
@@ -73,6 +75,7 @@ for d in dirs:
    x2 = 90
    crop = image[y1:y2, x1:x2, :]
    crop = misc.imresize(crop, (64, 64))
+   misc.imsave('result_images/'+name+'_crop2_og.png', crop)
    crop[0:,0,:]  = [0,0,255] # left
    crop[0:,63,:] = [0,0,255] # right
    crop[0,0:,:]  = [0,0,255] # top
@@ -91,6 +94,7 @@ for d in dirs:
    x2 = 105
    crop = image[y1:y2, x1:x2, :]
    crop = misc.imresize(crop, (64, 64))
+   misc.imsave('result_images/'+name+'_crop3_og.png', crop)
    crop[0:,0,:]  = [0,255,0] # left
    crop[0:,63,:] = [0,255,0] # right
    crop[0,0:,:]  = [0,255,0] # top
@@ -108,6 +112,7 @@ for d in dirs:
    x2 = 205
    crop = image[y1:y2, x1:x2, :]
    crop = misc.imresize(crop, (64, 64))
+   misc.imsave('result_images/'+name+'_crop4_og.png', crop)
    crop[0:,0,:]  = [255,140,0] # left
    crop[0:,63,:] = [255,140,0] # right
    crop[0,0:,:]  = [255,140,0] # top

### 2017-09-14 tests/edge_detection.py
update

@@ -14,10 +14,10 @@ cimgs = []
 uimgs = []
 
 # all the image paths
-real_paths   = sorted(glob.glob('test_images/original/*.png'))
+real_paths   = sorted(glob.glob('test_images/flickr/*.png'))
 cgan_paths   = sorted(glob.glob('test_images/cgan/*.png'))
-ugan_0_paths = sorted(glob.glob('test_images/ugan_0.0/*.png'))
-ugan_1_paths = sorted(glob.glob('test_images/ugan_1.0/*.png'))
+ugan_0_paths = sorted(glob.glob('test_images/ugan_fl_0.0/*.png'))
+ugan_1_paths = sorted(glob.glob('test_images/ugan_fl_1.0/*.png'))
 
 # respective distances in image space of canny edge detection
 cgan_dist   = []
@@ -25,17 +25,18 @@ ugan_0_dist = []
 ugan_1_dist = []
 
 #save_images = ['n02607072_4739.png', 'n01496331_15872.png', 'n01496331_22079.png']
-save_images = ['n01496331_15872.png']
 
-largest = 0
-l_img = ''
+# orange corral
+#save_images = ['5538756669_6a5627ea9c_o.png']
 
-save = 1
+save_images = ['525931976_dffc710a58_o.png', '8032289_2af635da3c_o.png', '1056733511_8a8c0d9410_o.png', '2508954302_63b17667ce_o.png']
+
+save = 0
 
 # just open and close quick to wipe it
-results_file = open('result_images/results.txt', 'w')
+results_file = open('edge_results/results.txt', 'w')
 results_file.close()
-results_file = open('result_images/results.txt', 'a')
+results_file = open('edge_results/results.txt', 'a')
 results_file.write('image_name,cgan_dist,ugan_0_dist,ugan_1_dist\n')
 
 # loop through all paths and open images
@@ -72,10 +73,6 @@ for r,c,u0,u1 in tqdm(zip(real_paths, cgan_paths, ugan_0_paths, ugan_1_paths)):
 
    d = np.linalg.norm(edges-cedges) - np.linalg.norm(edges-u0edges)
 
-   #if d > largest:
-   #   largest = d
-   #   l_img = image_name
-
    if save == 1:
 
       print image_name
@@ -86,37 +83,31 @@ for r,c,u0,u1 in tqdm(zip(real_paths, cgan_paths, ugan_0_paths, ugan_1_paths)):
 
       # save a bunch of images for paper
[…]

### 2017-09-14 tests/compare_hist.py
update

@@ -1,26 +1,44 @@
 import cv2
 import numpy as np
 
+for i in range(1,5):
 
+   # 
+   flickr = cv2.imread('result_images/flickr_crop'+str(i)+'_og.png')
+   cgan   = cv2.imread('result_images/cgan_crop'  +str(i)+'_og.png')
+   ugan   = cv2.imread('result_images/ugan_crop'  +str(i)+'_og.png')
+   uganp  = cv2.imread('result_images/uganp_crop' +str(i)+'_og.png')
 
+   flickr_hist = cv2.calcHist([flickr], [0,1,2], None, [8,8,8], [0,256,0,256,0,256])
+   cgan_hist   = cv2.calcHist([cgan],   [0,1,2], None, [8,8,8], [0,256,0,256,0,256])
+   ugan_hist   = cv2.calcHist([ugan],   [0,1,2], None, [8,8,8], [0,256,0,256,0,256])
+   uganp_hist  = cv2.calcHist([uganp],  [0,1,2], None, [8,8,8], [0,256,0,256,0,256])
 
-flickr = cv2.imread('result_images/flickr_crop4.png')
-cgan   = cv2.imread('result_images/cgan_crop4.png')
-ugan   = cv2.imread('result_images/ugan_crop4.png')
-uganp  = cv2.imread('result_images/uganp_crop4.png')
+   a = cv2.compareHist(flickr_hist, cgan_hist,  cv2.HISTCMP_BHATTACHARYYA)
+   b = cv2.compareHist(flickr_hist, ugan_hist,  cv2.HISTCMP_BHATTACHARYYA)
+   c = cv2.compareHist(flickr_hist, uganp_hist, cv2.HISTCMP_BHATTACHARYYA)
 
+   flickr = flickr/255.0
+   cgan   = cgan/255.0
+   ugan   = ugan/255.0
+   uganp  = uganp/255.0
 
-flickr_hist = cv2.calcHist([flickr], [0,1,2], None, [8,8,8], [0,256,0,256,0,256])
-cgan_hist   = cv2.calcHist([cgan],   [0,1,2], None, [8,8,8], [0,256,0,256,0,256])
-ugan_hist   = cv2.calcHist([ugan],   [0,1,2], None, [8,8,8], [0,256,0,256,0,256])
-uganp_hist  = cv2.calcHist([uganp],  [0,1,2], None, [8,8,8], [0,256,0,256,0,256])
-
[…]

### 2017-09-14 tests/em_dist.py

@@ -1,0 +1,83 @@
+#Import OpenCv library
+from cv2 import *
+
+### HISTOGRAM FUNCTION #########################################################
+def calcHistogram(src):
+    # Convert to HSV
+    hsv = cv.CreateImage(cv.GetSize(src), 8, 3)
+    cv.CvtColor(src, hsv, cv.CV_BGR2HSV)
+
+    # Extract the H and S planes
+    size = cv.GetSize(src)
+    h_plane = cv.CreateMat(size[1], size[0], cv.CV_8UC1)
+    s_plane = cv.CreateMat(size[1], size[0], cv.CV_8UC1)
+    cv.Split(hsv, h_plane, s_plane, None, None)
+    planes = [h_plane, s_plane]
+
+    #Define numer of bins
+    h_bins = 30
+    s_bins = 32
+
+    #Define histogram size
+    hist_size = [h_bins, s_bins]
+
+    # hue varies from 0 (~0 deg red) to 180 (~360 deg red again */
+    h_ranges = [0, 180]
+
+    # saturation varies from 0 (black-gray-white) to 255 (pure spectrum color)
+    s_ranges = [0, 255]
+
+    ranges = [h_ranges, s_ranges]
+
+    #Create histogram
+    hist = cv.CreateHist([h_bins, s_bins], cv.CV_HIST_ARRAY, ranges, 1)
+
+    #Calc histogram
+    cv.CalcHist([cv.GetImage(i) for i in planes], hist)
+
+    cv.NormalizeHist(hist, 1.0)
+
+    #Return histogram
+    return hist
+
+### EARTH MOVERS ############################################################
+def calcEM(hist1,hist2,h_bins,s_bins):
+
+#Define number of rows
+numRows = h_bins*s_bins
+
+sig1 = cv.CreateMat(numRows, 3, cv.CV_32FC1)
+sig2 = cv.CreateMat(numRows, 3, cv.CV_32FC1)    
+
+for h in range(h_bins):
+    for s in range(s_bins): 
+        bin_val = cv.QueryHistValue_2D(hist1, h, s)
+        cv.Set2D(sig1, h*s_bins+s, 0, cv.Scalar(bin_val))
+        cv.Set2D(sig1, h*s_bins+s, 1, cv.Scalar(h))
+        cv.Set2D(sig1, h*s_bins+s, 2, cv.Scalar(s))
+
+        bin_val = cv.QueryHistValue_2D(hist2, h, s)
[…]

### 2017-09-14 tests/psnr.py

@@ -1,0 +1,24 @@
+import cv2
+import numpy as np
+import math
+
+def psnr(img1, img2):
+   mse = np.mean( (img1 - img2) ** 2 )
+   return 10 * math.log10(255.0**2/mse)
+
+for i in range(1,5):
+
+   flickr = cv2.imread('result_images/flickr_crop'+str(i)+'_og.png')
+   cgan   = cv2.imread('result_images/cgan_crop'  +str(i)+'_og.png')
+   ugan   = cv2.imread('result_images/ugan_crop'  +str(i)+'_og.png')
+   uganp  = cv2.imread('result_images/uganp_crop' +str(i)+'_og.png')
+
+
+   print 'crop',i
+   print psnr(flickr,cgan)
+   print psnr(flickr,ugan)
+   print psnr(flickr,uganp)
+   print
+
+
+

### 2017-09-14 files/paper/paper.tex
mdpm stuff added

@@
 \IEEEauthorblockN{Md Jahidul Islam}
-\IEEEauthorblockA{UMN\\}
+\IEEEauthorblockA{University of Minnesota- Twin Cities\\
+MN, USA.\\
+islam034@umn.edu }
 \and
 \IEEEauthorblockN{Junaed Sattar}
-\IEEEauthorblockA{UMN\\
+\IEEEauthorblockA{University of Minnesota- Twin Cities\\
+MN, USA.\\
+junaed@umn.edu
 }}
@@
 
-\subsection{Diver Tracking}
+\subsection{Diver Tracking using Frequency-Domain Detection}
+We investigate the frequency-domain characteristics of the restored images through a case-study of periodic motion tracking in sequence of images.
+Particularly, we compared the performance of Mixed Domain Periodic Motion (MDPM)- tracker \cite{islam2017mixed} on a sequence of images of a diver swimming in  arbitrary directions.
+MDPM tracker is designed for underwater robots to follow scuba divers by   tracking distinct frequency-domain signatures (high-amplitude spectra at $1$-$2$Hz) pertaining to human swimming.
+Amplitude spectra in frequency-domain correspond to the periodic intensity variations in image-space over time, which is often eroded in noisy underwater images \cite{shkurti2017underwater}.
+
+Fig.
+\ref{mdpmStuff} illustrates the improved performance of MDPM tracker on generated images compared to the real ones.
+Underwater images often fail to capture the true contrast in intensity values between foreground and background due to low visibility.
+The generated images seem to restore these eroded intensity variations to some extent, causing much improved positive detection for MDPM tracker.
+
+\begin{figure*}
+\centering
+\begin{tabular}{p{4.0cm} p{4.0cm} p{4.0cm} p{4.0cm}}
+   \includegraphics[width=1.7in]{mdpm/real1} &
+   \includegraphics[width=1.7in]{mdpm/real2} &
+   \includegraphics[width=1.7in]{mdpm/real3} &
+   \includegraphics[width=1.7in]{mdpm/real4} \\
+   \includegraphics[width=1.7in]{mdpm/gen1} &
+   \includegraphics[width=1.7in]{mdpm/gen2} &
+   \includegraphics[width=1.7in]{mdpm/gen3} &
+   \includegraphics[width=1.7in]{mdpm/gen4} \\
+\end{tabular}
+\vspace{4mm}
+
+\begin{tabular}{l|c|c|c|r}
+ \cline{2-5}
+ &  Correct detection & Wrong detection & Missed detection & Total \# of frames\\ \hline  \cline{2-4}
+On real images  &  42 & 14 & 444 & 500  \\ \hline
+On generated images  &  147 & 24 & 329 & 500  \\ \hline
+\end{tabular}
+
+\caption{Performance of MDPM tracker \cite{islam2017mixed} on both real (top row) and generated (second row) images; the Table compares the detection performance for both sets of images over a sequence of $500$ frames.
+}
+\label{mdpmStuff}
+\end{figure*}
+
+%Flippers of a human diver typically oscillate at frequencies between $1$ and $2$ Hz, which produces periodic intensity variations in the image-space over time.
+These variations correspond to distinct signatures in the frequency-domain (high-amplitude spectra at $1$-$2$Hz), which can be used for reliable detection.
 

### 2017-09-14 tests/edge_detection.py
update

@@ -40,11 +40,13 @@ results_file = open('edge_results/results.txt', 'a')
 results_file.write('image_name,cgan_dist,ugan_0_dist,ugan_1_dist\n')
 
 # loop through all paths and open images
+i = 1
 for r,c,u0,u1 in tqdm(zip(real_paths, cgan_paths, ugan_0_paths, ugan_1_paths)):
 
    if save == 1 and ntpath.basename(r) not in save_images: continue
    
-   image_name = ntpath.basename(r).split('.png')[0]
+   #image_name = ntpath.basename(r).split('.png')[0]
+   image_name = str(i)
 
    rimg  = cv2.imread(r)
    cimg  = cv2.imread(c)
@@ -101,6 +103,8 @@ for r,c,u0,u1 in tqdm(zip(real_paths, cgan_paths, ugan_0_paths, ugan_1_paths)):
       cv2.imwrite('edge_results/'+image_name+'_u1edges.png', 255.0*u1edges)
 
       results_file.write(image_name+','+str(cgan_dist_)+','+str(ugan_0_dist_)+','+str(ugan_1_dist_)+'\n')
+
+      i += 1
 
 results_file.close()
 print 'done'

### 2017-09-14 files/paper/paper.tex
update

@@
 \usepackage{graphicx}
-\graphicspath{ {images/}{images/figure1/}{images/figure2/}{images/figure3/} }
+\graphicspath{ {images/}{images/figure1/}{images/figure2/}{images/figure3/} {images/edges/}}
 %\graphicspath{{images/failures/}}
@@
 We used several subsets of Imagenet \cite{deng2009imagenet} for training and evaluation of our methods. We also
-evaluate a tracking algorithm on a diving video taken from Youtube. Subsets of Imagenet containing underwater images
+evaluate a tracking algorithm on a diving video taken from Youtube
+\footnote{https://www.youtube.com/watch?v=QmRFmhILd5o}. Subsets of Imagenet containing underwater images
 were selected for the training of CycleGAN, and manually separated into two classes. We let $X$ be the set of
@@
 images from $X$ appeared to have come from $Y$. Finally, our image pairs for training data were generated by distorting
-all images in $X$ with $F$. Figure 2 shows sample training pairs.
+all images in $X$ with $F$. Figure 2 shows sample training pairs. When comparing with CycleGAN, we used a test set
+acquired from Flickr \footnote{How do I cite Flickr}.
 
 \subsection{Evaluation}
-We trained UGAN and UGAN-P on the image pairs generated by CycleGAN, and evaluated entirely on the images from the
+We train UGAN and UGAN-P on the image pairs generated by CycleGAN, and evaluate entirely on the images from the
 test set, $Y$. Note that these images do not contain any ground truth, as they are original distorted images from
@@
 amount of green or blue from the entire image.
+
+\begin{figure}
+\centering
+\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm}}
+
+   Original & UGAN & UGAN-P \\
+
+   \includegraphics[width=0.8in]{n01917289_4982_real} &
+   \includegraphics[width=0.8in]{n01917289_4982_gen_0} &
+   \includegraphics[width=0.8in]{n01917289_4982_gen_1} \\
+
+   \includegraphics[width=0.8in]{n01496331_16340_real} &
+   \includegraphics[width=0.8in]{n01496331_16340_gen_0} &
+   \includegraphics[width=0.8in]{n01496331_16340_gen_1} \\
+
+   \includegraphics[width=0.8in]{n01496331_22183_real} &
+   \includegraphics[width=0.8in]{n01496331_22183_gen_0} &
+   \includegraphics[width=0.8in]{n01496331_22183_gen_1} \\
+
+   \includegraphics[width=0.8in]{n01664065_29738_real} &
+   \includegraphics[width=0.8in]{n01664065_29738_gen_0} &
+   \includegraphics[width=0.8in]{n01664065_29738_gen_1} \\
+
+   \includegraphics[width=0.8in]{n01496331_11938_real} &
+   \includegraphics[width=0.8in]{n01496331_11938_gen_0} &
+   \includegraphics[width=0.8in]{n01496331_11938_gen_1} \\
+
+   \includegraphics[width=0.8in]{n02606052_2969_real} &
+   \includegraphics[width=0.8in]{n02606052_2969_gen_0} &
+   \includegraphics[width=0.8in]{n02606052_2969_gen_1} \\
+
+\end{tabular}
+\caption{Samples. The network can both recover color and also correct color if a small amount is present.}
+\end{figure}
 
@@
 ours are better by showing results from Canny Edge Detector.
+
+\begin{figure}
+\centering
+\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.7cm}}
+
+   Original & CycleGAN & UGAN & UGAN-P \\
+
+   \includegraphics[width=0.8in]{1_original} &
+   \includegraphics[width=0.8in]{1_cimg} &
+   \includegraphics[width=0.8in]{1_u0img} &
+   \includegraphics[width=0.8in]{1_u1img} \\ [-1ex]
+   \includegraphics[width=0.8in]{1_oedges} &
+   \includegraphics[width=0.8in]{1_cedges} &
+   \includegraphics[width=0.8in]{1_u0edges} &
+   \includegraphics[width=0.8in]{1_u1edges} \\
+
+   \includegraphics[width=0.8in]{2_original} &
+   \includegraphics[width=0.8in]{2_cimg} &
+   \includegraphics[width=0.8in]{2_u0img} &
+   \includegraphics[width=0.8in]{2_u1img} \\ [-1ex]
+   \includegraphics[width=0.8in]{2_oedges} &
+   \includegraphics[width=0.8in]{2_cedges} &
+   \includegraphics[width=0.8in]{2_u0edges} &
+   \includegraphics[width=0.8in]{2_u1edges} \\
+
+   \includegraphics[width=0.8in]{3_original} &
+   \includegraphics[width=0.8in]{3_cimg} &
+   \includegraphics[width=0.8in]{3_u0img} &
+   \includegraphics[width=0.8in]{3_u1img} \\ [-1ex]
+   \includegraphics[width=0.8in]{3_oedges} &
+   \includegraphics[width=0.8in]{3_cedges} &
+   \includegraphics[width=0.8in]{3_u0edges} &
+   \includegraphics[width=0.8in]{3_u1edges} \\
+
+   \includegraphics[width=0.8in]{4_original} &
+   \includegraphics[width=0.8in]{4_cimg} &
+   \includegraphics[width=0.8in]{4_u0img} &
+   \includegraphics[width=0.8in]{4_u1img} \\ [-1ex]
+   \includegraphics[width=0.8in]{4_oedges} &
+   \includegraphics[width=0.8in]{4_cedges} &
+   \includegraphics[width=0.8in]{4_u0edges} &
+   \includegraphics[width=0.8in]{4_u1edges} \\
+
+\end{tabular}
+\caption{Running the Canny Edge Detector on sample images. Both variants of UGAN contain less noise than CycleGAN,
+and are closer in the image space to the original. For each pair, the top row is the input image, and bottom row
+the result of the edge detector.}
+\end{figure}
 
@@
 
-\begin{tabular}{l|c|c|c|r}
+\begin{tabular}{l|c|c|c|r|}
  \cline{2-5}
@@
 
-\begin{figure}
-\centering
-\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.5cm}}
-   % TODO 
-   % I couldn't figure out how to get the text centered above the images
-   % Also, the numbers below the images should be centered too, and more
-   % obviously below the row instead of seemlingly above the next one. Those
-   % numbers are the distances in pixel space (normalized between [0,1]) from
-   % the edge image to the original edge image.
-
-   5 \small{Original} & \small{CycleGAN} & \small{UGAN} & \small{UGAN-P} \\
-
-%   \includegraphics[width=0.8in]{n01496331_15872_original} &
-%   \includegraphics[width=0.8in]{n01496331_15872_cimg}     &
-%   \includegraphics[width=0.8in]{n01496331_15872_u0img}    &
-%   \includegraphics[width=0.8in]{n01496331_15872_u1img}    \\ [-1ex]
-%   \includegraphics[width=0.8in]{n01496331_15872_oedges}   &
-%   \includegraphics[width=0.8in]{n01496331_15872_cedges}   &
-%   \includegraphics[width=0.8in]{n01496331_15872_u0edges}  &
-%   \includegraphics[width=0.8in]{n01496331_15872_u1edges}  \\
-   0 & \small{125.78} & \small{80.68} & \small{78.49} \\
-
-%   \includegraphics[width=0.8in]{n01496331_22079_original} &
-%   \includegraphics[width=0.8in]{n01496331_22079_cimg}     & 
-%   \includegraphics[width=0.8in]{n01496331_22079_u0img}    &
-%   \includegraphics[width=0.8in]{n01496331_22079_u1img}    \\ [-1ex]
-%   \includegraphics[width=0.8in]{n01496331_22079_oedges}   &
-%   \includegraphics[width=0.8in]{n01496331_22079_cedges}   &
-%   \includegraphics[width=0.8in]{n01496331_22079_u0edges}  &
-%   \includegraphics[width=0.8in]{n01496331_22079_u1edges}  \\
-   0 & \small{94.57} & \small{38.22} & \small{37.29} \\
-
-%   \includegraphics[width=0.8in]{n02607072_4739_original} &
-%   \includegraphics[width=0.8in]{n02607072_4739_cimg} &
-%   \includegraphics[width=0.8in]{n02607072_4739_u0img} &
-%   \includegraphics[width=0.8in]{n02607072_4739_u1img} \\ [-1ex]
-%   \includegraphics[width=0.8in]{n02607072_4739_oedges} &
-%   \includegraphics[width=0.8in]{n02607072_4739_cedges} &
-%   \includegraphics[width=0.8in]{n02607072_4739_u0edges} &
-%   \includegraphics[width=0.8in]{n02607072_4739_u1edges} \\
-   0 & \small{100.69} & \small{87.81} & \small{87.95} \\
-
-\end{tabular}
-\caption{Running the Canny Edge Detector on sample images. Both variants of UGAN contain less noise than CycleGAN,
-and are closer in the image space to the original. For each pair, the top row is the input image, and bottom row
-the result of the edge detector.}
-\end{figure}
-
 \section{Conclusion}

### 2017-09-14 classify/train.py

@@ -1,0 +1,269 @@
+'''
+
+   Main training file
+
+   The goal is to correct the colors in underwater images.
+   CycleGAN was used to create images that appear to be underwater.
+   Those will be sent into the generator, which will attempt to correct the
+   colors.
+
+'''
+
+import cPickle as pickle
+import tensorflow as tf
+from tqdm import tqdm
+from scipy import misc
+import numpy as np
+import argparse
+import ntpath
+import sys
+import os
+import time
+import glob
+
+sys.path.insert(0, 'ops/')
+sys.path.insert(0, 'nets/')
+from tf_ops import *
+
+import data_ops
+
+if __name__ == '__main__':
+   parser = argparse.ArgumentParser()
+   parser.add_argument('--DATA',          required=False,default='rocks',type=str,help='Dataset to use')
+   parser.add_argument('--EPOCHS',        required=False,default=4,type=int,help='Number of epochs for GAN')
+   parser.add_argument('--NETWORK',       required=False,default='pix2pix',type=str,help='Network to use')
+   parser.add_argument('--L1_WEIGHT',     required=False,default=100.,type=float,help='Weight for L1 loss')
+   parser.add_argument('--IG_WEIGHT',     required=False,default=1.,type=float,help='Weight for image gradient loss')
+   parser.add_argument('--BATCH_SIZE',    required=False,default=32,type=int,help='Batch size')
+   parser.add_argument('--LOSS_METHOD',   required=False,default='gan',help='Loss function for GAN')
+   parser.add_argument('--LEARNING_RATE', required=False,default=2e-5,type=float,help='Learning rate')
+   a = parser.parse_args()
+
+   LEARNING_RATE = float(a.LEARNING_RATE)
+   LOSS_METHOD   = a.LOSS_METHOD
+   BATCH_SIZE    = a.BATCH_SIZE
+   L1_WEIGHT     = float(a.L1_WEIGHT)
+   IG_WEIGHT     = float(a.IG_WEIGHT)
+   NETWORK       = a.NETWORK
+   EPOCHS        = a.EPOCHS
+   DATA          = a.DATA
+   LAYER_NORM          = bool(a.LAYER_NORM)
+   
[…]

### 2017-09-14 tests/edge_detection.py

@@ -24,14 +24,9 @@ cgan_dist   = []
 ugan_0_dist = []
 ugan_1_dist = []
 
-#save_images = ['n02607072_4739.png', 'n01496331_15872.png', 'n01496331_22079.png']
-
-# orange corral
-#save_images = ['5538756669_6a5627ea9c_o.png']
-
 save_images = ['525931976_dffc710a58_o.png', '8032289_2af635da3c_o.png', '1056733511_8a8c0d9410_o.png', '2508954302_63b17667ce_o.png']
 
-save = 0
+save = 1
 
 # just open and close quick to wipe it
 results_file = open('edge_results/results.txt', 'w')

### 2017-09-15 files/paper/paper.tex
update

@@
    \begin{aligned}
-      \mathcal{L}_{UGAN}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + \lambda_{1} \mathcal{L}_{L1}(G) +  \lambda_{2} \mathcal{L}_{GDL}
+      \mathcal{L}_{UGAN-P}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + & \\
+      \lambda_{1} \mathcal{L}_{L1}(G) + & \lambda_{2} \mathcal{L}_{GDL}
    \end{aligned}
@@
 convolutions in the decoder are followed by a ReLU activation \cite{nair2010rectified} (no batch norm in the decoder).
-Exempt from this is the last
-layer of the decoder, which uses a TanH nonlinearity to match the input distribution of $[-1, 1]$. 
-%Batch normalization \cite{pmlr-v37-ioffe15} is used in the encoder portion
-%of the generator, but not in the decoder.
-%Following \cite{radford2015unsupervised}, we use batch normalization
-%\cite{pmlr-v37-ioffe15} throughout the generator, except for the last layer of the decoder.
+Exempt from this is the last layer of the decoder, which uses a TanH nonlinearity to match the input distribution of
+$[-1, 1]$.
 
@@
 which batch normalization would invalidate. The authors of \cite{gulrajani2017improved} recommend layer normalization
-\cite{ba2016layer}, but we found no significant improvements. In all of our experiments, we use $\lambda_{1} = 100$,
-$\lambda_{GP} = 10$, batch size of 32, Adam Optimizer \cite{kingma2014adam} with learning rate $1e-4$, and train for 100 epochs.
-Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$.
-For UGAN-P, we set $\lambda_{2} = 1.0$.
-Our implementation was done using the Tensorflow library \cite{abadi2016tensorflow}.
+\cite{ba2016layer}, but we found no significant improvements. In particular, the use of instance normalization
+\cite{ulyanov2016instance} in the generator has been shown to improve quality, but we leave that for future work.
+In all of our experiments, we use $\lambda_{1} = 100$, $\lambda_{GP} = 10$, batch size of 32, and the Adam Optimizer
+\cite{kingma2014adam} with learning rate $1e-4$. Following WGAN-GP, the discriminator is updated $n$ times for every
+update of the generator, where $n = 5$. For UGAN-P, we set $\lambda_{2} = 1.0$. Our implementation was done using the
+Tensorflow library \cite{abadi2016tensorflow}.
 \footnote{Code is available at https://github.com/cameronfabbri/Underwater-Color-Correction}
+All networks were trained from scratch on a GTX 1080 for 100 epochs. Inference on the GPU takes on average $ 0.0138s$,
+which is about 72 Frames Per Second (FPS). On a CPU (Intel Core i7-5930K), inference takes on average $ 0.1244s$, which
+is about 8 FPS. We find both of these measures acceptable for underwater tasks.
 
@@
 all images in $X$ with $F$. Figure 2 shows sample training pairs. When comparing with CycleGAN, we used a test set
-acquired from Flickr \footnote{How do I cite Flickr}.
+of 56 images acquired from Flickr \footnote{How do I cite Flickr}.
 
 \subsection{Evaluation}
-We train UGAN and UGAN-P on the image pairs generated by CycleGAN, and evaluate entirely on the images from the
+We train UGAN and UGAN-P on the image pairs generated by CycleGAN, and evaluate on the images from the
 test set, $Y$. Note that these images do not contain any ground truth, as they are original distorted images from
 Imagenet. Images for training and testing are of size $256 \times 256 \times 3$ and normalized between $[-1, 1]$.
+Figure 3 shows samples from the test set. Notably, these images contain varying amounts of noise. Both UGAN and UGAN-P
+are able to recover lost color information, as well as correct any color information this is present.
 
-While many of the distorted images in the test set contain a blue or green hue, that is not always the case. In certain
-environments, it is possible that objects close to the camera are undistorted with correct colors, while the background
+While many of the distorted images contain a blue or green hue over the entire image space, that is not always the case.
+In certain environments,
+it is possible that objects close to the camera are undistorted with correct colors, while the background
 of the image contains distortion. In these cases, we would like the network to only correct parts of the image that
-appear distorted. Figure X shows a sample of such an image, which implies it does not simply subtract a variable
-amount of green or blue from the entire image.
+appear distorted. The last row in Figure 3 shows a sample of such an image. The orange of the clownfish is left
+unchanged while the distorted sea anemone in the background has its color corrected.
+
+We use three metrics for a quantitative evaluation. First, we compare to CycleGAN, as it inherently learns an inverse
+mapping during the training of $F: X \rightarrow Y$, using the Canny edge detector
+\cite{canny1986computational} as it provides a color agnostic evaluation of the images in comparison to ground truth.
+Second, we compare local image patches to provide sharpness metrics on our images. Lastly, we show how an existing
+tracking algorithm for an underwater robot improves performance with generated images.
 
@@
 
-   Original & UGAN & UGAN-P \\
+   ~\quad Original & ~\quad UGAN & \quad UGAN-P \\
 
@@
 
+   \includegraphics[width=0.8in]{n01914609_1607_real} &
+   \includegraphics[width=0.8in]{n01914609_1607_gen_0} &
+   \includegraphics[width=0.8in]{n01914609_1607_gen_1} \\
+
+   \includegraphics[width=0.8in]{n02607072_6241_real} &
+   \includegraphics[width=0.8in]{n02607072_6241_gen_0} &
+   \includegraphics[width=0.8in]{n02607072_6241_gen_1} \\
+
 \end{tabular}
-\caption{Samples. The network can both recover color and also correct color if a small amount is present.}
+\caption{Samples from our Imagenet testing set. The network can both recover color and also correct color if a small amount is present.}
 \end{figure}
@@
 \subsection{Comparison to CycleGAN}
-\textbf{note also this is on cyclegan's training set - retraining now with a test set in mind....should be quick.}
 It is important to note that during the process of learning a mapping $F: X \rightarrow Y$, CycleGAN also learns a
-mapping $G: Y \rightarrow X$. Here we show that UGAN and UGAN-P provide superior performance.
-Second, show some general results. Explain how our network is able to do three very important things: 1) Restore an
-image to its natural colors with varying amounts of distortion, i.e. blue hue, green hue, aka not just one type of
-color distortion. 2) The network does not just subtract a certain hue from the entire image. Show how in the clownfish
-image, part of the image has good colors, while part of it doesn't. Our network is able to leave correct colors. Third,
-show that even images taken towards the water's surface, either above or below, are able to be restored correctly.
+mapping $G: Y \rightarrow X$. Here we show that UGAN and UGAN-P provide superior performance. We use a Canny edge
+detector \cite{canny1986computational} to provide a color agnostic evaluation of the images, as the original image
+contains distorted colors. Figure 4 shows the resulting images. We noticed that CycleGAN was mostly able to restore
+color, however the images contained various amounts noise. Because restoring color information should not alter the
+overall structure of the image, we measure the distance in the image space between the edges found in the original 
+and the generated images. Table 1 provides the measurements from Figure 4, as well as the average over the entire
+dataset.
 
-Third mention that since CycleGAN has a cycle consistent nature, compare their results. Then from there go into how
-ours are better by showing results from Canny Edge Detector.
+% I would like this table to match up with the figure showing edge detections. I wasn't able to
+% get letters on the left side at each row though.
+\begin{table}
+\centering
+\caption{Distances in image space}
+\begin{tabular}{| c | c | c | c |}
+   \hline
+   Row/Method & CycleGAN & UGAN & UGAN-P \\ \hline
+   A          & 116.45 & 85.71  & 86.15  \\ \hline
+   B          & 114.49 & 97.92  & 101.01 \\ \hline
+   C          & 120.84 & 96.53  & 97.57  \\ \hline
+   D          & 129.27 & 108.90 & 110.50 \\ \hline
+   Mean       & 111.60 & 94.91  & 96.51 \\ \hline
+\end{tabular}
+\end{table}
+
+\newpage
 
@@
 
-   Original & CycleGAN & UGAN & UGAN-P \\
+   ~\quad Original & ~CycleGAN & ~\quad UGAN & \quad UGAN-P \\
 

### 2017-09-15 nets/pix2pix.py

@@ -7,28 +7,36 @@ from tf_ops import *
 
 def netG(x, LOSS_METHOD):
       
-   enc_conv1 = tcl.conv2d(x, 64, 4, 2, activation_fn=tf.identity, normalizer_fn=tcl.batch_norm, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_enc_conv1')
+   enc_conv1 = tcl.conv2d(x, 64, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_enc_conv1')
+   enc_conv1 = instance_norm(enc_conv1)
    enc_conv1 = lrelu(enc_conv1)
    
-   enc_conv2 = tcl.conv2d(enc_conv1, 128, 4, 2, activation_fn=tf.identity, normalizer_fn=tcl.batch_norm, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_enc_conv2')
+   enc_conv2 = tcl.conv2d(enc_conv1, 128, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_enc_conv2')
+   enc_conv2 = instance_norm(enc_conv2)
    enc_conv2 = lrelu(enc_conv2)
    
-   enc_conv3 = tcl.conv2d(enc_conv2, 256, 4, 2, activation_fn=tf.identity, normalizer_fn=tcl.batch_norm, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_enc_conv3')
+   enc_conv3 = tcl.conv2d(enc_conv2, 256, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_enc_conv3')
+   enc_conv3 = instance_norm(enc_conv3)
    enc_conv3 = lrelu(enc_conv3)
 
-   enc_conv4 = tcl.conv2d(enc_conv3, 512, 4, 2, activation_fn=tf.identity, normalizer_fn=tcl.batch_norm, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_enc_conv4')
+   enc_conv4 = tcl.conv2d(enc_conv3, 512, 4, 2, activation_fn=tf.identity, weights_initializer=tf.random_normal_initializer(stddev=0.02), scope='g_enc_conv4')
[…]

### 2017-09-15 new_train.py

@@ -1,0 +1,270 @@
+'''
+
+   Main training file
+
+   The goal is to correct the colors in underwater images.
+   CycleGAN was used to create images that appear to be underwater.
+   Those will be sent into the generator, which will attempt to correct the
+   colors.
+
+'''
+
+import cPickle as pickle
+import tensorflow as tf
+from tqdm import tqdm
+from scipy import misc
+import numpy as np
+import argparse
+import ntpath
+import sys
+import os
+import glob
+import time
+
+sys.path.insert(0, 'ops/')
+sys.path.insert(0, 'nets/')
+from tf_ops import *
+
+import data_ops
+
+if __name__ == '__main__':
+   parser = argparse.ArgumentParser()
+   parser.add_argument('--LAYER_NORM',    required=False,default=0,type=int,help='Pixel shuffle')
+   parser.add_argument('--DATA',          required=False,default='underwater_imagenet',type=str,help='Dataset to use')
+   parser.add_argument('--EPOCHS',        required=False,default=4,type=int,help='Number of epochs for GAN')
+   parser.add_argument('--NETWORK',       required=False,default='pix2pix',type=str,help='Network to use')
+   parser.add_argument('--L1_WEIGHT',     required=False,default=100.,type=float,help='Weight for L1 loss')
+   parser.add_argument('--IG_WEIGHT',     required=False,default=1.,type=float,help='Weight for image gradient loss')
+   parser.add_argument('--BATCH_SIZE',    required=False,default=32,type=int,help='Batch size')
+   parser.add_argument('--LOSS_METHOD',   required=False,default='gan',help='Loss function for GAN')
+   parser.add_argument('--LEARNING_RATE', required=False,default=2e-5,type=float,help='Learning rate')
+   a = parser.parse_args()
+
+   LEARNING_RATE = float(a.LEARNING_RATE)
+   LOSS_METHOD   = a.LOSS_METHOD
+   BATCH_SIZE    = a.BATCH_SIZE
+   L1_WEIGHT     = float(a.L1_WEIGHT)
+   IG_WEIGHT     = float(a.IG_WEIGHT)
+   NETWORK       = a.NETWORK
+   EPOCHS        = a.EPOCHS
[…]

### 2017-09-15 tests/edge_detection.py

@@ -26,7 +26,7 @@ ugan_1_dist = []
 
 save_images = ['525931976_dffc710a58_o.png', '8032289_2af635da3c_o.png', '1056733511_8a8c0d9410_o.png', '2508954302_63b17667ce_o.png']
 
-save = 1
+save = 0
 
 # just open and close quick to wipe it
 results_file = open('edge_results/results.txt', 'w')

### 2017-09-15 train.py

@@ -18,8 +18,8 @@ import argparse
 import ntpath
 import sys
 import os
-import time
 import glob
+import time
 
 sys.path.insert(0, 'ops/')
 sys.path.insert(0, 'nets/')
@@ -214,7 +214,6 @@ if __name__ == '__main__':
    epoch_num = step/(num_train/BATCH_SIZE)
 
    while epoch_num < EPOCHS:
-   
       epoch_num = step/(num_train/BATCH_SIZE)
 
       idx = np.random.choice(np.arange(num_train), BATCH_SIZE, replace=False)

### 2017-09-15 files/paper/paper.tex
JUNAED: Edited and left comments as 'starnotes' in the file. Please ensure you address those, and fix all the references to images. Do not hardcode image numbers, but use \ref and \labels. I have fixed figure 1, so use that as a reference.

@@
 
-\documentclass[conference,reqno]{IEEEtran}
+\documentclass[letterpaper, 10pt, conference]{ieeeconf}
 
@@
 \usepackage{url}
+\usepackage{hyperref} % JS: Remove this if you cannot compile.
+
+\pdfminorversion=4
+% Junaed's definition of a sidenote to look into
+\newcommand{\marginlabel}[1]{\mbox{}\marginpar[\raggedleft\hspace{0pt}{#1}]{
+\raggedright\hspace{0pt}{#1}}}
+\newcommand{\starnote}[1]{\marginlabel{$\bigstar$}\textbf{[#1]}}
+\newcommand{\nostarnote}[1]{}
+\newcommand{\baad}[1]{} 
+% End Junaed's definition
+
+\IEEEoverridecommandlockouts
+\overrideIEEEmargins
+
 % url.sty was written by Donald Arseneau. It provides better support for
@@
 
-\begin{document}
+\title{UGAN: Underwater Image Restoration using Generative Adversarial Networks}
+\author{Cameron Fabbri$^{1}$, Md Jahidul Islam$^{2}$, and Junaed Sattar$^{3}$
+\thanks{				
+  The authors are with the Department of Computer Science and Engineering, University of Minnesota-Twin  Cities, MN 55455, USA. \newline
+ {\tt\small\{$^{1}$fabbr013, $^{2}$islam034, $^{3}$junaed\}@umn.edu} 
+}
+}
 
-\title{UGAN: Underwater Image Restoration using Generative Adversarial Networks}
-
-\author{\IEEEauthorblockN{Cameron Fabbri}
-\IEEEauthorblockA{Information Directorate\\
-Air Force Research Laboratory \\
-Rome, NY, USA.\\
-cameron.fabbri@us.af.mil}
-\and
-\IEEEauthorblockN{Md Jahidul Islam}
-\IEEEauthorblockA{University of Minnesota- Twin Cities\\
-MN, USA.\\
-islam034@umn.edu }
-\and
-\IEEEauthorblockN{Junaed Sattar}
-\IEEEauthorblockA{University of Minnesota- Twin Cities\\
-MN, USA.\\
-junaed@umn.edu
-}}
+% \author{\IEEEauthorblockN{Cameron Fabbri$^{1}$}
+% \IEEEauthorblockA{Information Directorate\\
+% Air Force Research Laboratory \\
+% Rome, NY, USA.\\
+% cameron.fabbri@us.af.mil}
+% \and
+% \IEEEauthorblockN{Md Jahidul Islam \& Junaed Sattar}
+% \IEEEauthorblockA{Department of Computer Science and Engineering\\University of Minnesota- Twin Cities, MN, USA.\\
+% \{islam034, junaed\}@umn.edu }
+% \and
+% \IEEEauthorblockN{Junaed Sattar}
+% \IEEEauthorblockA{Department of Computer Science and Engineering\\University of Minnesota- Twin Cities,MN, USA.\\
+% junaed@umn.edu
+%}
 
@@
 
+\begin{document}
+
 % make the title area
@@
 \begin{abstract}
-Autonomous underwater robots often rely on visual input for decision making due to its non-intrusive and passive nature.
-However, due to many factors such as light refraction, particles in the water, and color distortion, images are often times very noisy.
-This paper propose a method using Generative Adversarial Networks (GANs) to denoise underwater images, and show that these 
-images provide both increased accuracy for an underwater tracking algorithm, as well as a more visually appealing image.
-Furthermore, we show how recently proposed methods are able to generate a dataset for the purpose of underwater image reconstruction.
+Autonomous underwater vehicles (AUVs) rely on a variety of sensors -- acoustic, inertial and visual -- for intelligent decision making. Due
+to its non-intrusive, passive nature, and high information content, vision is an attractive sensing modality, particularly at shallower
+depths. However, factors such as light refraction and absorption, suspended particles in the water, and color distortion affect the quality
+of visual data, resulting in noisy and distorted images. AUVs that rely on visual sensing thus face difficult challenges, and consequently
+exhibit poor performance on vision-driven tasks. This paper proposes a method to improve the quality of visual underwater scenes using
+Generative Adversarial Networks (GANs), with the goal of improving input to vision-driven behaviors further down the autonomy
+pipeline. Furthermore, we show how recently proposed methods are able to generate a dataset for the purpose of such underwater image
+reconstruction\starnote{Reconstruction meaning what we are doing here, right? So this is a contribution too, to show how CycleGAN is used to
+generate the dataset, correct?}. For any visually-guided underwater robots, this improvement can result in increased safety and reliability
+through robust visual perception. To that effect, we present quantitative and qualitative data which demonstrates that images corrected
+through the proposed approach generate more visually appealing images, and also provide increased accuracy for an underwater diver tracking
+algorithm.
 \end{abstract}
 
-\IEEEpeerreviewmaketitle
+%\IEEEpeerreviewmaketitle
 
 \section{Introduction}
-TODO - talk about having to go back to the same location if you want to get good/bad pairs of the ``same'' image.
-Vision is a commonly used sensor in autonomous underwater robots due to its non-intrusive, passive, and energy
-effecient nature. The monitoring of coral reefs \cite{shkurti2012multi}, deep ocean exploration
-\cite{whitcomb2000advances}, and mapping of the seabed are all tasks suitable for autonomous robots because they
-provide safety by taking the risk instead of a human. Despite the advantages vision provides, many underwater
-environments can be quite noisy due to light refraction and particles present in the water. Because red wavelengths are
-quickly absorbed by water, images tend to have a green or blue hue to them. As you go deeper, this worsens as more
-and more red wavelengths are being absorbed. This extremely non-linear distortion has many factors such as the amount
-of light present (overcast vs sunny or depth), particles in the water, time of day, and the camera being used. This may
-cause difficulty in tasks such as segmentation, tracking, or classification due to their indirect or direct use of
-color.
+TODO - talk about having to go back to the same location if you want to get good/bad pairs of the ``same'' image.\starnote{I assume Cam will
+do this?}  Underwater robotics has been a steadily growing subfield of autonomous field robotics, assisted by the advent of novel platforms,
+sensors and propulsion mechanisms. While autonomous underwater vehicles are often equipped with a variety of sensors, visual sensing is an
+attractive option because of its non-intrusive, passive, and energy efficient nature. The monitoring of coral reefs \cite{shkurti2012multi},
+deep ocean exploration \cite{whitcomb2000advances}, and mapping of the seabed\starnote{Citation?} are a number of tasks where
+visually-guided AUVs and ROVs (Remotely Operated Vehicles) have seen widespread use. Use of these robots ensures humans are not exposed to
+the hazards of underwater exploration, as they no longer need to venture to the depths (which was how such tasks were carried out in the
+past). Despite the advantages of using vision, underwater environments pose unique challenges to visual sensing, as phenomena such as light
+refraction, absorption and scattering from suspended particles can greatly affect the optics of light. As an example, because red
+wavelengths are quickly absorbed by water, images tend to have a green or blue hue to them. As one goes deeper, this effect worsens, as more
+and more red hue is absorbed. This distortion is extremely non-linear in nature, and is affected by a large number of factors, such as the
+amount of light present (overcast versus sunny, operational depth), amount of particles in the water, time of day, and the camera being
+used. This may cause difficulty in tasks such as segmentation, tracking, or classification due to their indirect or direct use of color.
 
-As color and illumination begin to change with the depth, vision based algorithms must be very generalizable in order
-to work within the depth ranges a robot may operate in. Because of the high cost and difficulty of acquiring a
-variety of underwater data, as well as the high amount of noise introduced, many algorithms may perform poorly in
-these different domains. Figure 1 shows the high variability that may occur in underwater environments. A step towards a
-solution to this
-issue is to be able to restore the images such that they appear to be above water, i.e., with colors corrected and
-particles removed. By performing a many to one mapping of these domains from underwater to not underwater (what the
-image would look like in the air), algorithms that have
+As color and illumination begin to change with the depth, vision-based algorithms must need to be very generalizable in order to work within
+the depth ranges a robot may operate in. Because of the high cost and difficulty of acquiring a variety of underwater data to train a visual
+system on, as well as the high amount of noise introduced, algorithms may (and do) perform poorly in these different
+domains. Figure~\ref{fig:samples}\starnote{DO NOT USE HARDCODED FIGURE NUMBERS!!! Use a label\{\} right before the caption, and then refer
+to it using the ref\{\} command as I have done here -- see the \LaTeX source.} shows the high variability in visual scenes that may occur in
+underwater environments. A step towards a solution to this issue is to be able to restore the images such that they appear to be above
+water, \emph{i.e.}, with colors corrected and suspended particles removed from the scene. By performing a many-to-one mapping of these
+domains from underwater to not underwater (what the image would look like above water), algorithms that have difficulty performing across
+multiple forms of noise may be able to focus only one clean domain.
 
@@
 \end{tabular}
+\label{fig:samples}
 \caption{Sample underwater images displaying the diversity of distortion that can occur. \textbf{Maybe say something about how
@@
 
-\noindent difficulty performing across multiple forms of noise may be able to focus only one clean domain.
-
-Deep neural networks have been shown to be powerful non-linear function approximators, especially in the field of
-vision. Often times, these networks recquire large amounts of data, either labeled or paired with ground truth.
-For the problem of automatically colorizing grayscale images, paired training data is essentially free due to the
-fact that any color image can be converted to black and white. However, underwater images distorted by either color
-or some other visual effect lack ground truth. We use the recently proposed CycleGAN \cite{zhu2017unpaired}, which
-learns to translate an image from domain $X$ to domain $Y$, as a way to generate a paired dataset. By letting $X$ be
-a set of undistorted underwater images, and $Y$ be a set of distorted underwater images, we can generate an image
-that appears to be underwater while retaining ground truth.
+Deep neural networks have been shown to be powerful non-linear function approximators, especially in the field of vision\starnote{Cite the
+  canonical Deep Learning paper here please}. Often times, these networks require large amounts of data, either labeled or paired with
+ground truth. For the problem of automatically colorizing grayscale images\starnote{CITE something on this?}, paired training data is
+readily available due to the fact that any color image can be converted to black and white. However, underwater images distorted by either
+color or some other phenomenon lack ground truth, which is a major hindrance towards adopting a similar approach for correction.
+This paper proposes a technique based on Generative Adversarial Networks (GANs) to improve the quality of visual underwater scenes with the goal of improving the performance of vision-driven behaviors for autonomous underwater robots\starnote{Summarize the approach here.
+Then talk about datasets as you have done already.} We use the recently proposed CycleGAN~\cite{zhu2017unpaired} approach, which learns to translate an image from any arbitrary domain $X$ to another arbitrary domain $Y$, as a way to generate a paired dataset.
+By letting $X$ be a set of undistorted underwater images\starnote{need to say where we find the undistorted ones}, and $Y$ be a set of distorted underwater images, we can generate an image that appears to be underwater while retaining ground truth.
 
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2017-09-15 files/paper/paper.tex
update

@@
 Deep neural networks have been shown to be powerful non-linear function approximators, especially in the field of vision\starnote{Cite the
-  canonical Deep Learning paper here please}. Often times, these networks require large amounts of data, either labeled or paired with
-ground truth. For the problem of automatically colorizing grayscale images\starnote{CITE something on this?}, paired training data is
+  canonical Deep Learning paper here please} \cite{krizhevsky2012imagenet}. Often times, these networks require large amounts of data, either labeled or paired with
+ground truth. For the problem of automatically colorizing grayscale images \cite{zhang2016colorful}\starnote{CITE something on this?}, paired training data is
 readily available due to the fact that any color image can be converted to black and white. However, underwater images distorted by either

### 2017-09-15 tests/compare_hist.py
update

@@ -3,7 +3,6 @@ import numpy as np
 
 for i in range(1,5):
 
-   # 
    flickr = cv2.imread('result_images/flickr_crop'+str(i)+'_og.png')
    cgan   = cv2.imread('result_images/cgan_crop'  +str(i)+'_og.png')
    ugan   = cv2.imread('result_images/ugan_crop'  +str(i)+'_og.png')

### 2017-09-15 tests/psnr.py

@@ -14,10 +14,10 @@ for i in range(1,5):
    uganp  = cv2.imread('result_images/uganp_crop' +str(i)+'_og.png')
 
 
-   print 'crop',i
-   print psnr(flickr,cgan)
-   print psnr(flickr,ugan)
-   print psnr(flickr,uganp)
+   print 'crop  ',i
+   print 'cgan: ',psnr(flickr,cgan)
+   print 'ugan: ',psnr(flickr,ugan)
+   print 'uganp:',psnr(flickr,uganp)
    print
 
 

### 2017-09-15 tests/stats.py

@@ -1,36 +1,27 @@
 import scipy.misc as misc
 import math
 import numpy as np
+import cv2
 
-# our image
-image1 = misc.imread('files/paper/images/n01496331_11938_gen_IG_0.0.png').astype('float32')
-image1 = image1/255.0
+for i in range(1,5):
 
-#cyclegan image
-image2 = misc.imread('files/paper/images/n01496331_11938.png').astype('float32')
-image2 = image2/255.0
+   flickr = cv2.imread('result_images/flickr_crop'+str(i)+'_og.png')/255.0
+   cgan   = cv2.imread('result_images/cgan_crop'  +str(i)+'_og.png')/255.0
+   ugan   = cv2.imread('result_images/ugan_crop'  +str(i)+'_og.png')/255.0
+   uganp  = cv2.imread('result_images/uganp_crop' +str(i)+'_og.png')/255.0
 
-# real image
-image3 = misc.imread('files/paper/images/n01496331_11938_real.png').astype('float32')
-image3 = image3/255.0
-
-img1 = image1[50:150, :100, :]
-img2 = image2[50:150, :100, :]
-img3 = image3[50:150, :100, :]
-
-misc.imsave('original.png', image1)
-misc.imsave('ours.png', img1)
-misc.imsave('theirs.png', img2)
-misc.imsave('real.png', img3)
-
-print 'Variance'
-print 'ours:     ',np.var(img1)
-print 'cyclegan: ',np.var(img2)
-print 'real:     ',np.var(img3)
-print
-print 'Mean'
-print 'ours:     ',np.mean(img1)
-print 'cyclegan: ',np.mean(img2)
-print 'real:     ',np.mean(img3)
-
-
+   print 'crop',i
+   print 'Variance'
+   print 'real:  ',np.var(flickr)
+   print 'cgan:  ',np.var(cgan)
+   print 'ugan:  ',np.var(ugan)
+   print 'uganp: ',np.var(uganp)
+   print
+   print 'Mean'
+   print 'real:  ',np.mean(flickr)
+   print 'cgan:  ',np.mean(cgan)
+   print 'ugan:  ',np.mean(ugan)
+   print 'uganp: ',np.mean(uganp)
+   print
+   print '---'
+   print

### 2017-09-15 tests/compare_hist.py
update

@@ -1,5 +1,6 @@
 import cv2
 import numpy as np
+from scipy.stats import signaltonoise
 
 for i in range(1,5):
 
@@ -37,6 +38,16 @@ for i in range(1,5):
    print 'flickr_cgan:',a
    print 'flickr_ugan:',b
    print 'flickr_uganp:',c
+   print
+   print signaltonoise(flickr, axis=None)
+   print signaltonoise(cgan, axis=None)
+   print signaltonoise(ugan, axis=None)
+   print signaltonoise(uganp, axis=None)
+   print
+   print cv2.Laplacian(flickr, cv2.CV_64F).var()
+   print cv2.Laplacian(cgan, cv2.CV_64F).var()
+   print cv2.Laplacian(ugan, cv2.CV_64F).var()
+   print cv2.Laplacian(uganp, cv2.CV_64F).var()
    print 
    print '---'
    print

### 2017-09-15 tests/stats.py

@@ -1,27 +1,0 @@
-import scipy.misc as misc
-import math
-import numpy as np
-import cv2
-
-for i in range(1,5):
-
-   flickr = cv2.imread('result_images/flickr_crop'+str(i)+'_og.png')/255.0
-   cgan   = cv2.imread('result_images/cgan_crop'  +str(i)+'_og.png')/255.0
-   ugan   = cv2.imread('result_images/ugan_crop'  +str(i)+'_og.png')/255.0
-   uganp  = cv2.imread('result_images/uganp_crop' +str(i)+'_og.png')/255.0
-
-   print 'crop',i
-   print 'Variance'
-   print 'real:  ',np.var(flickr)
-   print 'cgan:  ',np.var(cgan)
-   print 'ugan:  ',np.var(ugan)
-   print 'uganp: ',np.var(uganp)
-   print
-   print 'Mean'
-   print 'real:  ',np.mean(flickr)
-   print 'cgan:  ',np.mean(cgan)
-   print 'ugan:  ',np.mean(ugan)
-   print 'uganp: ',np.mean(uganp)
-   print
-   print '---'
-   print

### 2017-09-15 tests/compare_hist.py
update

@@ -2,6 +2,33 @@ import cv2
 import numpy as np
 from scipy.stats import signaltonoise
 
+def gdl(generated, true):
+
+   true_x_shifted_right = true[1:,:,:]
+   true_x_shifted_left = true[:-1,:,:]
+   true_x_gradient = np.abs(true_x_shifted_right - true_x_shifted_left)
+
+   generated_x_shifted_right = generated[1:,:,:]
+   generated_x_shifted_left = generated[:-1,:,:]
+   generated_x_gradient = np.abs(generated_x_shifted_right - generated_x_shifted_left)
+   
+   loss_x_gradient = np.linalg.norm(true_x_gradient - generated_x_gradient)
+
+   true_y_shifted_right = true[:,1:,:]
+   true_y_shifted_left = true[:,:-1,:]
+   true_y_gradient = np.abs(true_y_shifted_right - true_y_shifted_left)
+
+   generated_y_shifted_right = generated[:,1:,:]
+   generated_y_shifted_left = generated[:,:-1,:]
+   generated_y_gradient = np.abs(generated_y_shifted_right - generated_y_shifted_left)
+    
+   loss_y_gradient = np.linalg.norm(true_y_gradient - generated_y_gradient)
+
+   loss = loss_x_gradient + loss_y_gradient
+
+   return loss
+
+
 for i in range(1,5):
 
    flickr = cv2.imread('result_images/flickr_crop'+str(i)+'_og.png')
@@ -23,32 +50,38 @@ for i in range(1,5):
    ugan   = ugan/255.0
    uganp  = uganp/255.0
 
-   print 'crop',i
-   print
-   print 'flickr_mean :',np.mean(flickr)
-   print 'cgan_mean   :',np.mean(cgan)
-   print 'ugan_mean   :',np.mean(ugan)
-   print 'uganp_mean  :',np.mean(uganp)
-   print
-   print 'flickr_var  :',np.var(flickr)
-   print 'cgan_var    :',np.var(cgan)
-   print 'ugan_var    :',np.var(ugan)
-   print 'uganp_var   :',np.var(uganp)
-   print
-   print 'flickr_cgan:',a
-   print 'flickr_ugan:',b
-   print 'flickr_uganp:',c
-   print
-   print signaltonoise(flickr, axis=None)
-   print signaltonoise(cgan, axis=None)
-   print signaltonoise(ugan, axis=None)
-   print signaltonoise(uganp, axis=None)
[…]

### 2017-09-15 files/paper/paper.tex
update

--- 2017-09-15 files/paper/paper.tex
@@
-%% bare_conf.tex
-%% V1.4
-%% 2012/12/27
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8 or later) with an IEEE conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex,
-%%                    bare_jrnl_transmag.tex
-%%*************************************************************************
-
 \documentclass[letterpaper, 10pt, conference]{ieeeconf}
@@
 \graphicspath{ {images/}{images/figure1/}{images/figure2/}{images/figure3/} {images/edges/}}
-%\graphicspath{{images/failures/}}
-%\graphicspath{{images/figure1/}}
 
@@
 \overrideIEEEmargins
-
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
-% Basically, \url{my_url_here}.
 
@@
 
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-% 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
 \begin{document}
 
-% make the title area
 \maketitle
 
-% As a general rule, do not put math, special symbols or citations
-% in the abstract
 \begin{abstract}
@@
 \section{Introduction}
-TODO - talk about having to go back to the same location if you want to get good/bad pairs of the ``same'' image.\starnote{I assume Cam will
-do this?}  Underwater robotics has been a steadily growing subfield of autonomous field robotics, assisted by the advent of novel platforms,
+%TODO - talk about having to go back to the same location if you want to get good/bad pairs of the ``same'' image.\starnote{I assume Cam will
+%do this?}
+Underwater robotics has been a steadily growing subfield of autonomous field robotics, assisted by the advent of novel platforms,
 sensors and propulsion mechanisms. While autonomous underwater vehicles are often equipped with a variety of sensors, visual sensing is an
@@
 system on, as well as the high amount of noise introduced, algorithms may (and do) perform poorly in these different
-domains. Figure~\ref{fig:samples}\starnote{DO NOT USE HARDCODED FIGURE NUMBERS!!! Use a label\{\} right before the caption, and then refer
-to it using the ref\{\} command as I have done here -- see the \LaTeX source.} shows the high variability in visual scenes that may occur in
+domains. Figure~\ref{fig:samples} shows the high variability in visual scenes that may occur in
 underwater environments. A step towards a solution to this issue is to be able to restore the images such that they appear to be above
@@
 \label{fig:samples}
-\caption{Sample underwater images displaying the diversity of distortion that can occur. \textbf{Maybe say something about how
-some images lost all color, but some kept some color for close objects.}}
+\caption{Sample underwater images displaying the diversity of distortion that can occur. Due to the variety of distances
+of objects in the image, there is a varying amount of color loss and distortion.}
 \end{figure}
 
-Deep neural networks have been shown to be powerful non-linear function approximators, especially in the field of vision\starnote{Cite the
-  canonical Deep Learning paper here please}. Often times, these networks require large amounts of data, either labeled or paired with
-ground truth. For the problem of automatically colorizing grayscale images\starnote{CITE something on this?}, paired training data is
+Deep neural networks have been shown to be powerful non-linear function approximators, especially in the field of vision \cite{krizhevsky2012imagenet}.
+Often times, these networks require large amounts of data, either labeled or paired with
+ground truth. For the problem of automatically colorizing grayscale images \cite{zhang2016colorful}, paired training
+data is
 readily available due to the fact that any color image can be converted to black and white. However, underwater images distorted by either
 color or some other phenomenon lack ground truth, which is a major hindrance towards adopting a similar approach for correction.
-This paper proposes a technique based on Generative Adversarial Networks (GANs) to improve the quality of visual underwater scenes with the goal of improving the performance of vision-driven behaviors for autonomous underwater robots\starnote{Summarize the approach here.
-Then talk about datasets as you have done already.} We use the recently proposed CycleGAN~\cite{zhu2017unpaired} approach, which learns to translate an image from any arbitrary domain $X$ to another arbitrary domain $Y$, as a way to generate a paired dataset.
-By letting $X$ be a set of undistorted underwater images\starnote{need to say where we find the undistorted ones}, and $Y$ be a set of distorted underwater images, we can generate an image that appears to be underwater while retaining ground truth.
+This paper proposes a technique based on Generative Adversarial Networks (GANs) to improve the quality of visual underwater scenes with the goal of improving the performance of vision-driven behaviors for autonomous underwater robots
+%\starnote{Summarize the approach here. Then talk about datasets as you have done already.}
+We use the recently proposed CycleGAN~\cite{zhu2017unpaired} approach, which learns to translate an image from any arbitrary domain $X$ to another arbitrary domain $Y$ \textit{without} image pairs, as a way to generate a paired dataset.
+By letting $X$ be a set of undistorted underwater images\starnote{need to say where we find the undistorted ones}, and
+$Y$ be a set of distorted underwater images, we can generate an image that appears to be underwater while retaining
+ground truth.
 
@@
 \cite{zhang2016colorful,iizuka2016let}, most are focused on the task of grayscale to color.
-The work of \cite{torres2005color} used an energy minimization formulation using a Markov Random Field. 
-MORE RELATED BLAH. Many use physics based models to directly model the light source and such.
-Most similar to our line of work is the recently proposed WaterGAN \cite{li2017watergan}, which uses
-GANs for color correction of underwater images. As ground truth pairs do not exist for underwater images,
-their first step is to structure a generator to create realistic underwater images. Their generator model
-can be broken down into three stages: 1) Attenuation, which accounts for range-dependent attenuation of light.
+The work of \cite{torres2005color} uses an energy minimization formulation using a Markov Random Field. 
+Many employ the use of a physics based model to directly model light refraction \cite{jordt2014underwater}.
+Most similar to our line of work is the recently proposed WaterGAN \cite{li2017watergan}, which uses an adversarial
+approach towards generating realistic underwater images. Their generator model can be broken down into three stages:
+1) Attenuation, which accounts for range-dependent attenuation of light.
 2) Scattering, which models the haze effect caused by photons scattering back towards the image sensor. 3)
 Vingetting, which produces a shading effect on the image corners that can be caused by certain camera lenses.
-Opposed to our work, they use a GAN for generating the underwater images and Euclidean loss for color correction,
-where as we use a GAN for both. Furthermore, they require depth information during the training of WaterGAN,
-whereas we only require two separate image domains.
+Opposed to our work, they use a GAN for generating the underwater images and strictly Euclidean loss for color
+correction, where as we use a GAN for both. Furthermore, they require depth information during the training of WaterGAN,
+whereas we only require two separate image domains throughout.
 
@@
 Much like the work of \cite{isola2016image}, we use image pairs from two domains an input and ground truth.
+\starnote{Somewhere I think we should mention that unpaired image to image translation is more difficult, and
+that cyclegan is a good way to generate a dataset in such a way to do this with image pairs.}
 
@@
 dataset of images. Given two datasets $X$ and $Y$, where $I^C \in X$ and $I^D \in Y$, CycleGAN learns a mapping
-$F: X \rightarrow Y$. Figure 2 shows paired samples generated from CycleGAN. From this paired dataset we train a
+$F: X \rightarrow Y$. Figure ~\ref{fig:cgan_samples} shows paired samples generated from CycleGAN. From this paired dataset we train a
 generator $G$ to learn the function $f: I^D \rightarrow I^C$. It should be noted that during our data generation process,
@@
 image to try and fool the discriminator, which is trained to distinguish be between distorted and non-distorted
-underwater images. In the original GAN formulation, the goal is to solve the minimax problem: \newline
+underwater images. In the original GAN formulation, our goal is to solve the minimax problem:
 
@@
 \end{tabular}
+\label{fig:cgan_samples}
 \caption{Paired samples of ground truth and distorted images generated by CycleGAN. Top row: Ground truth.
@@
 directly penalizing the differences of image gradient predictions in the generator, as proposed by
-\cite{mathieu2015deep}. Given a ground truth image $I^C$, predicted image $I^P = G(I^C)$, and $\alpha \geq 1$, the
+\cite{mathieu2015deep}. Given a ground truth image $I^C$, predicted image $I^P = G(I^D)$, and $\alpha \geq 1$, the
 Gradient Difference Loss (GDL) is given by
@@
       \mathcal{L}_{GDL}(I^C, I^P) = \\ \sum\limits_{i,j} || & I^C_{i,j} - I^C_{i-1,j}| - | I^P_{i,j} - I^P_{i-1,j}||^{\alpha} + \\
-      || & I^C_{i,j-1} - I^C_{i,j}| - | I^P_{i,j-1} - I^P_{i,j}||^{\alpha},
+      || & I^C_{i,j-1} - I^C_{i,j}| - | I^P_{i,j-1} - I^P_{i,j}||^{\alpha}.
    \end{aligned}
+   \label{gdl_eq}
 \end{equation}
@@
 \noindent In our experiments, we denote our network as UGAN-P when considering the GDL, which can be expressed as
+\starnote{I don't like the - in this equation, but don't know how to change it to be shorter}
 
@@
 generator uses kernel size $4 \times 4$ with stride 2. Convolutions in the encoder portion of the network are followed
-by batch normalization \cite{pmlr-v37-ioffe15} and a leaky ReLU activation with slope $0.02$, while transpose
+by batch normalization \cite{pmlr-v37-ioffe15} and a leaky ReLU activation with slope $0.2$, while transpose
 convolutions in the decoder are followed by a ReLU activation \cite{nair2010rectified} (no batch norm in the decoder).
 Exempt from this is the last layer of the decoder, which uses a TanH nonlinearity to match the input distribution of
-$[-1, 1]$.
+$[-1, 1]$. Recent work has proposed Instance Normalization \cite{ulyanov2016instance} to improve quality
+in image-to-image translation tasks, however we observed no added benefit.
 
-Our discriminator is modeled after that of \cite{radford2015unsupervised}, except no batch normalization is used. This
-is due to the fact that we penalize the norm of the discriminator's gradient with respect to each input individually,
-which batch normalization would invalidate. The authors of \cite{gulrajani2017improved} recommend layer normalization
-\cite{ba2016layer}, but we found no significant improvements. In particular, the use of instance normalization
-\cite{ulyanov2016instance} in the generator has been shown to improve quality, but we leave that for future work.
+Our fully convolutional discriminator is modeled after that of \cite{radford2015unsupervised}, except no batch
+normalization is used. This is due to the fact that WGAN-GP penalizes the norm of the discriminator's gradient with
+respect to each input individually, which batch normalization would invalidate. The authors of
+\cite{gulrajani2017improved} recommend layer normalization \cite{ba2016layer}, but we found no significant improvements.
+Our discriminator is modeled as a PatchGAN \cite{isola2016image,li2016precomputed,}, which discriminates at the level of
+image patches. As opposed to a regular discriminator, which outputs a scalar value corresponding to real or fake, our
+PatchGAN discriminator outputs a $32 \times 32 \times 1$ feature. This provides a metric for high level frequencies,
+which is combinied with the low level frequencies from the $L1$ loss.
+
 In all of our experiments, we use $\lambda_{1} = 100$, $\lambda_{GP} = 10$, batch size of 32, and the Adam Optimizer
-\cite{kingma2014adam} with learning rate $1e-4$. Following WGAN-GP, the discriminator is updated $n$ times for every
+\cite{kingma2014adam} with learning rate $1e-4$. When considering the GDL, we use $\alpha = 1$. Following WGAN-GP, the discriminator is updated $n$ times for every
 update of the generator, where $n = 5$. For UGAN-P, we set $\lambda_{2} = 1.0$. Our implementation was done using the
 Tensorflow library \cite{abadi2016tensorflow}.
-\footnote{Code is available at https://github.com/cameronfabbri/Underwater-Color-Correction}
+\footnote{Code is available at \url{https://github.com/cameronfabbri/Underwater-Color-Correction}}
 All networks were trained from scratch on a GTX 1080 for 100 epochs. Inference on the GPU takes on average $ 0.0138s$,
@@
 \footnote{https://www.youtube.com/watch?v=QmRFmhILd5o}. Subsets of Imagenet containing underwater images
-were selected for the training of CycleGAN, and manually separated into two classes. We let $X$ be the set of
+were selected for the training of CycleGAN, and manually separated into two classes based on visual inspection. We let
+$X$ be the set of
 underwater images with no distortion, and $Y$ be the set of underwater images with distortion. $X$ contained 6143
@@
 images from $X$ appeared to have come from $Y$. Finally, our image pairs for training data were generated by distorting
-all images in $X$ with $F$. Figure 2 shows sample training pairs. When comparing with CycleGAN, we used a test set
-of 56 images acquired from Flickr \footnote{How do I cite Flickr}.
+all images in $X$ with $F$. Figure ~\ref{cgan_samples} shows sample training pairs. When comparing with CycleGAN, we used a test set
+of 56 images acquired from Flickr \textsuperscript{TM}.
 
@@
 Imagenet. Images for training and testing are of size $256 \times 256 \times 3$ and normalized between $[-1, 1]$.
-Figure 3 shows samples from the test set. Notably, these images contain varying amounts of noise. Both UGAN and UGAN-P
+Figure ~\ref{test_samples} shows samples from the test set. Notably, these images contain varying amounts of noise. Both UGAN and UGAN-P
 are able to recover lost color information, as well as correct any color information this is present.
@@
 of the image contains distortion. In these cases, we would like the network to only correct parts of the image that
-appear distorted. The last row in Figure 3 shows a sample of such an image. The orange of the clownfish is left
+appear distorted. The last row in Figure ~\ref{test_samples} shows a sample of such an image. The orange of the clownfish is left
 unchanged while the distorted sea anemone in the background has its color corrected.
@@
 mapping during the training of $F: X \rightarrow Y$, using the Canny edge detector
-\cite{canny1986computational} as it provides a color agnostic evaluation of the images in comparison to ground truth.
+\cite{canny1986computational}. This provides a color agnostic evaluation of the images in comparison to ground truth.
 Second, we compare local image patches to provide sharpness metrics on our images. Lastly, we show how an existing
@@
 \caption{Samples from our Imagenet testing set. The network can both recover color and also correct color if a small amount is present.}
+\label{fig:test_samples}
 \end{figure}
@@
 It is important to note that during the process of learning a mapping $F: X \rightarrow Y$, CycleGAN also learns a
-mapping $G: Y \rightarrow X$. Here we show that UGAN and UGAN-P provide superior performance. We use a Canny edge
-detector \cite{canny1986computational} to provide a color agnostic evaluation of the images, as the original image
-contains distorted colors. Figure 4 shows the resulting images. We noticed that CycleGAN was mostly able to restore
-color, however the images contained various amounts noise. Because restoring color information should not alter the
-overall structure of the image, we measure the distance in the image space between the edges found in the original 
-and the generated images. Table 1 provides the measurements from Figure 4, as well as the average over the entire
-dataset.
+mapping $G: Y \rightarrow X$. Here we show that UGAN and UGAN-P provide superior performance. We use the Canny edge
+detector \cite{canny1986computational} to provide a color agnostic evaluation of the images, as the original contain
+distorted colors and cannot be compared back to as ground truth. Due to the fact that restoring color information
+should not alter the overall structure of the image, we measure the distance in the image space between the edges
+found in the original and generated images. Figure ~\ref{canny_samples} shows the original images and results from
+edge detection. Table 1 provides the measurements from Figure ~\ref{canny_samples}, as well as the average over the
+entire dataset.
+
+We explore the artifacts of content loss, as seen in Figure ~\ref{zoom}. In particular, we compare local statistics
+of the highlighted image patches, where each image patch is resized to $64 \times 64$. We use the GDL
+\cite{mathieu2015deep} from (\ref{gdl_eq}) as a sharpness measure.
 
@@
 the result of the edge detector.}
+\label{fig:canny_samples}
 \end{figure}
@@
 
+   \qquad \qquad ~ Original & \qquad \qquad CycleGAN & \qquad \qquad ~ \textbf{UGAN} & \qquad \qquad \textbf{UGAN-P} \\
+
    \includegraphics[width=1.7in]{flickr_cmp} &
@@
    \includegraphics[width=1.7in]{ugan_cmp} &
-   \includegraphics[width=1.7in]{uganp_cmp} \\
+   \includegraphics[width=1.7in]{uganp_cmp} \\ [-11ex]
 
@@
 \end{figure*}
+
 \begin{figure*}
-\begin{tabular}{p{1.9cm} p{1.9cm} p{1.9cm} p{1.9cm} p{1.9cm} p{1.9cm} p{1.9cm} p{1.9cm} }
+\begin{tabular}{p{1.8cm} p{1.85cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.9cm} }
 
@@
 \end{tabular}
-\caption{Zooming in on comparisons.}
+\caption{Comparison of local image patches. Each patch was resized to $64 \times 64$.}
+\label{fig:zoom}
 \end{figure*}
@@
 \end{tabular}
+\label{fig:mdpm}
 \vspace{4mm}

### 2017-09-15 files/paper/paper.tex
update

@@
 \cite{gulrajani2017improved} recommend layer normalization \cite{ba2016layer}, but we found no significant improvements.
-Our discriminator is modeled as a PatchGAN \cite{isola2016image,li2016precomputed,}, which discriminates at the level of
+Our discriminator is modeled as a PatchGAN \cite{isola2016image,li2016precomputed}, which discriminates at the level of
 image patches. As opposed to a regular discriminator, which outputs a scalar value corresponding to real or fake, our
-PatchGAN discriminator outputs a $32 \times 32 \times 1$ feature. This provides a metric for high level frequencies,
-which is combinied with the low level frequencies from the $L1$ loss.
+PatchGAN discriminator outputs a $32 \times 32 \times 1$ feature matrix, which provides a metric for high level
+frequencies. %which is combinied with the low level frequencies from the $L1$ loss.
 
 In all of our experiments, we use $\lambda_{1} = 100$, $\lambda_{GP} = 10$, batch size of 32, and the Adam Optimizer
-\cite{kingma2014adam} with learning rate $1e-4$. When considering the GDL, we use $\alpha = 1$. Following WGAN-GP, the discriminator is updated $n$ times for every
-update of the generator, where $n = 5$. For UGAN-P, we set $\lambda_{2} = 1.0$. Our implementation was done using the
+\cite{kingma2014adam} with learning rate $1e-4$. Following WGAN-GP, the discriminator is updated $n$ times for every
+update of the generator, where $n = 5$. For UGAN-P, we set $\lambda_{2} = 1.0$ and $\alpha = 1$. Our implementation was done using the
 Tensorflow library \cite{abadi2016tensorflow}.

### 2017-09-15 files/paper/paper.tex
Fixed bib entries that were erroneous, and edited some of the related work section. Also fixed missing image references.

@@
 
-\title{UGAN: Underwater Image Restoration using Generative Adversarial Networks}
+\title{UGAN: Improving Underwater Image Quality using Generative Adversarial Networks}
 \author{Cameron Fabbri$^{1}$, Md Jahidul Islam$^{2}$, and Junaed Sattar$^{3}$
@@
 attractive option because of its non-intrusive, passive, and energy efficient nature. The monitoring of coral reefs \cite{shkurti2012multi},
-deep ocean exploration \cite{whitcomb2000advances}, and mapping of the seabed\starnote{Citation?} are a number of tasks where
+deep ocean exploration \cite{whitcomb2000advances}, and mapping of the seabed~\cite{bingham2010robotic} are a number of tasks where
 visually-guided AUVs and ROVs (Remotely Operated Vehicles) have seen widespread use. Use of these robots ensures humans are not exposed to
@@
 \label{fig:samples}
-\caption{Sample underwater images displaying the diversity of distortion that can occur. Due to the variety of distances
-of objects in the image, there is a varying amount of color loss and distortion.}
+\caption{Sample underwater images with natural and man-made artifacts (which in this case is our underwater robot) displaying the 
+diversity of distortion that can occur. With the varying camera-to-object distances in the images, the distortion and loss of 
+color varies between the different images.}
 \end{figure}
@@
 
-While there have been many very successful recent approaches towards automatic colorization
-\cite{zhang2016colorful,iizuka2016let}, most are focused on the task of grayscale to color.
-The work of \cite{torres2005color} uses an energy minimization formulation using a Markov Random Field. 
-Many employ the use of a physics based model to directly model light refraction \cite{jordt2014underwater}.
-Most similar to our line of work is the recently proposed WaterGAN \cite{li2017watergan}, which uses an adversarial
-approach towards generating realistic underwater images. Their generator model can be broken down into three stages:
-1) Attenuation, which accounts for range-dependent attenuation of light.
-2) Scattering, which models the haze effect caused by photons scattering back towards the image sensor. 3)
-Vingetting, which produces a shading effect on the image corners that can be caused by certain camera lenses.
-Opposed to our work, they use a GAN for generating the underwater images and strictly Euclidean loss for color
-correction, where as we use a GAN for both. Furthermore, they require depth information during the training of WaterGAN,
-whereas we only require two separate image domains throughout.
+While there have been a number of successful recent approaches towards automatic colorization 
+\cite{zhang2016colorful,iizuka2016let}, most are focused on the task of converting grayscale images to color. Quite a few 
+approaches use a physics-based technique to directly model light refraction~\cite{jordt2014underwater}. Specifically for
+restoring color in underwater images, the work of~\cite{torres2005color} uses an energy minimization formulation using a Markov 
+Random Field. Most similar to the work proposed in this paper is the recently proposed WaterGAN~\cite{li2017watergan}, 
+which uses an adversarial approach towards generating realistic underwater images. Their generator model can be broken down into 
+three stages: 1) Attenuation, which accounts for range-dependent attenuation of light. 2) Scattering, which models the haze 
+effect caused by photons scattering back towards the image sensor and 3) Vignetting, which produces a shading effect on the 
+image corners that can be caused by certain camera lenses. Differentiating from our work, they use a GAN for generating the 
+underwater images and use strictly Euclidean loss for color correction, whereas we use a GAN for both. Furthermore, they require 
+depth information during the training of WaterGAN, which can be often difficult to attain particularly for underwater 
+autonomous robotic applications. Our work only requires images of objects in two separate domains (\emph{e.g.}, underwater 
+and terrestrial) throughout the entire process.
 
-Recent work in generative models, specifically GANs, have shown great success
-in areas such as inpainting \cite{pathak2016context}, style transfer \cite{Gatys_2016_CVPR}, and image-to-image
-translation \cite{isola2016image,zhu2017unpaired}. This is highly due to their ability to provide a more meaningful
-loss than simply the Euclidean distance, which has been shown to produce blurry results. In our work, we structure
-the problem as paired image-to-image translation, using Generative Adversarial Networks (GANs) as our generative model.
-Much like the work of \cite{isola2016image}, we use image pairs from two domains an input and ground truth.
-\starnote{Somewhere I think we should mention that unpaired image to image translation is more difficult, and
-that cyclegan is a good way to generate a dataset in such a way to do this with image pairs.}
+Recent work in generative models, specifically GANs, have shown great success in areas such as inpainting 
+\cite{pathak2016context}, style transfer \cite{Gatys_2016_CVPR}, and image-to-image translation 
+\cite{isola2016image,zhu2017unpaired}. This is primarily due to their ability to provide a more meaningful loss than simply the 
+Euclidean distance, which has been shown to produce blurry results. In our work, we structure the problem of estimating 
+the true appearance of underwater imagery as a paired image-to-image translation problem, using Generative Adversarial Networks 
+(GANs) as our generative model\starnote{this needs a little bit more expansion}. Much like the work of \cite{isola2016image}, we 
+use image pairs from two domains as input and ground truth. \starnote{Somewhere I think we should mention that unpaired image to 
+image translation is more difficult, and that cyclegan is a good way to generate a dataset in such a way to do this with image 
+pairs.}
 
@@
 \noindent In our experiments, we denote our network as UGAN-P when considering the GDL, which can be expressed as
-\starnote{I don't like the - in this equation, but don't know how to change it to be shorter}
+\starnote{JS: DONE. I don't like the - in this equation, but don't know how to change it to be shorter}
 
@@
    \begin{aligned}
-      \mathcal{L}_{UGAN-P}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + & \\
+      \mathcal{L}_{UGAN\scalebox{0.4}[1.0]{\( - \)}P}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + & \\
+      % \mathcal{L}_{UGAN-P}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + & \\
       \lambda_{1} \mathcal{L}_{L1}(G) + & \lambda_{2} \mathcal{L}_{GDL}
@@
 \subsection{Datasets}
-We used several subsets of Imagenet \cite{deng2009imagenet} for training and evaluation of our methods. We also
-evaluate a tracking algorithm on a diving video taken from Youtube
-\footnote{https://www.youtube.com/watch?v=QmRFmhILd5o}. Subsets of Imagenet containing underwater images
-were selected for the training of CycleGAN, and manually separated into two classes based on visual inspection. We let
-$X$ be the set of
-underwater images with no distortion, and $Y$ be the set of underwater images with distortion. $X$ contained 6143
-images, and $Y$ contained 1817 images. We then trained CycleGAN to learn the mapping $F: X \rightarrow Y$, such that
-images from $X$ appeared to have come from $Y$. Finally, our image pairs for training data were generated by distorting
-all images in $X$ with $F$. Figure ~\ref{cgan_samples} shows sample training pairs. When comparing with CycleGAN, we used a test set
-of 56 images acquired from Flickr \textsuperscript{TM}.
+We used several subsets of Imagenet~\cite{deng2009imagenet} for training and evaluation of our methods. We also evaluate a tracking
+algorithm on a video of scuba divers taken from Youtube \footnote{https://www.youtube.com/watch?v=QmRFmhILd5o}. Subsets of Imagenet
+containing underwater images were selected for the training of CycleGAN, and manually separated into two classes based on visual
+inspection. We let $X$ be the set of underwater images with no distortion, and $Y$ be the set of underwater images with distortion. $X$
+contained 6143 images, and $Y$ contained 1817 images. We then trained CycleGAN to learn the mapping $F: X \rightarrow Y$, such that images
+from $X$ appeared to have come from $Y$. Finally, our image pairs for training data were generated by distorting all images in $X$ with
+$F$. Figure~\ref{fig:cgan_samples} shows sample training pairs. When comparing with CycleGAN, we used a test set of 56 images 
+acquired from
+Flickr\texttrademark .
 
@@
 Imagenet. Images for training and testing are of size $256 \times 256 \times 3$ and normalized between $[-1, 1]$.
-Figure ~\ref{test_samples} shows samples from the test set. Notably, these images contain varying amounts of noise. Both UGAN and UGAN-P
+Figure ~\ref{fig:test_samples} shows samples from the test set. Notably, these images contain varying amounts of noise. Both UGAN 
+and UGAN-P
 are able to recover lost color information, as well as correct any color information this is present.
@@
 of the image contains distortion. In these cases, we would like the network to only correct parts of the image that
-appear distorted. The last row in Figure ~\ref{test_samples} shows a sample of such an image. The orange of the clownfish is left
+appear distorted. The last row in Figure ~\ref{fig:test_samples} shows a sample of such an image. The orange of the clownfish is 
+left
 unchanged while the distorted sea anemone in the background has its color corrected.
@@
 should not alter the overall structure of the image, we measure the distance in the image space between the edges
-found in the original and generated images. Figure ~\ref{canny_samples} shows the original images and results from
-edge detection. Table 1 provides the measurements from Figure ~\ref{canny_samples}, as well as the average over the
+found in the original and generated images. Figure ~\ref{fig:canny_samples} shows the original images and results from
+edge detection. Table 1 provides the measurements from Figure ~\ref{fig:canny_samples}, as well as the average over the
 entire dataset.
 
-We explore the artifacts of content loss, as seen in Figure ~\ref{zoom}. In particular, we compare local statistics
+We explore the artifacts of content loss, as seen in Figure ~\ref{fig:zoom}. In particular, we compare local statistics
 of the highlighted image patches, where each image patch is resized to $64 \times 64$. We use the GDL

### 2017-09-15 files/paper/_compile.sh

@@ -1,4 +1,5 @@
-rm paper.aux paper.b* paper.log
-pdflatex paper.tex
-bibtex paper.aux
-pdflatex paper.tex
+rm paper.aux paper.b* paper.log paper.pdf
+pdflatex paper
+bibtex paper
+bibtex paper
+pdflatex paper

### 2017-09-15 files/paper/paper.tex
Split the source into separate tex files for easy editing.

--- 2017-09-15 files/paper/paper.tex
@@
 \begin{document}
-
 \maketitle
 
-\begin{abstract}
-Autonomous underwater vehicles (AUVs) rely on a variety of sensors -- acoustic, inertial and visual -- for intelligent decision making. Due
-to its non-intrusive, passive nature, and high information content, vision is an attractive sensing modality, particularly at shallower
-depths. However, factors such as light refraction and absorption, suspended particles in the water, and color distortion affect the quality
-of visual data, resulting in noisy and distorted images. AUVs that rely on visual sensing thus face difficult challenges, and consequently
-exhibit poor performance on vision-driven tasks. This paper proposes a method to improve the quality of visual underwater scenes using
-Generative Adversarial Networks (GANs), with the goal of improving input to vision-driven behaviors further down the autonomy
-pipeline. Furthermore, we show how recently proposed methods are able to generate a dataset for the purpose of such underwater image
-reconstruction\starnote{Reconstruction meaning what we are doing here, right? So this is a contribution too, to show how CycleGAN is used to
-generate the dataset, correct?}. For any visually-guided underwater robots, this improvement can result in increased safety and reliability
-through robust visual perception. To that effect, we present quantitative and qualitative data which demonstrates that images corrected
-through the proposed approach generate more visually appealing images, and also provide increased accuracy for an underwater diver tracking
-algorithm.
-\end{abstract}
-
-%\IEEEpeerreviewmaketitle
-
-\section{Introduction}
-%TODO - talk about having to go back to the same location if you want to get good/bad pairs of the ``same'' image.\starnote{I assume Cam will
-%do this?}
-Underwater robotics has been a steadily growing subfield of autonomous field robotics, assisted by the advent of novel platforms,
-sensors and propulsion mechanisms. While autonomous underwater vehicles are often equipped with a variety of sensors, visual sensing is an
-attractive option because of its non-intrusive, passive, and energy efficient nature. The monitoring of coral reefs \cite{shkurti2012multi},
-deep ocean exploration \cite{whitcomb2000advances}, and mapping of the seabed\starnote{Citation?} are a number of tasks where
-visually-guided AUVs and ROVs (Remotely Operated Vehicles) have seen widespread use. Use of these robots ensures humans are not exposed to
-the hazards of underwater exploration, as they no longer need to venture to the depths (which was how such tasks were carried out in the
-past). Despite the advantages of using vision, underwater environments pose unique challenges to visual sensing, as phenomena such as light
-refraction, absorption and scattering from suspended particles can greatly affect the optics of light. As an example, because red
-wavelengths are quickly absorbed by water, images tend to have a green or blue hue to them. As one goes deeper, this effect worsens, as more
-and more red hue is absorbed. This distortion is extremely non-linear in nature, and is affected by a large number of factors, such as the
-amount of light present (overcast versus sunny, operational depth), amount of particles in the water, time of day, and the camera being
-used. This may cause difficulty in tasks such as segmentation, tracking, or classification due to their indirect or direct use of color.
-
-As color and illumination begin to change with the depth, vision-based algorithms must need to be very generalizable in order to work within
-the depth ranges a robot may operate in. Because of the high cost and difficulty of acquiring a variety of underwater data to train a visual
-system on, as well as the high amount of noise introduced, algorithms may (and do) perform poorly in these different
-domains. Figure~\ref{fig:samples} shows the high variability in visual scenes that may occur in
-underwater environments. A step towards a solution to this issue is to be able to restore the images such that they appear to be above
-water, \emph{i.e.}, with colors corrected and suspended particles removed from the scene. By performing a many-to-one mapping of these
-domains from underwater to not underwater (what the image would look like above water), algorithms that have difficulty performing across
-multiple forms of noise may be able to focus only one clean domain.
-
-\begin{figure}
-\centering
-\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.7cm}}
-
-   \includegraphics[width=0.8in]{n01496331_7428_f1} &
-   \includegraphics[width=0.8in]{n01496331_16340_f1} &
-   \includegraphics[width=0.8in]{n01914609_5148_f1} &
-   \includegraphics[width=0.8in]{robot_f1} \\
-   \includegraphics[width=0.8in]{n01664065_30279_f1} &
-   \includegraphics[width=0.8in]{n01917289_5711_f1} &
-   \includegraphics[width=0.8in]{n01917289_4087_f1} &
-   \includegraphics[width=0.8in]{n02607072_10395_f1} \\
-
-\end{tabular}
-\label{fig:samples}
-\caption{Sample underwater images displaying the diversity of distortion that can occur. Due to the variety of distances
-of objects in the image, there is a varying amount of color loss and distortion.}
-\end{figure}
-
-Deep neural networks have been shown to be powerful non-linear function approximators, especially in the field of vision \cite{krizhevsky2012imagenet}.
-Often times, these networks require large amounts of data, either labeled or paired with
-ground truth. For the problem of automatically colorizing grayscale images \cite{zhang2016colorful}, paired training
-data is
-readily available due to the fact that any color image can be converted to black and white. However, underwater images distorted by either
-color or some other phenomenon lack ground truth, which is a major hindrance towards adopting a similar approach for correction.
-This paper proposes a technique based on Generative Adversarial Networks (GANs) to improve the quality of visual underwater scenes with the goal of improving the performance of vision-driven behaviors for autonomous underwater robots
-%\starnote{Summarize the approach here. Then talk about datasets as you have done already.}
-We use the recently proposed CycleGAN~\cite{zhu2017unpaired} approach, which learns to translate an image from any arbitrary domain $X$ to another arbitrary domain $Y$ \textit{without} image pairs, as a way to generate a paired dataset.
-By letting $X$ be a set of undistorted underwater images\starnote{need to say where we find the undistorted ones}, and
-$Y$ be a set of distorted underwater images, we can generate an image that appears to be underwater while retaining
-ground truth.
-
-\section{Related Work}
-
-While there have been many very successful recent approaches towards automatic colorization
-\cite{zhang2016colorful,iizuka2016let}, most are focused on the task of grayscale to color.
-The work of \cite{torres2005color} uses an energy minimization formulation using a Markov Random Field. 
-Many employ the use of a physics based model to directly model light refraction \cite{jordt2014underwater}.
-Most similar to our line of work is the recently proposed WaterGAN \cite{li2017watergan}, which uses an adversarial
-approach towards generating realistic underwater images. Their generator model can be broken down into three stages:
-1) Attenuation, which accounts for range-dependent attenuation of light.
-2) Scattering, which models the haze effect caused by photons scattering back towards the image sensor. 3)
-Vingetting, which produces a shading effect on the image corners that can be caused by certain camera lenses.
-Opposed to our work, they use a GAN for generating the underwater images and strictly Euclidean loss for color
-correction, where as we use a GAN for both. Furthermore, they require depth information during the training of WaterGAN,
-whereas we only require two separate image domains throughout.
-
-Recent work in generative models, specifically GANs, have shown great success
-in areas such as inpainting \cite{pathak2016context}, style transfer \cite{Gatys_2016_CVPR}, and image-to-image
-translation \cite{isola2016image,zhu2017unpaired}. This is highly due to their ability to provide a more meaningful
-loss than simply the Euclidean distance, which has been shown to produce blurry results. In our work, we structure
-the problem as paired image-to-image translation, using Generative Adversarial Networks (GANs) as our generative model.
-Much like the work of \cite{isola2016image}, we use image pairs from two domains an input and ground truth.
-\starnote{Somewhere I think we should mention that unpaired image to image translation is more difficult, and
-that cyclegan is a good way to generate a dataset in such a way to do this with image pairs.}
-
-\section{Method}
-
-\subsection{Dataset Generation}
-Here we describe our dataset generation process. Depth, lighting conditions, camera
-model, and location are all factors that affect the amount of distortion an underwater image undergoes. Under certain
-conditions, it is possible that an underwater image may have very little distortion, or none at all.
-We let $I^C$ be an underwater image with no distortion, and $I^D$
-be the same image with distortion. Our goal is to learn the function $f: I^D \rightarrow I^C$. Becasue of the
-difficulty of collecting underwater data, more often than not only $I^D$ or $I^C$ exist, but never both.
-
-We use the recently proposed CycleGAN \cite{zhu2017unpaired} to generate $I^D$ from $I^C$, which gives us a paired
-dataset of images. Given two datasets $X$ and $Y$, where $I^C \in X$ and $I^D \in Y$, CycleGAN learns a mapping
-$F: X \rightarrow Y$. Figure ~\ref{fig:cgan_samples} shows paired samples generated from CycleGAN. From this paired dataset we train a
-generator $G$ to learn the function $f: I^D \rightarrow I^C$. It should be noted that during our data generation process,
-CycleGAN simultaneously learns a mapping $G: Y \rightarrow X$, which is similar to $f$. In section IV we show a comparison with our method.
-
-\subsection{Adversarial Networks}
-GANs \cite{goodfellow2014generative} are a class of generative models based on game theory in which a generator
-network competes against an adversary. Conditioned on an image $I^D$, the generator is trained to produce an \
-image to try and fool the discriminator, which is trained to distinguish be between distorted and non-distorted
-underwater images. In the original GAN formulation, our goal is to solve the minimax problem:
-
-\begin{figure}
-\centering
-\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.7cm}}
-
-   \includegraphics[width=0.8in]{n01496331_873_X} &
-   \includegraphics[width=0.8in]{n01664065_4022_X} &
-   \includegraphics[width=0.8in]{n01917289_889_X} &
-   \includegraphics[width=0.8in]{n01914609_116_X} \\
-   \includegraphics[width=0.8in]{n01496331_873_Y} &
-   \includegraphics[width=0.8in]{n01664065_4022_Y} &
-   \includegraphics[width=0.8in]{n01917289_889_Y} &
-   \includegraphics[width=0.8in]{n01914609_116_Y} \\
-
-\end{tabular}
-\label{fig:cgan_samples}
-\caption{Paired samples of ground truth and distorted images generated by CycleGAN. Top row: Ground truth.
-Bottom row: Generated samples.}
-\end{figure}
-
-\begin{equation}
-\begin{aligned}
-   \min\limits_{G}\max\limits_{D} \mathbb{E} & _{I^C \sim p_{train}(I^C)} [logD(I^C)] + \\
-   \mathbb{E} & _{I^D \sim p_{gen}(I^D)}[log(1 - D(G(I^D)))]
-\end{aligned}
-\end{equation}
-
-\noindent Note for simplicity in notation, we will further omit $I^C \sim p_{train}$ and $I^D \sim p_{gen}$. In this
-formulation, the discriminator is hypothesized as a classifier with a sigmoid cross entropy loss function, which in
-practice may lead to issues such as the vanish gradient and mode collapse. There have been many recent works which
-hypothesize a different loss function for the discriminator
-\cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}. We focus on the Wasserstein GAN
-(WGAN) \cite{arjovsky2017wasserstein} formulation, which proposes to use the Earth-Mover or \textit{Wasserstein-1}
-distance $W$ by constructing a value function using the Kantorovich-Rubinstein duality \cite{villani2008optimal}.
-In this formulation, $W$ is approximated given a set of $k$-Lipschitz functions $f$ modeled as neural networks. To
-ensure $f$ is $k$-Lipschitz, the weights of the discriminator are clipped to some range $[-c, c]$. In our work, we
-adopt the Wasserstein GAN with gradient penalty (WGAN-GP) \cite{gulrajani2017improved}, which instead of clipping
-network weights like in \cite{arjovsky2017wasserstein}, ensures the Lipschitz constraint by enforcing a soft
-constraint on the gradient norm of the discriminator's output with respect to its input. Following
-\cite{gulrajani2017improved}, our new objective then becomes
-
-\begin{equation}
-\begin{aligned}
-   \mathcal{L}_{WGAN}(G,D) = \mathbb{E} [D(I^C)] - \mathbb{E} & [D(G(I^D))] + \\
-   \lambda_{GP} \mathbb{E} & _{\hat{x} \sim \mathbb{P}_{\hat{x}}} [(|| \nabla_{\hat{x}} D(\hat{x})||_2 -1)^2 ],
-\end{aligned}
-\end{equation}
-
-%\begin{equation}
-%\begin{aligned}
-%   \mathcal{L}_{GAN} = \mathbb{E}_{I^D \sim p_{gen}(I^D)} [D(I^D)] - \mathbb{E} & _{I^C \sim p_{train}(I^C)} [D(I^C)] + \\
-%   \lambda \mathbb{E} & _{\hat{x} \sim \mathbb{P}_{\hat{x}}} [(|| \nabla_{\hat{x}} D(\hat{x})||_2 -1)^2 ].
-%\end{aligned}
-%\end{equation}
-
-\noindent where $\mathbb{P}_{\hat{x}}$ is defined as samples along straight lines between pairs of points coming from
-the true data distribution and the generator distribution, and $\lambda_{GP}$ is a weighing factor. In order to give $G$
-some sense of ground truth, as well as capture low level frequencies in the image, we also consider the $L1$ loss
-
-\begin{equation}
-   \mathcal{L}_{L1} = \mathbb{E} [ || I^C - G(I^D) ||_1 ].
-\end{equation}
-%\begin{equation}
-%   \mathcal{L}_{L1} = \mathbb{E}_{I^D \sim p_{gen}, I^C \sim p_{train}} [ || I^C - G(I^D) ||_1 ].
-%\end{equation}
-
-\noindent Combining these, we get our final objective function for our network, which we call Underwater GAN (UGAN),
-
-\begin{equation}
-   \begin{aligned}
-      \mathcal{L}_{UGAN}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + \lambda_{1} \mathcal{L}_{L1}(G).
-   \end{aligned}
-\end{equation}
-
-\subsection{Image Gradient Difference Loss}
-Often times generative models produce blurry images. We explore a strategy to sharpen these predictions by
-directly penalizing the differences of image gradient predictions in the generator, as proposed by
-\cite{mathieu2015deep}. Given a ground truth image $I^C$, predicted image $I^P = G(I^D)$, and $\alpha \geq 1$, the
-Gradient Difference Loss (GDL) is given by
-
-\begin{equation}
-   \begin{aligned}
-      \mathcal{L}_{GDL}(I^C, I^P) = \\ \sum\limits_{i,j} || & I^C_{i,j} - I^C_{i-1,j}| - | I^P_{i,j} - I^P_{i-1,j}||^{\alpha} + \\
-      || & I^C_{i,j-1} - I^C_{i,j}| - | I^P_{i,j-1} - I^P_{i,j}||^{\alpha}.
-   \end{aligned}
-   \label{gdl_eq}
-\end{equation}
-
-\noindent In our experiments, we denote our network as UGAN-P when considering the GDL, which can be expressed as
-\starnote{I don't like the - in this equation, but don't know how to change it to be shorter}
-
-\begin{equation}
-   \begin{aligned}
-      \mathcal{L}_{UGAN-P}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + & \\
-      \lambda_{1} \mathcal{L}_{L1}(G) + & \lambda_{2} \mathcal{L}_{GDL}
-   \end{aligned}
-\end{equation}
-
-\subsection{Network Architecture and Training Details}
-Our generator network is a fully convolutional encoder-decoder, similar to the work of \cite{isola2016image}, which is
-designed as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.
-Encoder-decoder networks downsample (encode) the input via convolutions to a lower dimensional embedding, in which
-this embedding is then upsampled (decode) via transpose convolutions to reconstruct an image. The advantage of using
-a ``U-Net'' comes from explicitly preserving spatial dependencies produced by the encoder, as opposed to relying on the
-embedding to contain all of the information. This is done by the addition of ``skip connections'', which concatenate
-the activations produced from a convolution layer $i$ in the encoder to the input of a transpose convolution layer
-$n-i+1$ in the decoder, where $n$ is the total number of layers in the network. Each convolutional layer in our
-generator uses kernel size $4 \times 4$ with stride 2. Convolutions in the encoder portion of the network are followed
-by batch normalization \cite{pmlr-v37-ioffe15} and a leaky ReLU activation with slope $0.2$, while transpose
-convolutions in the decoder are followed by a ReLU activation \cite{nair2010rectified} (no batch norm in the decoder).
-Exempt from this is the last layer of the decoder, which uses a TanH nonlinearity to match the input distribution of
-$[-1, 1]$. Recent work has proposed Instance Normalization \cite{ulyanov2016instance} to improve quality
-in image-to-image translation tasks, however we observed no added benefit.
-
-Our fully convolutional discriminator is modeled after that of \cite{radford2015unsupervised}, except no batch
-normalization is used. This is due to the fact that WGAN-GP penalizes the norm of the discriminator's gradient with
-respect to each input individually, which batch normalization would invalidate. The authors of
-\cite{gulrajani2017improved} recommend layer normalization \cite{ba2016layer}, but we found no significant improvements.
-Our discriminator is modeled as a PatchGAN \cite{isola2016image,li2016precomputed}, which discriminates at the level of
-image patches. As opposed to a regular discriminator, which outputs a scalar value corresponding to real or fake, our
-PatchGAN discriminator outputs a $32 \times 32 \times 1$ feature matrix, which provides a metric for high level
-frequencies. %which is combinied with the low level frequencies from the $L1$ loss.
-
-In all of our experiments, we use $\lambda_{1} = 100$, $\lambda_{GP} = 10$, batch size of 32, and the Adam Optimizer
-\cite{kingma2014adam} with learning rate $1e-4$. Following WGAN-GP, the discriminator is updated $n$ times for every
-update of the generator, where $n = 5$. For UGAN-P, we set $\lambda_{2} = 1.0$ and $\alpha = 1$. Our implementation was done using the
-Tensorflow library \cite{abadi2016tensorflow}.
-\footnote{Code is available at \url{https://github.com/cameronfabbri/Underwater-Color-Correction}}
-All networks were trained from scratch on a GTX 1080 for 100 epochs. Inference on the GPU takes on average $ 0.0138s$,
-which is about 72 Frames Per Second (FPS). On a CPU (Intel Core i7-5930K), inference takes on average $ 0.1244s$, which
-is about 8 FPS. We find both of these measures acceptable for underwater tasks.
-
-\section{Experiments}
-\subsection{Datasets}
-We used several subsets of Imagenet \cite{deng2009imagenet} for training and evaluation of our methods. We also
-evaluate a tracking algorithm on a diving video taken from Youtube
-\footnote{https://www.youtube.com/watch?v=QmRFmhILd5o}. Subsets of Imagenet containing underwater images
-were selected for the training of CycleGAN, and manually separated into two classes based on visual inspection. We let
-$X$ be the set of
-underwater images with no distortion, and $Y$ be the set of underwater images with distortion. $X$ contained 6143
-images, and $Y$ contained 1817 images. We then trained CycleGAN to learn the mapping $F: X \rightarrow Y$, such that
-images from $X$ appeared to have come from $Y$. Finally, our image pairs for training data were generated by distorting
-all images in $X$ with $F$. Figure ~\ref{cgan_samples} shows sample training pairs. When comparing with CycleGAN, we used a test set
-of 56 images acquired from Flickr \textsuperscript{TM}.
-
-\subsection{Evaluation}
-We train UGAN and UGAN-P on the image pairs generated by CycleGAN, and evaluate on the images from the
-test set, $Y$. Note that these images do not contain any ground truth, as they are original distorted images from
-Imagenet. Images for training and testing are of size $256 \times 256 \times 3$ and normalized between $[-1, 1]$.
-Figure ~\ref{test_samples} shows samples from the test set. Notably, these images contain varying amounts of noise. Both UGAN and UGAN-P
-are able to recover lost color information, as well as correct any color information this is present.
-
-While many of the distorted images contain a blue or green hue over the entire image space, that is not always the case.
-In certain environments,
-it is possible that objects close to the camera are undistorted with correct colors, while the background
-of the image contains distortion. In these cases, we would like the network to only correct parts of the image that
-appear distorted. The last row in Figure ~\ref{test_samples} shows a sample of such an image. The orange of the clownfish is left
-unchanged while the distorted sea anemone in the background has its color corrected.
-
-We use three metrics for a quantitative evaluation. First, we compare to CycleGAN, as it inherently learns an inverse
-mapping during the training of $F: X \rightarrow Y$, using the Canny edge detector
-\cite{canny1986computational}. This provides a color agnostic evaluation of the images in comparison to ground truth.
-Second, we compare local image patches to provide sharpness metrics on our images. Lastly, we show how an existing
-tracking algorithm for an underwater robot improves performance with generated images.
-
-\begin{figure}
-\centering
-\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm}}
-
-   ~\quad Original & ~\quad UGAN & \quad UGAN-P \\
-
-   \includegraphics[width=0.8in]{n01917289_4982_real} &
-   \includegraphics[width=0.8in]{n01917289_4982_gen_0} &
-   \includegraphics[width=0.8in]{n01917289_4982_gen_1} \\
-
-   \includegraphics[width=0.8in]{n01496331_16340_real} &
-   \includegraphics[width=0.8in]{n01496331_16340_gen_0} &
-   \includegraphics[width=0.8in]{n01496331_16340_gen_1} \\
-
-   \includegraphics[width=0.8in]{n01496331_22183_real} &
-   \includegraphics[width=0.8in]{n01496331_22183_gen_0} &
-   \includegraphics[width=0.8in]{n01496331_22183_gen_1} \\
-
-   \includegraphics[width=0.8in]{n01664065_29738_real} &
-   \includegraphics[width=0.8in]{n01664065_29738_gen_0} &
-   \includegraphics[width=0.8in]{n01664065_29738_gen_1} \\
-
-   \includegraphics[width=0.8in]{n01496331_11938_real} &
-   \includegraphics[width=0.8in]{n01496331_11938_gen_0} &
-   \includegraphics[width=0.8in]{n01496331_11938_gen_1} \\
-
-   \includegraphics[width=0.8in]{n02606052_2969_real} &
-   \includegraphics[width=0.8in]{n02606052_2969_gen_0} &
-   \includegraphics[width=0.8in]{n02606052_2969_gen_1} \\
-
-   \includegraphics[width=0.8in]{n01914609_1607_real} &
-   \includegraphics[width=0.8in]{n01914609_1607_gen_0} &
-   \includegraphics[width=0.8in]{n01914609_1607_gen_1} \\
-
-   \includegraphics[width=0.8in]{n02607072_6241_real} &
-   \includegraphics[width=0.8in]{n02607072_6241_gen_0} &
-   \includegraphics[width=0.8in]{n02607072_6241_gen_1} \\
-
-\end{tabular}
-\caption{Samples from our Imagenet testing set. The network can both recover color and also correct color if a small amount is present.}
-\label{fig:test_samples}
-\end{figure}
-
-% Directly from the first paper on the inception score: We find that it’s important to evaluate the metric on a large
-% enough number of samples (i.e. 50k) as part of this metric measures diversity.
-% % Therefore we should not include it I think
-% \footnote{Code for inception score can be found at https://github.com/openai/improved-gan}
-%\begin{center}
-%\begin{tabular}{c c c c c c}
-%Samples & real & ugan & ugan-p & cyclegan \\ \hline
-%Model & True Images & UGAN & UGAN-P & CycleGAN \\ \hline
-%Score $\pm$ std. & $5.69 \pm 0.23$ & $6.18 \pm 0.35$ & $6.30 \pm 0.32$ & $6.37 \pm 0.43$ \\ \hline
-%\end{tabular}
-%\end{center}
-
-\subsection{Comparison to CycleGAN}
-It is important to note that during the process of learning a mapping $F: X \rightarrow Y$, CycleGAN also learns a
-mapping $G: Y \rightarrow X$. Here we show that UGAN and UGAN-P provide superior performance. We use the Canny edge
-detector \cite{canny1986computational} to provide a color agnostic evaluation of the images, as the original contain
-distorted colors and cannot be compared back to as ground truth. Due to the fact that restoring color information
-should not alter the overall structure of the image, we measure the distance in the image space between the edges
-found in the original and generated images. Figure ~\ref{canny_samples} shows the original images and results from
-edge detection. Table 1 provides the measurements from Figure ~\ref{canny_samples}, as well as the average over the
-entire dataset.
-
-We explore the artifacts of content loss, as seen in Figure ~\ref{zoom}. In particular, we compare local statistics
-of the highlighted image patches, where each image patch is resized to $64 \times 64$. We use the GDL
-\cite{mathieu2015deep} from (\ref{gdl_eq}) as a sharpness measure.
-
-% I would like this table to match up with the figure showing edge detections. I wasn't able to
-% get letters on the left side at each row though.
-\begin{table}
-\centering
-\caption{Distances in image space}
-\begin{tabular}{| c | c | c | c |}
-   \hline
-   Row/Method & CycleGAN & UGAN & UGAN-P \\ \hline
-   A          & 116.45 & 85.71  & 86.15  \\ \hline
-   B          & 114.49 & 97.92  & 101.01 \\ \hline
-   C          & 120.84 & 96.53  & 97.57  \\ \hline
-   D          & 129.27 & 108.90 & 110.50 \\ \hline
-   Mean       & 111.60 & 94.91  & 96.51 \\ \hline
-\end{tabular}
-\end{table}
-
-\newpage
-
-\begin{figure}
-\centering
-\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.7cm}}
-
-   ~\quad Original & ~CycleGAN & ~\quad UGAN & \quad UGAN-P \\
-
-   \includegraphics[width=0.8in]{1_original} &
-   \includegraphics[width=0.8in]{1_cimg} &
-   \includegraphics[width=0.8in]{1_u0img} &
-   \includegraphics[width=0.8in]{1_u1img} \\ [-1ex]
-   \includegraphics[width=0.8in]{1_oedges} &
-   \includegraphics[width=0.8in]{1_cedges} &
-   \includegraphics[width=0.8in]{1_u0edges} &
-   \includegraphics[width=0.8in]{1_u1edges} \\
-
-   \includegraphics[width=0.8in]{2_original} &
-   \includegraphics[width=0.8in]{2_cimg} &
-   \includegraphics[width=0.8in]{2_u0img} &
-   \includegraphics[width=0.8in]{2_u1img} \\ [-1ex]
-   \includegraphics[width=0.8in]{2_oedges} &
-   \includegraphics[width=0.8in]{2_cedges} &
-   \includegraphics[width=0.8in]{2_u0edges} &
-   \includegraphics[width=0.8in]{2_u1edges} \\
-
-   \includegraphics[width=0.8in]{3_original} &
-   \includegraphics[width=0.8in]{3_cimg} &
-   \includegraphics[width=0.8in]{3_u0img} &
-   \includegraphics[width=0.8in]{3_u1img} \\ [-1ex]
-   \includegraphics[width=0.8in]{3_oedges} &
-   \includegraphics[width=0.8in]{3_cedges} &
-   \includegraphics[width=0.8in]{3_u0edges} &
-   \includegraphics[width=0.8in]{3_u1edges} \\
-
-   \includegraphics[width=0.8in]{4_original} &
-   \includegraphics[width=0.8in]{4_cimg} &
-   \includegraphics[width=0.8in]{4_u0img} &
-   \includegraphics[width=0.8in]{4_u1img} \\ [-1ex]
-   \includegraphics[width=0.8in]{4_oedges} &
-   \includegraphics[width=0.8in]{4_cedges} &
-   \includegraphics[width=0.8in]{4_u0edges} &
-   \includegraphics[width=0.8in]{4_u1edges} \\
-
-\end{tabular}
-\caption{Running the Canny Edge Detector on sample images. Both variants of UGAN contain less noise than CycleGAN,
-and are closer in the image space to the original. For each pair, the top row is the input image, and bottom row
-the result of the edge detector.}
-\label{fig:canny_samples}
-\end{figure}
-
-% TODO definitely need help with formatting, but content is there
-\begin{figure*}
-\centering
-\begin{tabular}{p{4.0cm} p{4.0cm} p{4.0cm} p{4.0cm}}
-
-   \qquad \qquad ~ Original & \qquad \qquad CycleGAN & \qquad \qquad ~ \textbf{UGAN} & \qquad \qquad \textbf{UGAN-P} \\
-
-   \includegraphics[width=1.7in]{flickr_cmp} &
-   \includegraphics[width=1.7in]{cgan_cmp} &
-   \includegraphics[width=1.7in]{ugan_cmp} &
-   \includegraphics[width=1.7in]{uganp_cmp} \\ [-11ex]
-
-\end{tabular}
-\end{figure*}
-
-\begin{figure*}
-\begin{tabular}{p{1.8cm} p{1.85cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.9cm} }
-
-   \includegraphics[width=0.8in]{flickr_crop1} &
-   \includegraphics[width=0.8in]{flickr_crop2} &
-   \includegraphics[width=0.8in]{cgan_crop1} &
-   \includegraphics[width=0.8in]{cgan_crop2} &
-   \includegraphics[width=0.8in]{ugan_crop1} &
-   \includegraphics[width=0.8in]{ugan_crop2} &
-   \includegraphics[width=0.8in]{ugan_crop1} &
-   \includegraphics[width=0.8in]{ugan_crop2} \\
-
-   \includegraphics[width=0.8in]{flickr_crop3} &
-   \includegraphics[width=0.8in]{flickr_crop4} &
-   \includegraphics[width=0.8in]{cgan_crop3} &
-   \includegraphics[width=0.8in]{cgan_crop4} &
-   \includegraphics[width=0.8in]{ugan_crop3} &
-   \includegraphics[width=0.8in]{ugan_crop4} &
-   \includegraphics[width=0.8in]{ugan_crop3} &
-   \includegraphics[width=0.8in]{ugan_crop4} \\
-
-\end{tabular}
-\caption{Comparison of local image patches. Each patch was resized to $64 \times 64$.}
-\label{fig:zoom}
-\end{figure*}
-
-\subsection{Diver Tracking using Frequency-Domain Detection}
-We investigate the frequency-domain characteristics of the restored images through a case-study of periodic motion tracking in sequence of images.
-Particularly, we compared the performance of Mixed Domain Periodic Motion (MDPM)- tracker \cite{islam2017mixed} on a sequence of images of a diver swimming in  arbitrary directions.
-MDPM tracker is designed for underwater robots to follow scuba divers by   tracking distinct frequency-domain signatures (high-amplitude spectra at $1$-$2$Hz) pertaining to human swimming.
-Amplitude spectra in frequency-domain correspond to the periodic intensity variations in image-space over time, which is often eroded in noisy underwater images \cite{shkurti2017underwater}.
-
-Fig.
-\ref{mdpmStuff} illustrates the improved performance of MDPM tracker on generated images compared to the real ones.
-Underwater images often fail to capture the true contrast in intensity values between foreground and background due to low visibility.
-The generated images seem to restore these eroded intensity variations to some extent, causing much improved positive detection for MDPM tracker.
-
-\begin{figure*}
-\centering
-\begin{tabular}{p{4.0cm} p{4.0cm} p{4.0cm} p{4.0cm}}
-   \includegraphics[width=1.7in]{mdpm/real1} &
-   \includegraphics[width=1.7in]{mdpm/real2} &
-   \includegraphics[width=1.7in]{mdpm/real3} &
-   \includegraphics[width=1.7in]{mdpm/real4} \\
-   \includegraphics[width=1.7in]{mdpm/gen1} &
-   \includegraphics[width=1.7in]{mdpm/gen2} &
-   \includegraphics[width=1.7in]{mdpm/gen3} &
-   \includegraphics[width=1.7in]{mdpm/gen4} \\
-\end{tabular}
-\label{fig:mdpm}
-\vspace{4mm}
-
-\begin{tabular}{l|c|c|c|r|}
- \cline{2-5}
- &  Correct detection & Wrong detection & Missed detection & Total \# of frames\\ \hline  \cline{2-4}
-On real images  &  42 & 14 & 444 & 500  \\ \hline
-On generated images  &  147 & 24 & 329 & 500  \\ \hline
-\end{tabular}
-
-\caption{Performance of MDPM tracker \cite{islam2017mixed} on both real (top row) and generated (second row) images; the Table compares the detection performance for both sets of images over a sequence of $500$ frames.
-}
-\label{mdpmStuff}
-\end{figure*}
-
-%Flippers of a human diver typically oscillate at frequencies between $1$ and $2$ Hz, which produces periodic intensity variations in the image-space over time.
-These variations correspond to distinct signatures in the frequency-domain (high-amplitude spectra at $1$-$2$Hz), which can be used for reliable detection.
-
-\section{Conclusion}
-
-Future work: Getting a better and larger dataset. I think that would help a great deal. Also data augmentation
-after CycleGAN, such as gaussian blurring, noise, particle effect, more lighting effects etc.
-
-\section*{Acknowledgment}
+\input{tex/abstract}
+\input{tex/introduction}
+\input{tex/related}
+\input{tex/methodology.tex}
+\input{tex/experiments}
+\input{tex/conclusions}
 

### 2017-09-15 files/paper/tex/abstract.tex
Split the source into separate tex files for easy editing.

\begin{abstract}
Autonomous underwater vehicles (AUVs) rely on a variety of sensors -- acoustic, inertial and visual -- for intelligent decision 
making. Due
to its non-intrusive, passive nature, and high information content, vision is an attractive sensing modality, particularly at 
shallower
depths. However, factors such as light refraction and absorption, suspended particles in the water, and color distortion affect 
the quality
of visual data, resulting in noisy and distorted images. AUVs that rely on visual sensing thus face difficult challenges, and 
consequently
exhibit poor performance on vision-driven tasks. This paper proposes a method to improve the quality of visual underwater scenes 
using
Generative Adversarial Networks (GANs), with the goal of improving input to vision-driven behaviors further down the autonomy
pipeline. Furthermore, we show how recently proposed methods are able to generate a dataset for the purpose of such underwater 
image
reconstruction\starnote{Reconstruction meaning what we are doing here, right? So this is a contribution too, to show how CycleGAN 
is used to
generate the dataset, correct?}. For any visually-guided underwater robots, this improvement can result in increased safety and 
reliability
through robust visual perception. To that effect, we present quantitative and qualitative data which demonstrates that images 
corrected
through the proposed approach generate more visually appealing images, and also provide increased accuracy for an underwater diver 
tracking
algorithm.
\end{abstract}

### 2017-09-15 files/paper/tex/conclusions.tex
Split the source into separate tex files for easy editing.

\section{Conclusion}

Future work: Getting a better and larger dataset. I think that would help a great deal. Also data augmentation
after CycleGAN, such as gaussian blurring, noise, particle effect, more lighting effects etc.

\section*{Acknowledgment}
Anyone we wish to acknowledge?

### 2017-09-15 files/paper/tex/experiments.tex
Split the source into separate tex files for easy editing.

\section{Experiments}
\subsection{Datasets}
We used several subsets of Imagenet~\cite{deng2009imagenet} for training and evaluation of our methods. We also evaluate a 
tracking
algorithm on a video of scuba divers taken from Youtube \footnote{https://www.youtube.com/watch?v=QmRFmhILd5o}. Subsets of 
Imagenet
containing underwater images were selected for the training of CycleGAN, and manually separated into two classes based on visual
inspection. We let $X$ be the set of underwater images with no distortion, and $Y$ be the set of underwater images with 
distortion. $X$
contained 6143 images, and $Y$ contained 1817 images. We then trained CycleGAN to learn the mapping $F: X \rightarrow Y$, such 
that images
from $X$ appeared to have come from $Y$. Finally, our image pairs for training data were generated by distorting all images in $X$ 
with
$F$. Figure~\ref{fig:cgan_samples} shows sample training pairs. When comparing with CycleGAN, we used a test set of 56 images 
acquired from
Flickr\texttrademark .

\subsection{Evaluation}
We train UGAN and UGAN-P on the image pairs generated by CycleGAN, and evaluate on the images from the
test set, $Y$. Note that these images do not contain any ground truth, as they are original distorted images from
Imagenet. Images for training and testing are of size $256 \times 256 \times 3$ and normalized between $[-1, 1]$.
Figure ~\ref{fig:test_samples} shows samples from the test set. Notably, these images contain varying amounts of noise. Both UGAN 
and UGAN-P
are able to recover lost color information, as well as correct any color information this is present.

While many of the distorted images contain a blue or green hue over the entire image space, that is not always the case.
In certain environments,
it is possible that objects close to the camera are undistorted with correct colors, while the background
of the image contains distortion. In these cases, we would like the network to only correct parts of the image that
appear distorted. The last row in Figure ~\ref{fig:test_samples} shows a sample of such an image. The orange of the clownfish is 
left
unchanged while the distorted sea anemone in the background has its color corrected.

We use three metrics for a quantitative evaluation. First, we compare to CycleGAN, as it inherently learns an inverse
mapping during the training of $F: X \rightarrow Y$, using the Canny edge detector
\cite{canny1986computational}. This provides a color agnostic evaluation of the images in comparison to ground truth.
Second, we compare local image patches to provide sharpness metrics on our images. Lastly, we show how an existing
tracking algorithm for an underwater robot improves performance with generated images.

\begin{figure}
\centering
\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm}}

   ~\quad Original & ~\quad UGAN & \quad UGAN-P \\

   \includegraphics[width=0.8in]{n01917289_4982_real} &
   \includegraphics[width=0.8in]{n01917289_4982_gen_0} &
   \includegraphics[width=0.8in]{n01917289_4982_gen_1} \\

   \includegraphics[width=0.8in]{n01496331_16340_real} &
   \includegraphics[width=0.8in]{n01496331_16340_gen_0} &
   \includegraphics[width=0.8in]{n01496331_16340_gen_1} \\

   \includegraphics[width=0.8in]{n01496331_22183_real} &
   \includegraphics[width=0.8in]{n01496331_22183_gen_0} &
   \includegraphics[width=0.8in]{n01496331_22183_gen_1} \\

   \includegraphics[width=0.8in]{n01664065_29738_real} &
   \includegraphics[width=0.8in]{n01664065_29738_gen_0} &
   \includegraphics[width=0.8in]{n01664065_29738_gen_1} \\

   \includegraphics[width=0.8in]{n01496331_11938_real} &
   \includegraphics[width=0.8in]{n01496331_11938_gen_0} &
   \includegraphics[width=0.8in]{n01496331_11938_gen_1} \\

   \includegraphics[width=0.8in]{n02606052_2969_real} &
   \includegraphics[width=0.8in]{n02606052_2969_gen_0} &
   \includegraphics[width=0.8in]{n02606052_2969_gen_1} \\

   \includegraphics[width=0.8in]{n01914609_1607_real} &
   \includegraphics[width=0.8in]{n01914609_1607_gen_0} &
   \includegraphics[width=0.8in]{n01914609_1607_gen_1} \\

   \includegraphics[width=0.8in]{n02607072_6241_real} &
   \includegraphics[width=0.8in]{n02607072_6241_gen_0} &
   \includegraphics[width=0.8in]{n02607072_6241_gen_1} \\

\end{tabular}
\caption{Samples from our Imagenet testing set. The network can both recover color and also correct color if a small amount is 
present.}
\label{fig:test_samples}
\end{figure}

% Directly from the first paper on the inception score: We find that it’s important to evaluate the metric on a large
% enough number of samples (i.e. 50k) as part of this metric measures diversity.
% % Therefore we should not include it I think
% \footnote{Code for inception score can be found at https://github.com/openai/improved-gan}
%\begin{center}
%\begin{tabular}{c c c c c c}
%Samples & real & ugan & ugan-p & cyclegan \\ \hline
%Model & True Images & UGAN & UGAN-P & CycleGAN \\ \hline
%Score $\pm$ std. & $5.69 \pm 0.23$ & $6.18 \pm 0.35$ & $6.30 \pm 0.32$ & $6.37 \pm 0.43$ \\ \hline
%\end{tabular}
%\end{center}

\subsection{Comparison to CycleGAN}
It is important to note that during the process of learning a mapping $F: X \rightarrow Y$, CycleGAN also learns a
mapping $G: Y \rightarrow X$. Here we show that UGAN and UGAN-P provide superior performance. We use the Canny edge
detector \cite{canny1986computational} to provide a color agnostic evaluation of the images, as the original contain
distorted colors and cannot be compared back to as ground truth. Due to the fact that restoring color information
should not alter the overall structure of the image, we measure the distance in the image space between the edges
found in the original and generated images. Figure ~\ref{fig:canny_samples} shows the original images and results from
edge detection. Table 1 provides the measurements from Figure ~\ref{fig:canny_samples}, as well as the average over the
entire dataset.

We explore the artifacts of content loss, as seen in Figure ~\ref{fig:zoom}. In particular, we compare local statistics
of the highlighted image patches, where each image patch is resized to $64 \times 64$. We use the GDL
\cite{mathieu2015deep} from (\ref{gdl_eq}) as a sharpness measure.

% I would like this table to match up with the figure showing edge detections. I wasn't able to
% get letters on the left side at each row though.
\begin{table}
\centering
\caption{Distances in image space}
\begin{tabular}{| c | c | c | c |}
   \hline
   Row/Method & CycleGAN & UGAN & UGAN-P \\ \hline
   A          & 116.45 & 85.71  & 86.15  \\ \hline
   B          & 114.49 & 97.92  & 101.01 \\ \hline
   C          & 120.84 & 96.53  & 97.57  \\ \hline
   D          & 129.27 & 108.90 & 110.50 \\ \hline
   Mean       & 111.60 & 94.91  & 96.51 \\ \hline
\end{tabular}
\end{table}

\newpage

\begin{figure}
\centering
\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.7cm}}

   ~\quad Original & ~CycleGAN & ~\quad UGAN & \quad UGAN-P \\

   \includegraphics[width=0.8in]{1_original} &
   \includegraphics[width=0.8in]{1_cimg} &
   \includegraphics[width=0.8in]{1_u0img} &
   \includegraphics[width=0.8in]{1_u1img} \\ [-1ex]
   \includegraphics[width=0.8in]{1_oedges} &
   \includegraphics[width=0.8in]{1_cedges} &
   \includegraphics[width=0.8in]{1_u0edges} &
   \includegraphics[width=0.8in]{1_u1edges} \\

   \includegraphics[width=0.8in]{2_original} &
   \includegraphics[width=0.8in]{2_cimg} &
   \includegraphics[width=0.8in]{2_u0img} &
   \includegraphics[width=0.8in]{2_u1img} \\ [-1ex]
   \includegraphics[width=0.8in]{2_oedges} &
   \includegraphics[width=0.8in]{2_cedges} &
   \includegraphics[width=0.8in]{2_u0edges} &
   \includegraphics[width=0.8in]{2_u1edges} \\

   \includegraphics[width=0.8in]{3_original} &
   \includegraphics[width=0.8in]{3_cimg} &
   \includegraphics[width=0.8in]{3_u0img} &
   \includegraphics[width=0.8in]{3_u1img} \\ [-1ex]
   \includegraphics[width=0.8in]{3_oedges} &
   \includegraphics[width=0.8in]{3_cedges} &
   \includegraphics[width=0.8in]{3_u0edges} &
   \includegraphics[width=0.8in]{3_u1edges} \\

   \includegraphics[width=0.8in]{4_original} &
   \includegraphics[width=0.8in]{4_cimg} &
   \includegraphics[width=0.8in]{4_u0img} &
   \includegraphics[width=0.8in]{4_u1img} \\ [-1ex]
   \includegraphics[width=0.8in]{4_oedges} &
   \includegraphics[width=0.8in]{4_cedges} &
   \includegraphics[width=0.8in]{4_u0edges} &
   \includegraphics[width=0.8in]{4_u1edges} \\

\end{tabular}
\caption{Running the Canny Edge Detector on sample images. Both variants of UGAN contain less noise than CycleGAN,
and are closer in the image space to the original. For each pair, the top row is the input image, and bottom row
the result of the edge detector.}
\label{fig:canny_samples}
\end{figure}

% TODO definitely need help with formatting, but content is there
\begin{figure*}
\centering
\begin{tabular}{p{4.0cm} p{4.0cm} p{4.0cm} p{4.0cm}}

   \qquad \qquad ~ Original & \qquad \qquad CycleGAN & \qquad \qquad ~ \textbf{UGAN} & \qquad \qquad \textbf{UGAN-P} \\

   \includegraphics[width=1.7in]{flickr_cmp} &
   \includegraphics[width=1.7in]{cgan_cmp} &
   \includegraphics[width=1.7in]{ugan_cmp} &
   \includegraphics[width=1.7in]{uganp_cmp} \\ [-11ex]

\end{tabular}
\end{figure*}

\begin{figure*}
\begin{tabular}{p{1.8cm} p{1.85cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.9cm} }

   \includegraphics[width=0.8in]{flickr_crop1} &
   \includegraphics[width=0.8in]{flickr_crop2} &
   \includegraphics[width=0.8in]{cgan_crop1} &
   \includegraphics[width=0.8in]{cgan_crop2} &
   \includegraphics[width=0.8in]{ugan_crop1} &
   \includegraphics[width=0.8in]{ugan_crop2} &
   \includegraphics[width=0.8in]{ugan_crop1} &
   \includegraphics[width=0.8in]{ugan_crop2} \\

   \includegraphics[width=0.8in]{flickr_crop3} &
   \includegraphics[width=0.8in]{flickr_crop4} &
   \includegraphics[width=0.8in]{cgan_crop3} &
   \includegraphics[width=0.8in]{cgan_crop4} &
   \includegraphics[width=0.8in]{ugan_crop3} &
   \includegraphics[width=0.8in]{ugan_crop4} &
   \includegraphics[width=0.8in]{ugan_crop3} &
   \includegraphics[width=0.8in]{ugan_crop4} \\

\end{tabular}
\caption{Comparison of local image patches. Each patch was resized to $64 \times 64$.}
\label{fig:zoom}
\end{figure*}

\subsection{Diver Tracking using Frequency-Domain Detection}
We investigate the frequency-domain characteristics of the restored images through a case-study of periodic motion tracking in 
sequence of images. Particularly, we compared the performance of Mixed Domain Periodic Motion (MDPM)- tracker 
\cite{islam2017mixed} on a sequence of images of a diver swimming in  arbitrary directions. MDPM tracker is designed for 
underwater robots to follow scuba divers by   tracking distinct frequency-domain signatures (high-amplitude spectra at $1$-$2$Hz) 
pertaining to human swimming. Amplitude spectra in frequency-domain correspond to the periodic intensity variations in image-space 
over time, which is often eroded in noisy underwater images \cite{shkurti2017underwater}.

Fig. \ref{mdpmStuff} illustrates the improved performance of MDPM tracker on generated images compared to the real ones. 
Underwater images often fail to capture the true contrast in intensity values between foreground and background due to low 
visibility. The generated images seem to restore these eroded intensity variations to some extent, causing much improved positive 
detection for MDPM tracker.

\begin{figure*}
\centering
\begin{tabular}{p{4.0cm} p{4.0cm} p{4.0cm} p{4.0cm}}
   \includegraphics[width=1.7in]{mdpm/real1} &
   \includegraphics[width=1.7in]{mdpm/real2} &
   \includegraphics[width=1.7in]{mdpm/real3} &
   \includegraphics[width=1.7in]{mdpm/real4} \\
   \includegraphics[width=1.7in]{mdpm/gen1} &
   \includegraphics[width=1.7in]{mdpm/gen2} &
   \includegraphics[width=1.7in]{mdpm/gen3} &
   \includegraphics[width=1.7in]{mdpm/gen4} \\
\end{tabular}
\label{fig:mdpm}
\vspace{4mm}

\begin{tabular}{l|c|c|c|r|}
 \cline{2-5}
 &  Correct detection & Wrong detection & Missed detection & Total \# of frames\\ \hline  \cline{2-4}
On real images  &  42 & 14 & 444 & 500  \\ \hline
On generated images  &  147 & 24 & 329 & 500  \\ \hline
\end{tabular}

\caption{Performance of MDPM tracker \cite{islam2017mixed} on both real (top row) and generated (second row) images; the Table 
compares the detection performance for both sets of images over a sequence of $500$ frames.   }
\label{mdpmStuff}
\end{figure*}

%Flippers of a human diver typically oscillate at frequencies between $1$ and $2$ Hz, which produces periodic intensity variations 
in the image-space over time. These variations correspond to distinct signatures in the frequency-domain (high-amplitude spectra 
at $1$-$2$Hz), which can be used for reliable detection.

### 2017-09-15 files/paper/tex/introduction.tex
Split the source into separate tex files for easy editing.

\section{Introduction}
%TODO - talk about having to go back to the same location if you want to get good/bad pairs of the ``same'' image.\starnote{I 
assume Cam will
%do this?}
Underwater robotics has been a steadily growing subfield of autonomous field robotics, assisted by the advent of novel platforms,
sensors and propulsion mechanisms. While autonomous underwater vehicles are often equipped with a variety of sensors, visual 
sensing is an
attractive option because of its non-intrusive, passive, and energy efficient nature. The monitoring of coral reefs 
\cite{shkurti2012multi},
deep ocean exploration \cite{whitcomb2000advances}, and mapping of the seabed~\cite{bingham2010robotic} are a number of tasks 
where
visually-guided AUVs and ROVs (Remotely Operated Vehicles) have seen widespread use. Use of these robots ensures humans are not 
exposed to
the hazards of underwater exploration, as they no longer need to venture to the depths (which was how such tasks were carried out 
in the
past). Despite the advantages of using vision, underwater environments pose unique challenges to visual sensing, as phenomena such 
as light
refraction, absorption and scattering from suspended particles can greatly affect the optics of light. As an example, because red
wavelengths are quickly absorbed by water, images tend to have a green or blue hue to them. As one goes deeper, this effect 
worsens, as more
and more red hue is absorbed. This distortion is extremely non-linear in nature, and is affected by a large number of factors, 
such as the
amount of light present (overcast versus sunny, operational depth), amount of particles in the water, time of day, and the camera 
being
used. This may cause difficulty in tasks such as segmentation, tracking, or classification due to their indirect or direct use of 
color.

As color and illumination begin to change with the depth, vision-based algorithms must need to be very generalizable in order to 
work within
the depth ranges a robot may operate in. Because of the high cost and difficulty of acquiring a variety of underwater data to 
train a visual
system on, as well as the high amount of noise introduced, algorithms may (and do) perform poorly in these different
domains. Figure~\ref{fig:samples} shows the high variability in visual scenes that may occur in
underwater environments. A step towards a solution to this issue is to be able to restore the images such that they appear to be 
above
water, \emph{i.e.}, with colors corrected and suspended particles removed from the scene. By performing a many-to-one mapping of 
these
domains from underwater to not underwater (what the image would look like above water), algorithms that have difficulty performing 
across
multiple forms of noise may be able to focus only one clean domain.

\begin{figure}
\centering
\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.7cm}}

   \includegraphics[width=0.8in]{n01496331_7428_f1} &
   \includegraphics[width=0.8in]{n01496331_16340_f1} &
   \includegraphics[width=0.8in]{n01914609_5148_f1} &
   \includegraphics[width=0.8in]{robot_f1} \\
   \includegraphics[width=0.8in]{n01664065_30279_f1} &
   \includegraphics[width=0.8in]{n01917289_5711_f1} &
   \includegraphics[width=0.8in]{n01917289_4087_f1} &
   \includegraphics[width=0.8in]{n02607072_10395_f1} \\

\end{tabular}
\label{fig:samples}
\caption{Sample underwater images with natural and man-made artifacts (which in this case is our underwater robot) displaying the 
diversity of distortion that can occur. With the varying camera-to-object distances in the images, the distortion and loss of 
color varies between the different images.}
\end{figure}

Deep neural networks have been shown to be powerful non-linear function approximators, especially in the field of vision 
\cite{krizhevsky2012imagenet}. Often times, these networks require large amounts of data, either labeled or paired with
ground truth. For the problem of automatically colorizing grayscale images \cite{zhang2016colorful}, paired training
data is
readily available due to the fact that any color image can be converted to black and white. However, underwater images distorted 
by either
color or some other phenomenon lack ground truth, which is a major hindrance towards adopting a similar approach for correction. 
This paper proposes a technique based on Generative Adversarial Networks (GANs) to improve the quality of visual underwater scenes 
with the goal of improving the performance of vision-driven behaviors for autonomous underwater robots
%\starnote{Summarize the approach here. Then talk about datasets as you have done already.}
We use the recently proposed CycleGAN~\cite{zhu2017unpaired} approach, which learns to translate an image from any arbitrary 
domain $X$ to another arbitrary domain $Y$ \textit{without} image pairs, as a way to generate a paired dataset.
By letting $X$ be a set of undistorted underwater images\starnote{need to say where we find the undistorted ones}, and
$Y$ be a set of distorted underwater images, we can generate an image that appears to be underwater while retaining
ground truth.

### 2017-09-15 files/paper/tex/methodology.tex
Split the source into separate tex files for easy editing.

\section{Methodology}
\label{sec:methodology}

\subsection{Dataset Generation}
Here we describe our dataset generation process. Depth, lighting conditions, camera
model, and location are all factors that affect the amount of distortion an underwater image undergoes. Under certain
conditions, it is possible that an underwater image may have very little distortion, or none at all.
We let $I^C$ be an underwater image with no distortion, and $I^D$
be the same image with distortion. Our goal is to learn the function $f: I^D \rightarrow I^C$. Becasue of the
difficulty of collecting underwater data, more often than not only $I^D$ or $I^C$ exist, but never both.

We use the recently proposed CycleGAN \cite{zhu2017unpaired} to generate $I^D$ from $I^C$, which gives us a paired
dataset of images. Given two datasets $X$ and $Y$, where $I^C \in X$ and $I^D \in Y$, CycleGAN learns a mapping
$F: X \rightarrow Y$. Figure ~\ref{fig:cgan_samples} shows paired samples generated from CycleGAN. From this paired dataset we 
train a
generator $G$ to learn the function $f: I^D \rightarrow I^C$. It should be noted that during our data generation process,
CycleGAN simultaneously learns a mapping $G: Y \rightarrow X$, which is similar to $f$. In section IV we show a comparison with 
our method.

\subsection{Adversarial Networks}
GANs \cite{goodfellow2014generative} are a class of generative models based on game theory in which a generator
network competes against an adversary. Conditioned on an image $I^D$, the generator is trained to produce an \
image to try and fool the discriminator, which is trained to distinguish be between distorted and non-distorted
underwater images. In the original GAN formulation, our goal is to solve the minimax problem:

\begin{figure}
\centering
\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.7cm}}

   \includegraphics[width=0.8in]{n01496331_873_X} &
   \includegraphics[width=0.8in]{n01664065_4022_X} &
   \includegraphics[width=0.8in]{n01917289_889_X} &
   \includegraphics[width=0.8in]{n01914609_116_X} \\
   \includegraphics[width=0.8in]{n01496331_873_Y} &
   \includegraphics[width=0.8in]{n01664065_4022_Y} &
   \includegraphics[width=0.8in]{n01917289_889_Y} &
   \includegraphics[width=0.8in]{n01914609_116_Y} \\

\end{tabular}
\label{fig:cgan_samples}
\caption{Paired samples of ground truth and distorted images generated by CycleGAN. Top row: Ground truth.
Bottom row: Generated samples.}
\end{figure}

\begin{equation}
\begin{aligned}
   \min\limits_{G}\max\limits_{D} \mathbb{E} & _{I^C \sim p_{train}(I^C)} [logD(I^C)] + \\
   \mathbb{E} & _{I^D \sim p_{gen}(I^D)}[log(1 - D(G(I^D)))]
\end{aligned}
\end{equation}

\noindent Note for simplicity in notation, we will further omit $I^C \sim p_{train}$ and $I^D \sim p_{gen}$. In this
formulation, the discriminator is hypothesized as a classifier with a sigmoid cross entropy loss function, which in
practice may lead to issues such as the vanish gradient and mode collapse. There have been many recent works which
hypothesize a different loss function for the discriminator
\cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}. We focus on the Wasserstein GAN
(WGAN) \cite{arjovsky2017wasserstein} formulation, which proposes to use the Earth-Mover or \textit{Wasserstein-1}
distance $W$ by constructing a value function using the Kantorovich-Rubinstein duality \cite{villani2008optimal}.
In this formulation, $W$ is approximated given a set of $k$-Lipschitz functions $f$ modeled as neural networks. To
ensure $f$ is $k$-Lipschitz, the weights of the discriminator are clipped to some range $[-c, c]$. In our work, we
adopt the Wasserstein GAN with gradient penalty (WGAN-GP) \cite{gulrajani2017improved}, which instead of clipping
network weights like in \cite{arjovsky2017wasserstein}, ensures the Lipschitz constraint by enforcing a soft
constraint on the gradient norm of the discriminator's output with respect to its input. Following
\cite{gulrajani2017improved}, our new objective then becomes

\begin{equation}
\begin{aligned}
   \mathcal{L}_{WGAN}(G,D) = \mathbb{E} [D(I^C)] - \mathbb{E} & [D(G(I^D))] + \\
   \lambda_{GP} \mathbb{E} & _{\hat{x} \sim \mathbb{P}_{\hat{x}}} [(|| \nabla_{\hat{x}} D(\hat{x})||_2 -1)^2 ],
\end{aligned}
\end{equation}

%\begin{equation}
%\begin{aligned}
%   \mathcal{L}_{GAN} = \mathbb{E}_{I^D \sim p_{gen}(I^D)} [D(I^D)] - \mathbb{E} & _{I^C \sim p_{train}(I^C)} [D(I^C)] + \\
%   \lambda \mathbb{E} & _{\hat{x} \sim \mathbb{P}_{\hat{x}}} [(|| \nabla_{\hat{x}} D(\hat{x})||_2 -1)^2 ].
%\end{aligned}
%\end{equation}

\noindent where $\mathbb{P}_{\hat{x}}$ is defined as samples along straight lines between pairs of points coming from
the true data distribution and the generator distribution, and $\lambda_{GP}$ is a weighing factor. In order to give $G$
some sense of ground truth, as well as capture low level frequencies in the image, we also consider the $L1$ loss

\begin{equation}
   \mathcal{L}_{L1} = \mathbb{E} [ || I^C - G(I^D) ||_1 ].
\end{equation}
%\begin{equation}
%   \mathcal{L}_{L1} = \mathbb{E}_{I^D \sim p_{gen}, I^C \sim p_{train}} [ || I^C - G(I^D) ||_1 ].
%\end{equation}

\noindent Combining these, we get our final objective function for our network, which we call Underwater GAN (UGAN),

\begin{equation}
   \begin{aligned}
      \mathcal{L}_{UGAN}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + \lambda_{1} \mathcal{L}_{L1}(G).
   \end{aligned}
\end{equation}

\subsection{Image Gradient Difference Loss}
Often times generative models produce blurry images. We explore a strategy to sharpen these predictions by
directly penalizing the differences of image gradient predictions in the generator, as proposed by
\cite{mathieu2015deep}. Given a ground truth image $I^C$, predicted image $I^P = G(I^D)$, and $\alpha \geq 1$, the
Gradient Difference Loss (GDL) is given by

\begin{equation}
   \begin{aligned}
      \mathcal{L}_{GDL}(I^C, I^P) = \\ \sum\limits_{i,j} || & I^C_{i,j} - I^C_{i-1,j}| - | I^P_{i,j} - I^P_{i-1,j}||^{\alpha} + \\
      || & I^C_{i,j-1} - I^C_{i,j}| - | I^P_{i,j-1} - I^P_{i,j}||^{\alpha}.
   \end{aligned}
   \label{gdl_eq}
\end{equation}

\noindent In our experiments, we denote our network as UGAN-P when considering the GDL, which can be expressed as
\starnote{JS: DONE. I don't like the - in this equation, but don't know how to change it to be shorter}

\begin{equation}
   \begin{aligned}
      \mathcal{L}_{UGAN\scalebox{0.4}[1.0]{\( - \)}P}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + & \\
      % \mathcal{L}_{UGAN-P}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + & \\
      \lambda_{1} \mathcal{L}_{L1}(G) + & \lambda_{2} \mathcal{L}_{GDL}
   \end{aligned}
\end{equation}

\subsection{Network Architecture and Training Details}
Our generator network is a fully convolutional encoder-decoder, similar to the work of \cite{isola2016image}, which is
designed as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.
Encoder-decoder networks downsample (encode) the input via convolutions to a lower dimensional embedding, in which
this embedding is then upsampled (decode) via transpose convolutions to reconstruct an image. The advantage of using
a ``U-Net'' comes from explicitly preserving spatial dependencies produced by the encoder, as opposed to relying on the
embedding to contain all of the information. This is done by the addition of ``skip connections'', which concatenate
the activations produced from a convolution layer $i$ in the encoder to the input of a transpose convolution layer
$n-i+1$ in the decoder, where $n$ is the total number of layers in the network. Each convolutional layer in our
generator uses kernel size $4 \times 4$ with stride 2. Convolutions in the encoder portion of the network are followed
by batch normalization \cite{pmlr-v37-ioffe15} and a leaky ReLU activation with slope $0.2$, while transpose
convolutions in the decoder are followed by a ReLU activation \cite{nair2010rectified} (no batch norm in the decoder).
Exempt from this is the last layer of the decoder, which uses a TanH nonlinearity to match the input distribution of
$[-1, 1]$. Recent work has proposed Instance Normalization \cite{ulyanov2016instance} to improve quality
in image-to-image translation tasks, however we observed no added benefit.

Our fully convolutional discriminator is modeled after that of \cite{radford2015unsupervised}, except no batch
normalization is used. This is due to the fact that WGAN-GP penalizes the norm of the discriminator's gradient with
respect to each input individually, which batch normalization would invalidate. The authors of
\cite{gulrajani2017improved} recommend layer normalization \cite{ba2016layer}, but we found no significant improvements.
Our discriminator is modeled as a PatchGAN \cite{isola2016image,li2016precomputed}, which discriminates at the level of
image patches. As opposed to a regular discriminator, which outputs a scalar value corresponding to real or fake, our
PatchGAN discriminator outputs a $32 \times 32 \times 1$ feature matrix, which provides a metric for high level
frequencies. %which is combinied with the low level frequencies from the $L1$ loss.

In all of our experiments, we use $\lambda_{1} = 100$, $\lambda_{GP} = 10$, batch size of 32, and the Adam Optimizer
\cite{kingma2014adam} with learning rate $1e-4$. Following WGAN-GP, the discriminator is updated $n$ times for every
update of the generator, where $n = 5$. For UGAN-P, we set $\lambda_{2} = 1.0$ and $\alpha = 1$. Our implementation was done using 
the
Tensorflow library \cite{abadi2016tensorflow}.
\footnote{Code is available at \url{https://github.com/cameronfabbri/Underwater-Color-Correction}}
All networks were trained from scratch on a GTX 1080 for 100 epochs. Inference on the GPU takes on average $ 0.0138s$,
which is about 72 Frames Per Second (FPS). On a CPU (Intel Core i7-5930K), inference takes on average $ 0.1244s$, which
is about 8 FPS. We find both of these measures acceptable for underwater tasks.

### 2017-09-15 files/paper/tex/related.tex
Split the source into separate tex files for easy editing.

\section{Related Work}
\label{sec:related}

While there have been a number of successful recent approaches towards automatic colorization 
\cite{zhang2016colorful,iizuka2016let}, most are focused on the task of converting grayscale images to color. Quite a few 
approaches use a physics-based technique to directly model light refraction~\cite{jordt2014underwater}. Specifically for
restoring color in underwater images, the work of~\cite{torres2005color} uses an energy minimization formulation using a Markov 
Random Field. Most similar to the work proposed in this paper is the recently proposed WaterGAN~\cite{li2017watergan}, 
which uses an adversarial approach towards generating realistic underwater images. Their generator model can be broken down into 
three stages: 1) Attenuation, which accounts for range-dependent attenuation of light. 2) Scattering, which models the haze 
effect caused by photons scattering back towards the image sensor and 3) Vignetting, which produces a shading effect on the 
image corners that can be caused by certain camera lenses. Differentiating from our work, they use a GAN for generating the 
underwater images and use strictly Euclidean loss for color correction, whereas we use a GAN for both. Furthermore, they require 
depth information during the training of WaterGAN, which can be often difficult to attain particularly for underwater 
autonomous robotic applications. Our work only requires images of objects in two separate domains (\emph{e.g.}, underwater 
and terrestrial) throughout the entire process.

Recent work in generative models, specifically GANs, have shown great success in areas such as inpainting 
\cite{pathak2016context}, style transfer \cite{Gatys_2016_CVPR}, and image-to-image translation 
\cite{isola2016image,zhu2017unpaired}. This is primarily due to their ability to provide a more meaningful loss than simply the 
Euclidean distance, which has been shown to produce blurry results. In our work, we structure the problem of estimating 
the true appearance of underwater imagery as a paired image-to-image translation problem, using Generative Adversarial Networks 
(GANs) as our generative model\starnote{this needs a little bit more expansion}. Much like the work of \cite{isola2016image}, we 
use image pairs from two domains as input and ground truth. \starnote{Somewhere I think we should mention that unpaired image to 
image translation is more difficult, and that cyclegan is a good way to generate a dataset in such a way to do this with image 
pairs.}

### 2017-09-15 files/paper/tex/experiments.tex
Moved some sections to experiments. Added text to methodology.

@@
 \section{Experiments}
+\label{sec:experiments}
+
 \subsection{Datasets}
@@
 %\end{center}
+
+\subsection{Training and Inference Performance}
+In all of our experiments, we use $\lambda_{1} = 100$, $\lambda_{GP} = 10$, batch size of 32, and the Adam Optimizer 
+\cite{kingma2014adam} with learning rate $1e-4$. Following WGAN-GP, the discriminator is updated $n$ times for every update of the 
+generator, where $n = 5$. For UGAN-P, we set $\lambda_{2} = 1.0$ and $\alpha = 1$. Our implementation was done using the 
+Tensorflow library \cite{abadi2016tensorflow}. \footnote{Code is available at 
+\url{https://github.com/cameronfabbri/Underwater-Color-Correction}} All networks were trained from scratch on a GTX 1080 for 100 
+epochs. Inference on the GPU takes on average $ 0.0138s$, which is about 72 Frames Per Second (FPS). On a CPU (Intel Core 
+i7-5930K), inference takes on average $ 0.1244s$, which is about 8 FPS. We find both of these measures acceptable for underwater 
+tasks.
 

### 2017-09-15 files/paper/tex/methodology.tex
Moved some sections to experiments. Added text to methodology.

@@
 \label{sec:methodology}
+\starnote{A short summary of the method needs to go here, like an overview, so the reader can `stay in the loop' so to speak.}
 
 \subsection{Dataset Generation}
-Here we describe our dataset generation process. Depth, lighting conditions, camera
-model, and location are all factors that affect the amount of distortion an underwater image undergoes. Under certain
-conditions, it is possible that an underwater image may have very little distortion, or none at all.
-We let $I^C$ be an underwater image with no distortion, and $I^D$
-be the same image with distortion. Our goal is to learn the function $f: I^D \rightarrow I^C$. Becasue of the
-difficulty of collecting underwater data, more often than not only $I^D$ or $I^C$ exist, but never both.
+Depth, lighting conditions, camera model, and physical location in the underwater environment are all factors that affect the 
+amount of distortion an image will be subjected to. Under certain conditions, it is possible that an underwater image may have 
+very little distortion, or none at all. To generate the dataset to train the generative model\starnote{check this please}, we let 
+$I^C$ be an underwater image with no distortion, and $I^D$ be the same image with distortion. Our goal is to learn the function 
+$f: I^D \rightarrow I^C$. Becasue of the difficulty of collecting underwater data, more often than not only $I^D$ or $I^C$ exist, 
+but never both.
 
-We use the recently proposed CycleGAN \cite{zhu2017unpaired} to generate $I^D$ from $I^C$, which gives us a paired
-dataset of images. Given two datasets $X$ and $Y$, where $I^C \in X$ and $I^D \in Y$, CycleGAN learns a mapping
-$F: X \rightarrow Y$. Figure ~\ref{fig:cgan_samples} shows paired samples generated from CycleGAN. From this paired dataset we 
-train a
-generator $G$ to learn the function $f: I^D \rightarrow I^C$. It should be noted that during our data generation process,
-CycleGAN simultaneously learns a mapping $G: Y \rightarrow X$, which is similar to $f$. In section IV we show a comparison with 
-our method.
+To circumvent the problem of insufficient image data in $I^D$, we use CycleGAN to generate $I^D$ from $I^C$, which gives us a 
+paired dataset of images. Given two datasets $X$ and $Y$, where $I^C \in X$ and $I^D \in Y$, CycleGAN learns a mapping $F: X 
+\rightarrow Y$. Figure~\ref{fig:cgan_samples} shows paired samples generated from CycleGAN. From this paired dataset we train a 
+generator $G$ to learn the function $f: I^D \rightarrow I^C$. It should be noted that during our data generation process, CycleGAN 
+simultaneously learns a mapping $G: Y \rightarrow X$, which is similar to $f$. In Section~\ref{sec:experiments}, we compare images 
+generated by CycleGAN with images generated through our approach.
 
 \subsection{Adversarial Networks}
-GANs \cite{goodfellow2014generative} are a class of generative models based on game theory in which a generator
-network competes against an adversary. Conditioned on an image $I^D$, the generator is trained to produce an \
-image to try and fool the discriminator, which is trained to distinguish be between distorted and non-distorted
-underwater images. In the original GAN formulation, our goal is to solve the minimax problem:
+\starnote{check this paragraph as I added some more text}In machine learning literature, Generative Adversarial Networks 
+(GANs)~\cite{goodfellow2014generative} represent a class of generative models based on game theory in which a generator network 
+competes against an adversary. From a classification perspective, the generator network produces instances which actively attempts 
+to `mislead' the discriminator network. The goal is for the discriminator network to be able to distinguish between `true' 
+instances and the `false' but realistic looking instances produced by the generator network, and thus improve its classification 
+accuracy. In our case, conditioned on an image $I^D$, the generator is trained to produce an image to try and confuse the 
+discriminator, which is trained to distinguish between distorted and non-distorted underwater images. In the original GAN 
+formulation, our goal is to solve the minimax problem:
 
@@
 
-\noindent Note for simplicity in notation, we will further omit $I^C \sim p_{train}$ and $I^D \sim p_{gen}$. In this
-formulation, the discriminator is hypothesized as a classifier with a sigmoid cross entropy loss function, which in
-practice may lead to issues such as the vanish gradient and mode collapse. There have been many recent works which
-hypothesize a different loss function for the discriminator
+Note for simplicity in notation, we will further omit $I^C \sim p_{train}$ and $I^D \sim p_{gen}$. In this formulation, 
+the discriminator is hypothesized as a classifier with a sigmoid cross-entropy loss function, which in practice may lead to issues 
+such as the vanish gradient and mode collapse~\starnote{Clarify?}. There have been a number of recent methods which hypothesize a 
+different loss function for the discriminator
 \cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}. We focus on the Wasserstein GAN
@@
 frequencies. %which is combinied with the low level frequencies from the $L1$ loss.
-
-In all of our experiments, we use $\lambda_{1} = 100$, $\lambda_{GP} = 10$, batch size of 32, and the Adam Optimizer
-\cite{kingma2014adam} with learning rate $1e-4$. Following WGAN-GP, the discriminator is updated $n$ times for every
-update of the generator, where $n = 5$. For UGAN-P, we set $\lambda_{2} = 1.0$ and $\alpha = 1$. Our implementation was done using 
-the
-Tensorflow library \cite{abadi2016tensorflow}.
-\footnote{Code is available at \url{https://github.com/cameronfabbri/Underwater-Color-Correction}}
-All networks were trained from scratch on a GTX 1080 for 100 epochs. Inference on the GPU takes on average $ 0.0138s$,
-which is about 72 Frames Per Second (FPS). On a CPU (Intel Core i7-5930K), inference takes on average $ 0.1244s$, which
-is about 8 FPS. We find both of these measures acceptable for underwater tasks.

### 2017-09-15 files/paper/tex/introduction.tex

@@
 This paper proposes a technique based on Generative Adversarial Networks (GANs) to improve the quality of visual underwater scenes 
-with the goal of improving the performance of vision-driven behaviors for autonomous underwater robots
+with the goal of improving the performance of vision-driven behaviors for autonomous underwater robots.
 %\starnote{Summarize the approach here. Then talk about datasets as you have done already.}

### 2017-09-16 files/paper/tex/methodology.tex
update

@@
 \label{sec:methodology}
-\starnote{A short summary of the method needs to go here, like an overview, so the reader can `stay in the loop' so to speak.}
+Underwater images distorted by color or circumstance lack ground truth, which is a necessity for previous colorization
+approaches. Furthermore, the distortion present in an underwater image is highly nonlinear; simple methods such as
+adding a hue to an image do not capture all of the dependencies. We propose to use CycleGAN as a distortion model in
+order to generate paired images for training. Given a domain of underwater images with no distortion, and a domain of
+underwater images with distortion, CycleGAN is able to perform style transfer. Given an undistorted image, CycleGAN
+distorts it such that it appears to have come from the domain of distorted images. These pairs are then used in our
+algorithm for image reconstruction.
 

### 2017-09-16 classify/train.py

@@ -1,16 +1,6 @@
-'''
-
-   Main training file
-
-   The goal is to correct the colors in underwater images.
-   CycleGAN was used to create images that appear to be underwater.
-   Those will be sent into the generator, which will attempt to correct the
-   colors.
-
-'''
-
 import cPickle as pickle
 import tensorflow as tf
+slim = tf.contrib.slim
 from tqdm import tqdm
 from scipy import misc
 import numpy as np
@@ -21,151 +11,46 @@ import os
 import time
 import glob
 
-sys.path.insert(0, 'ops/')
-sys.path.insert(0, 'nets/')
+sys.path.insert(0, '../ops/')
 from tf_ops import *
 
 import data_ops
 
+from alexnet import *
+
 if __name__ == '__main__':
    parser = argparse.ArgumentParser()
-   parser.add_argument('--DATA',          required=False,default='rocks',type=str,help='Dataset to use')
-   parser.add_argument('--EPOCHS',        required=False,default=4,type=int,help='Number of epochs for GAN')
-   parser.add_argument('--NETWORK',       required=False,default='pix2pix',type=str,help='Network to use')
-   parser.add_argument('--L1_WEIGHT',     required=False,default=100.,type=float,help='Weight for L1 loss')
-   parser.add_argument('--IG_WEIGHT',     required=False,default=1.,type=float,help='Weight for image gradient loss')
    parser.add_argument('--BATCH_SIZE',    required=False,default=32,type=int,help='Batch size')
-   parser.add_argument('--LOSS_METHOD',   required=False,default='gan',help='Loss function for GAN')
    parser.add_argument('--LEARNING_RATE', required=False,default=2e-5,type=float,help='Learning rate')
    a = parser.parse_args()
 
    LEARNING_RATE = float(a.LEARNING_RATE)
-   LOSS_METHOD   = a.LOSS_METHOD
    BATCH_SIZE    = a.BATCH_SIZE
-   L1_WEIGHT     = float(a.L1_WEIGHT)
-   IG_WEIGHT     = float(a.IG_WEIGHT)
-   NETWORK       = a.NETWORK
-   EPOCHS        = a.EPOCHS
-   DATA          = a.DATA
[…]

### 2017-09-16 tests/stats.py

@@ -1,0 +1,27 @@
+import scipy.misc as misc
+import math
+import numpy as np
+import cv2
+
+for i in range(1,5):
+
+   flickr = cv2.imread('result_images/flickr_crop'+str(i)+'_og.png')/255.0
+   cgan   = cv2.imread('result_images/cgan_crop'  +str(i)+'_og.png')/255.0
+   ugan   = cv2.imread('result_images/ugan_crop'  +str(i)+'_og.png')/255.0
+   uganp  = cv2.imread('result_images/uganp_crop' +str(i)+'_og.png')/255.0
+
+   print 'crop',i
+   print 'Variance'
+   print 'real:  ',np.var(flickr)
+   print 'cgan:  ',np.var(cgan)
+   print 'ugan:  ',np.var(ugan)
+   print 'uganp: ',np.var(uganp)
+   print
+   print 'Mean'
+   print 'real:  ',np.mean(flickr)
+   print 'cgan:  ',np.mean(cgan)
+   print 'ugan:  ',np.mean(ugan)
+   print 'uganp: ',np.mean(uganp)
+   print
+   print '---'
+   print

### 2017-09-16 files/paper/tex/methodology.tex
update

@@
 amount of distortion an image will be subjected to. Under certain conditions, it is possible that an underwater image may have 
-very little distortion, or none at all. To generate the dataset to train the generative model\starnote{check this please}, we let 
+very little distortion, or none at all. We let 
 $I^C$ be an underwater image with no distortion, and $I^D$ be the same image with distortion. Our goal is to learn the function 
@@
 
-To circumvent the problem of insufficient image data in $I^D$, we use CycleGAN to generate $I^D$ from $I^C$, which gives us a 
+To circumvent the problem of insufficient image pairs, we use CycleGAN to generate $I^D$ from $I^C$, which gives us a 
 paired dataset of images. Given two datasets $X$ and $Y$, where $I^C \in X$ and $I^D \in Y$, CycleGAN learns a mapping $F: X 
@@
 (GANs)~\cite{goodfellow2014generative} represent a class of generative models based on game theory in which a generator network 
-competes against an adversary. From a classification perspective, the generator network produces instances which actively attempts 
-to `mislead' the discriminator network. The goal is for the discriminator network to be able to distinguish between `true' 
-instances and the `false' but realistic looking instances produced by the generator network, and thus improve its classification 
-accuracy. In our case, conditioned on an image $I^D$, the generator is trained to produce an image to try and confuse the 
-discriminator, which is trained to distinguish between distorted and non-distorted underwater images. In the original GAN 
-formulation, our goal is to solve the minimax problem:
+competes against an adversary. From a classification perspective, the generator network produces instances which actively attempt 
+to `fool' the discriminator network. The goal is for the discriminator network to be able to distinguish between `true' 
+instances coming from the dataset and `false' instances produced by the generator network.
+%, and thus improve its classification accuracy.
+In our case, conditioned on an image $I^D$, the generator is trained to produce an image to try and fool the 
+discriminator, which is trained to distinguish between distorted and non-distorted underwater images. In the original
+GAN formulation, our goal is to solve the minimax problem:
 
@@
 Note for simplicity in notation, we will further omit $I^C \sim p_{train}$ and $I^D \sim p_{gen}$. In this formulation, 
-the discriminator is hypothesized as a classifier with a sigmoid cross-entropy loss function, which in practice may lead to issues 
-such as the vanish gradient and mode collapse~\starnote{Clarify?}. There have been a number of recent methods which hypothesize a 
-different loss function for the discriminator
+the discriminator is hypothesized as a classifier with a sigmoid cross-entropy loss function, which in practice may lead
+to issues  such as the vanish gradient and mode collapse. As shown by \cite{arjovsky2017towards}, as
+the discriminator improves, the gradient of the generator vanishes, making it difficult or impossible to train. Mode
+collapse occurs when the generator ``collapses'' onto a single point, fooling the discriminator with only one instance
+\starnote{Such as when you are training a GAN to generate digits from MNIST, but it only generates a 7, when in reality
+you'd want it to generate a diverse amount of all the digits. Not sure if we should expand more.}.
+There have been a number of recent methods which hypothesize a different loss function for the discriminator
 \cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}. We focus on the Wasserstein GAN
@@
 \noindent In our experiments, we denote our network as UGAN-P when considering the GDL, which can be expressed as
-\starnote{JS: DONE. I don't like the - in this equation, but don't know how to change it to be shorter}
+%\starnote{JS: DONE. I don't like the - in this equation, but don't know how to change it to be shorter}
 

### 2017-09-16 files/paper/tex/methodology.tex
Minor edits.

@@
 \subsection{Adversarial Networks}
-\starnote{check this paragraph as I added some more text}In machine learning literature, Generative Adversarial Networks 
+\nostarnote{check this paragraph as I added some more text}In machine learning literature, Generative Adversarial Networks 
 (GANs)~\cite{goodfellow2014generative} represent a class of generative models based on game theory in which a generator network 
@@
 \end{tabular}
-\label{fig:cgan_samples}
 \caption{Paired samples of ground truth and distorted images generated by CycleGAN. Top row: Ground truth.
 Bottom row: Generated samples.}
+\label{fig:cgan_samples}
 \end{figure}

### 2017-09-16 tests/compare_hist.py
update

@@ -1,6 +1,7 @@
 import cv2
 import numpy as np
 from scipy.stats import signaltonoise
+import math
 
 def gdl(generated, true):
 
@@ -28,6 +29,9 @@ def gdl(generated, true):
 
    return loss
 
+def psnr(img1, img2):
+   mse = np.mean( (img1 - img2) ** 2 )
+   return 10 * math.log10(255.0**2/mse)
 
 for i in range(1,5):
 
@@ -72,10 +76,14 @@ for i in range(1,5):
    print 'flickr_ugan bhatt :',b
    print 'flickr_uganp bhatt:',c
    print
-   print 'snr flickr        :', signaltonoise(flickr, axis=None)
+   print 'snr flickr        :',signaltonoise(flickr, axis=None)
    print 'snr cgan          :',signaltonoise(cgan, axis=None)
    print 'snr ugan          :',signaltonoise(ugan, axis=None)
    print 'snr uganp         :',signaltonoise(uganp, axis=None)
+   print
+   print 'cgan:             ',psnr(flickr,cgan)
+   print 'ugan:             ',psnr(flickr,ugan)
+   print 'uganp:            ',psnr(flickr,uganp)
    print
    print 'laplac flickr     :',cv2.Laplacian(flickr, cv2.CV_64F).var()
    print 'laplac cgan       :',cv2.Laplacian(cgan, cv2.CV_64F).var()

### 2017-09-16 tests/compare_hist.py
update

@@ -54,42 +54,50 @@ for i in range(1,5):
    ugan   = ugan/255.0
    uganp  = uganp/255.0
 
+   '''
    print '+--------+'
    print '|  crop'+str(i)+' |'
    print '+--------+'
    print 
-   print 'gdl flickr-cgan   :',gdl(flickr, cgan)
-   print 'gdl flickr-ugan   :',gdl(flickr, ugan)
-   print 'gdl flickr-uganp  :',gdl(flickr, uganp)
+   print 'gdl flickr-cgan    :',gdl(flickr, cgan)
+   print 'gdl flickr-ugan    :',gdl(flickr, ugan)
+   print 'gdl flickr-uganp   :',gdl(flickr, uganp)
    print
-   print 'flickr_mean       :',np.mean(flickr)
-   print 'cgan_mean         :',np.mean(cgan)
-   print 'ugan_mean         :',np.mean(ugan)
-   print 'uganp_mean        :',np.mean(uganp)
+   print 'flickr_mean        :',np.mean(flickr)
+   print 'cgan_mean          :',np.mean(cgan)
+   print 'ugan_mean          :',np.mean(ugan)
+   print 'uganp_mean         :',np.mean(uganp)
    print
-   print 'flickr_var        :',np.var(flickr)
-   print 'cgan_var          :',np.var(cgan)
-   print 'ugan_var          :',np.var(ugan)
-   print 'uganp_var         :',np.var(uganp)
+   print 'flickr_std         :',np.std(flickr)
+   print 'cgan_std           :',np.std(cgan)
+   print 'ugan_std           :',np.std(ugan)
+   print 'uganp_std          :',np.std(uganp)
    print
-   print 'flickr_cgan bhatt :',a
-   print 'flickr_ugan bhatt :',b
-   print 'flickr_uganp bhatt:',c
+   print 'flickr_var         :',np.var(flickr)
+   print 'cgan_var           :',np.var(cgan)
+   print 'ugan_var           :',np.var(ugan)
+   print 'uganp_var          :',np.var(uganp)
    print
-   print 'snr flickr        :',signaltonoise(flickr, axis=None)
-   print 'snr cgan          :',signaltonoise(cgan, axis=None)
-   print 'snr ugan          :',signaltonoise(ugan, axis=None)
-   print 'snr uganp         :',signaltonoise(uganp, axis=None)
[…]

### 2017-09-16 files/paper/tex/experiments.tex
Minor edits.
update

@@
 of the highlighted image patches, where each image patch is resized to $64 \times 64$. We use the GDL
-\cite{mathieu2015deep} from (\ref{gdl_eq}) as a sharpness measure.
+\cite{mathieu2015deep} from (\ref{gdl_eq}) as a sharpness measure. Laplacian stuff \cite{pertuz2013analysis}
 
@@
 
-\newpage
+%\newpage
 
@@
    \includegraphics[width=1.7in]{ugan_cmp} &
-   \includegraphics[width=1.7in]{uganp_cmp} \\ [-11ex]
+   \includegraphics[width=1.7in]{uganp_cmp} \\ [-2ex]
 
@@
 \end{figure*}
+
+\begin{table}[ht]
+\footnotesize
+\centering
+\caption{Gradient Difference Loss Metrics}
+\begin{tabular}{| c | c | c | c | }
+   \hline
+   Patch/Method & CycleGAN & UGAN & UGAN-P \\ \hline
+   Red    & 11.53 & 9.39 & 10.93  \\ \hline
+   Blue   & 7.52  & 4.83 &  5.50\\ \hline
+   Green  & 4.15  & 3.18 & 3.25 \\ \hline
+   Orange & 6.72  & 5.65 & 5.79 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[ht]
+\footnotesize
+\centering
+\caption{Mean and Standard Deviation Metrics}
+\begin{tabular}{| c | c | c | c | c | }
+   \hline
+   Patch/Method & Original & CycleGAN & UGAN & UGAN-P \\ \hline
+   Red & 0.43 $\pm$ 0.23 & 0.42 $\pm$ 0.22 & 0.44 $\pm$ 0.23 & 0.45 $\pm$ 0.25 \\ \hline
+   Blue & 0.51 $\pm$ 0.18 & 0.57 $\pm$ 0.17 & 0.57 $\pm$ 0.17 & 0.57 $\pm$ 0.17 \\ \hline
+   Green & 0.36 $\pm$ 0.17 & 0.36 $\pm$ 0.14 & 0.37 $\pm$ 0.17 & 0.36 $\pm$ 0.17 \\ \hline
+   Orange & 0.3 $\pm$ 0.15 & 0.25 $\pm$ 0.12 & 0.26 $\pm$ 0.13 & 0.27 $\pm$ 0.14 \\ \hline
+\end{tabular}
+\end{table}
 

### 2017-09-16 files/paper/tex/experiments.tex
update

@@
 It is important to note that during the process of learning a mapping $F: X \rightarrow Y$, CycleGAN also learns a
-mapping $G: Y \rightarrow X$. Here we show that UGAN and UGAN-P provide superior performance. We use the Canny edge
+mapping $G: Y \rightarrow X$. Here we give a comparison to our methods. We use the Canny edge
 detector \cite{canny1986computational} to provide a color agnostic evaluation of the images, as the original contain
@@
 found in the original and generated images. Figure ~\ref{fig:canny_samples} shows the original images and results from
-edge detection. Table 1 provides the measurements from Figure ~\ref{fig:canny_samples}, as well as the average over the
-entire dataset.
+edge detection. Table 1 provides the measurements from Figure ~\ref{fig:canny_samples}, as well as the average over our
+entire Flickr\texttrademark ~dataset. Both UGAN and UGAN-P are consistently closer in the image space to the original
+than that of CycleGAN, suggesting noise due to blur. Next, we evaluate this noise explicitly.
 
@@
 of the highlighted image patches, where each image patch is resized to $64 \times 64$. We use the GDL
-\cite{mathieu2015deep} from (\ref{gdl_eq}) as a sharpness measure. Laplacian stuff \cite{pertuz2013analysis}
+\cite{mathieu2015deep} from (\ref{gdl_eq}) as a sharpness measure. A lower GDL measure implies a smoother transition
+between pixels, as a noisy image would have large jumps in the image's gradient, leading to a higher score.
+\starnote{I THINK.
+I would double check, bottom of page 4: https://arxiv.org/pdf/1511.05440.pdf}.
+As seen in Table \ref{fig:gdl_tbl}, the GDL is lower for both UGAN and UGAN-P. Interestingly, UGAN consistently has a
+lower score than UGAN-P, despite UGAN-P explicitly accounting for this metric in the objective function. Reasoning for
+this is left for our future work.
 
@@
 \end{tabular}
+\label{fig:gdl_tbl}
 \end{table}

### 2017-09-16 files/paper/tex/experiments.tex
update

@@
 
+Another metric we can use to compare image patches are the mean and standard deviation of a patch. The standard
+deviation gives us a sense of blurriness because it defines how far the data deviates from the mean. A lower standard
+deviation means that the data is closer to the mean \starnote{not sure if we exactly need to say that because I assume the reviewers will know what it is}.
+In the case of images, this would suggest a blurring effect due to the data being
+more clustered toward one pixel value. Table \ref{fig:mean_tbl} shows the mean and standard deviations for the local
+image patches seen in Figure \ref{fig:zoom}.
+
 % I would like this table to match up with the figure showing edge detections. I wasn't able to
@@
    \hline
-   Row/Method & CycleGAN & UGAN & UGAN-P \\ \hline
+   Row/Method & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ \hline
    A          & 116.45 & 85.71  & 86.15  \\ \hline
@@
 
-   ~\quad Original & ~CycleGAN & ~\quad UGAN & \quad UGAN-P \\
+   ~\quad Original & ~CycleGAN & ~\quad \textbf{UGAN} & \quad \textbf{UGAN-P} \\
 
@@
 \end{tabular}
+\label{fig:mean_tbl}
 \end{table}

### 2017-09-16 files/paper/tex/related.tex
Editing stuff for final version.

@@
 the true appearance of underwater imagery as a paired image-to-image translation problem, using Generative Adversarial Networks 
-(GANs) as our generative model\starnote{this needs a little bit more expansion}. Much like the work of \cite{isola2016image}, we 
+(GANs) as our generative model (see Section~\ref{sec:gans} for details). Much like the work of \cite{isola2016image}, we 
 use image pairs from two domains as input and ground truth. \starnote{Somewhere I think we should mention that unpaired image to 
-image translation is more difficult, and that cyclegan is a good way to generate a dataset in such a way to do this with image 
+image translation is more difficult, and that CycleGAN is a good way to generate a dataset in such a way to do this with image 
 pairs.}

### 2017-09-16 files/paper/tex/experiments.tex
update

@@
 
-We use three metrics for a quantitative evaluation. First, we compare to CycleGAN, as it inherently learns an inverse
-mapping during the training of $F: X \rightarrow Y$, using the Canny edge detector
-\cite{canny1986computational}. This provides a color agnostic evaluation of the images in comparison to ground truth.
+For a quantitative evaluation we compare to CycleGAN, as it inherently learns an inverse mapping during the training of
+$G: Y \rightarrow X$. We first use the Canny edge detector
+\cite{canny1986computational}, as this provides a color agnostic evaluation of the images in comparison to ground truth.
 Second, we compare local image patches to provide sharpness metrics on our images. Lastly, we show how an existing
@@
 
-   ~\quad Original & ~\quad UGAN & \quad UGAN-P \\
+   ~\quad Original & ~\quad \textbf{UGAN} & \quad \textbf{UGAN-P} \\
 
@@
 more clustered toward one pixel value. Table \ref{fig:mean_tbl} shows the mean and standard deviations for the local
-image patches seen in Figure \ref{fig:zoom}.
+image patches seen in Figure \ref{fig:zoom}. Despite qualitative evaluation showing our methods are much sharper,
+quantitatively they show only slight improvement. Other metrics such as entropy are left as future work.
 
@@
    \hline
-   Patch/Method & CycleGAN & UGAN & UGAN-P \\ \hline
+   Patch/Method & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ \hline
    Red    & 11.53 & 9.39 & 10.93  \\ \hline
@@
    \hline
-   Patch/Method & Original & CycleGAN & UGAN & UGAN-P \\ \hline
+   Patch/Method & Original & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ \hline
    Red & 0.43 $\pm$ 0.23 & 0.42 $\pm$ 0.22 & 0.44 $\pm$ 0.23 & 0.45 $\pm$ 0.25 \\ \hline

### 2017-09-16 files/paper/tex/abstract.tex
paper complete, first full draft.

@@
 Autonomous underwater vehicles (AUVs) rely on a variety of sensors -- acoustic, inertial and visual -- for intelligent decision 
-making. Due
-to its non-intrusive, passive nature, and high information content, vision is an attractive sensing modality, particularly at 
-shallower
-depths. However, factors such as light refraction and absorption, suspended particles in the water, and color distortion affect 
-the quality
-of visual data, resulting in noisy and distorted images. AUVs that rely on visual sensing thus face difficult challenges, and 
-consequently
-exhibit poor performance on vision-driven tasks. This paper proposes a method to improve the quality of visual underwater scenes 
-using
-Generative Adversarial Networks (GANs), with the goal of improving input to vision-driven behaviors further down the autonomy
-pipeline. Furthermore, we show how recently proposed methods are able to generate a dataset for the purpose of such underwater 
-image
-reconstruction\starnote{Reconstruction meaning what we are doing here, right? So this is a contribution too, to show how CycleGAN 
-is used to
-generate the dataset, correct?}. For any visually-guided underwater robots, this improvement can result in increased safety and 
-reliability
-through robust visual perception. To that effect, we present quantitative and qualitative data which demonstrates that images 
-corrected
-through the proposed approach generate more visually appealing images, and also provide increased accuracy for an underwater diver 
-tracking
-algorithm.
+making. Due to its non-intrusive, passive nature, and high information content, vision is an attractive sensing modality, 
+particularly at shallower depths. However, factors such as light refraction and absorption, suspended particles in the water, and 
+color distortion affect the quality of visual data, resulting in noisy and distorted images. AUVs that rely on visual sensing thus 
+face difficult challenges, and consequently exhibit poor performance on vision-driven tasks. This paper proposes a method to 
+improve the quality of visual underwater scenes using Generative Adversarial Networks (GANs), with the goal of improving input to 
+vision-driven behaviors further down the autonomy pipeline. Furthermore, we show how recently proposed methods are able to 
+generate a dataset for the purpose of such underwater image restoration\nostarnote{Reconstruction meaning what we are doing here, 
+right? So this is a contribution too, to show how CycleGAN is used to generate the dataset, correct?}. For any visually-guided 
+underwater robots, this improvement can result in increased safety and reliability through robust visual perception. To that 
+effect, we present quantitative and qualitative data which demonstrates that images corrected through the proposed approach 
+generate more visually appealing images, and also provide increased accuracy for an underwater diver tracking algorithm.
 \end{abstract}

### 2017-09-16 files/paper/tex/conclusions.tex
Minor edits.
paper complete, first full draft.

@@
 \section{Conclusion}
+This paper presents an approach for enhancing underwater color images through the use of generative adversarial networks. We 
+demonstrate the use of CycleGAN to generate dataset of paired images to provide a training set for the proposed restoration 
+model. Quantitative and qualitative results demonstrate the effectiveness of this method, and using a diver tracking algorithm on 
+corrected images of scuba divers show higher accuracy compared to the uncorrected image sequence.
 
-Future work: Getting a better and larger dataset. I think that would help a great deal. Also data augmentation
-after CycleGAN, such as gaussian blurring, noise, particle effect, more lighting effects etc.
+Future work will focus on creating a larger and more diverse dataset from underwater objects, thus making the network more 
+generalizable. Augmenting the data generated by CycleGAN with noise such as particle and lighting effects would improve 
+the diversity of the dataset. We also intend to investigate a number of different quantitative performance metrics to evaluate 
+our method.
 
 \section*{Acknowledgment}
-Anyone we wish to acknowledge?
+The authors are grateful to Oliver Hennigh for his implementation of the Gradient Difference Loss measure.

### 2017-09-16 files/paper/tex/experiments.tex
paper complete, first full draft.

@@
 We used several subsets of Imagenet~\cite{deng2009imagenet} for training and evaluation of our methods. We also evaluate a 
-tracking
-algorithm on a video of scuba divers taken from Youtube \footnote{https://www.youtube.com/watch?v=QmRFmhILd5o}. Subsets of 
+frequency- and spatial-domain diver-tracking algorithm on a video of scuba divers taken from YouTube\texttrademark\ 
+\footnote{https://www.youtube.com/watch?v=QmRFmhILd5o}. Subsets of 
 Imagenet
@@
 
-\begin{figure}
+\begin{figure}[th]
 \centering
-\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm}}
+\begin{tabular}{p{1.7cm} p{1.7cm} p{1.75cm}}
 
@@
 \end{tabular}
-\caption{Samples from our Imagenet testing set. The network can both recover color and also correct color if a small amount is 
+\caption{Samples from our ImageNet testing set. The network can both recover color and also correct color if a small amount is 
 present.}
@@
 
-\subsection{Training and Inference Performance}
-In all of our experiments, we use $\lambda_{1} = 100$, $\lambda_{GP} = 10$, batch size of 32, and the Adam Optimizer 
-\cite{kingma2014adam} with learning rate $1e-4$. Following WGAN-GP, the discriminator is updated $n$ times for every update of the 
-generator, where $n = 5$. For UGAN-P, we set $\lambda_{2} = 1.0$ and $\alpha = 1$. Our implementation was done using the 
-Tensorflow library \cite{abadi2016tensorflow}. \footnote{Code is available at 
-\url{https://github.com/cameronfabbri/Underwater-Color-Correction}} All networks were trained from scratch on a GTX 1080 for 100 
-epochs. Inference on the GPU takes on average $ 0.0138s$, which is about 72 Frames Per Second (FPS). On a CPU (Intel Core 
-i7-5930K), inference takes on average $ 0.1244s$, which is about 8 FPS. We find both of these measures acceptable for underwater 
-tasks.
+\subsection{Comparison to CycleGAN}
+It is important to note that during the process of learning a mapping $F: X \rightarrow Y$, CycleGAN also learns a mapping $G: Y 
+\rightarrow X$. Here we give a comparison to our methods. We use the Canny edge detector \cite{canny1986computational} to provide 
+a color agnostic evaluation of the images, as the original contain distorted colors and cannot be compared back to as ground 
+truth. Due to the fact that restoring color information should not alter the overall structure of the image, we measure the 
+distance in the image space between the edges found in the original and generated images. Figure ~\ref{fig:canny_samples} shows 
+the original images and results from edge detection. Table~\ref{tab:one} provides the measurements from Figure 
+~\ref{fig:canny_samples}, as well as the average over our entire Flickr\texttrademark\ dataset. Both UGAN and UGAN-P are 
+consistently closer in the image space to the original than that of CycleGAN, suggesting noise due to blur. Next, we evaluate this 
+noise explicitly.
 
-\subsection{Comparison to CycleGAN}
-It is important to note that during the process of learning a mapping $F: X \rightarrow Y$, CycleGAN also learns a
-mapping $G: Y \rightarrow X$. Here we give a comparison to our methods. We use the Canny edge
-detector \cite{canny1986computational} to provide a color agnostic evaluation of the images, as the original contain
-distorted colors and cannot be compared back to as ground truth. Due to the fact that restoring color information
-should not alter the overall structure of the image, we measure the distance in the image space between the edges
-found in the original and generated images. Figure ~\ref{fig:canny_samples} shows the original images and results from
-edge detection. Table 1 provides the measurements from Figure ~\ref{fig:canny_samples}, as well as the average over our
-entire Flickr\texttrademark ~dataset. Both UGAN and UGAN-P are consistently closer in the image space to the original
-than that of CycleGAN, suggesting noise due to blur. Next, we evaluate this noise explicitly.
+We explore the artifacts of content loss, as seen in Figure ~\ref{fig:zoom}. In particular, we compare local statistics of the 
+highlighted image patches, where each image patch is resized to $64 \times 64$. We use the GDL \cite{mathieu2015deep} from 
+(\ref{gdl_eq}) as a sharpness measure. A lower GDL measure implies a smoother transition between pixels, as a noisy image would 
+have large jumps in the image's gradient, leading to a higher score.\nostarnote{I THINK. I would double check, bottom of page 4: 
+https://arxiv.org/pdf/1511.05440.pdf.} As seen in Table \ref{fig:gdl_tbl}, the GDL is lower for both UGAN and UGAN-P. 
+Interestingly, UGAN consistently has a lower score than UGAN-P, despite UGAN-P explicitly accounting for this metric in the 
+objective function. Reasoning for this is left for our future work.
 
-We explore the artifacts of content loss, as seen in Figure ~\ref{fig:zoom}. In particular, we compare local statistics
-of the highlighted image patches, where each image patch is resized to $64 \times 64$. We use the GDL
-\cite{mathieu2015deep} from (\ref{gdl_eq}) as a sharpness measure. A lower GDL measure implies a smoother transition
-between pixels, as a noisy image would have large jumps in the image's gradient, leading to a higher score.
-\starnote{I THINK.
-I would double check, bottom of page 4: https://arxiv.org/pdf/1511.05440.pdf}.
-As seen in Table \ref{fig:gdl_tbl}, the GDL is lower for both UGAN and UGAN-P. Interestingly, UGAN consistently has a
-lower score than UGAN-P, despite UGAN-P explicitly accounting for this metric in the objective function. Reasoning for
-this is left for our future work.
-
-Another metric we can use to compare image patches are the mean and standard deviation of a patch. The standard
-deviation gives us a sense of blurriness because it defines how far the data deviates from the mean. A lower standard
-deviation means that the data is closer to the mean \starnote{not sure if we exactly need to say that because I assume the reviewers will know what it is}.
-In the case of images, this would suggest a blurring effect due to the data being
-more clustered toward one pixel value. Table \ref{fig:mean_tbl} shows the mean and standard deviations for the local
-image patches seen in Figure \ref{fig:zoom}. Despite qualitative evaluation showing our methods are much sharper,
-quantitatively they show only slight improvement. Other metrics such as entropy are left as future work.
+Another metric we use to compare image patches are the mean and standard deviation of a patch. The standard deviation gives us a 
+sense of blurriness because it defines how far the data deviates from the mean.\nostarnote{ A lower standard deviation means that 
+the data is closer to the mean . not sure if we exactly need to say that because I assume the reviewers will know what it is.} In 
+the case of images, this would suggest a blurring effect due to the data being more clustered toward one pixel value. Table 
+\ref{fig:mean_tbl} shows the mean and standard deviations of the RGB values for the local image patches seen in Figure 
+\ref{fig:zoom}. Despite qualitative evaluation showing our methods are much sharper, quantitatively they show only slight 
+improvement. Other metrics such as entropy are left as future work.
 
@@
 \end{tabular}
+\label{tab:one}
 \end{table}
@@
 
-\begin{figure}
+% \begin{figure*}[h]
+% \centering
+% \begin{tabular}{p{.4cm} p{1.7cm} p{1.7cm} p{1.7cm} p{1.7cm}}
+%   
+%    Set & ~\quad Original & ~CycleGAN & ~\quad \textbf{UGAN} & \quad \textbf{UGAN-P} \\
+% 
+%    \multirow{2}{*}{A} & \includegraphics[width=0.8in]{1_original} &
+%    \includegraphics[width=0.8in]{1_cimg} &
+%    \includegraphics[width=0.8in]{1_u0img} &
+%    \includegraphics[width=0.8in]{1_u1img} \\ [-1ex]
+%    \includegraphics[width=0.8in]{1_oedges} &
+%    \includegraphics[width=0.8in]{1_cedges} &
+%    \includegraphics[width=0.8in]{1_u0edges} &
+%    \includegraphics[width=0.8in]{1_u1edges} \\
+% 
+%    \multirow{2}{*}{B} & \includegraphics[width=0.8in]{2_original} &
+%    \includegraphics[width=0.8in]{2_cimg} &
+%    \includegraphics[width=0.8in]{2_u0img} &
+%    \includegraphics[width=0.8in]{2_u1img} \\ [-1ex]
+%    \includegraphics[width=0.8in]{2_oedges} &
+%    \includegraphics[width=0.8in]{2_cedges} &
+%    \includegraphics[width=0.8in]{2_u0edges} &
+%    \includegraphics[width=0.8in]{2_u1edges} \\
+% 
+%    \multirow{2}{*}{C} & \includegraphics[width=0.8in]{3_original} &
+%    \includegraphics[width=0.8in]{3_cimg} &
+%    \includegraphics[width=0.8in]{3_u0img} &
+%    \includegraphics[width=0.8in]{3_u1img} \\ [-1ex]
+%    \includegraphics[width=0.8in]{3_oedges} &
+%    \includegraphics[width=0.8in]{3_cedges} &
+%    \includegraphics[width=0.8in]{3_u0edges} &
+%    \includegraphics[width=0.8in]{3_u1edges} \\
+%    
+%    \multirow{2}{*}{D} & \includegraphics[width=0.8in]{4_original} &
+%    \includegraphics[width=0.8in]{4_cimg} &
+%    \includegraphics[width=0.8in]{4_u0img} &
+%    \includegraphics[width=0.8in]{4_u1img} \\ [-1ex]
+%    \includegraphics[width=0.8in]{4_oedges} &
+%    \includegraphics[width=0.8in]{4_cedges} &
+%    \includegraphics[width=0.8in]{4_u0edges} &
+%    \includegraphics[width=0.8in]{4_u1edges} \\
+% 
+% \end{tabular}
+% \caption{Running the Canny Edge Detector on sample images. Both variants of UGAN contain less noise than CycleGAN,
+% and are closer in the image space to the original. For each pair, the top row is the input image, and bottom row
+% the result of the edge detector.}
+% \label{fig:canny_samples}
+% \end{figure*}
+
+\begin{figure}[h]
 \centering
-\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.7cm}}
+\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.75cm}}
 
@@
 and are closer in the image space to the original. For each pair, the top row is the input image, and bottom row
-the result of the edge detector.}
+the result of the edge detector. The figure depicts four different sets of images, successively labeled A to D from top to 
+bottom. See Table~\ref{tab:one}.}
 \label{fig:canny_samples}
+\vspace{-5mm}
 \end{figure}
@@
    \hline
-   Patch/Method & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ \hline
+   \multicolumn{1}{|p{.7cm}|}{\centering Method/ \\ Patch} & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ \hline
    Red    & 11.53 & 9.39 & 10.93  \\ \hline
@@
    \hline
-   Patch/Method & Original & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ \hline
+   \multicolumn{1}{|p{.7cm}|}{\centering Method/ \\ Patch} & Original & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ 
+\hline
    Red & 0.43 $\pm$ 0.23 & 0.42 $\pm$ 0.22 & 0.44 $\pm$ 0.23 & 0.45 $\pm$ 0.25 \\ \hline
@@
 
+\subsection{Training and Inference Performance}
+In all of our experiments, we use $\lambda_{1} = 100$, $\lambda_{GP} = 10$, batch size of 32, and the Adam Optimizer 
+\cite{kingma2014adam} with learning rate $1e-4$. Following WGAN-GP, the discriminator is updated $n$ times for every update of the 
+generator, where $n = 5$. For UGAN-P, we set $\lambda_{2} = 1.0$ and $\alpha = 1$. Our implementation was done using the 
+Tensorflow library \cite{abadi2016tensorflow}. \footnote{Code is available at 
+\url{https://github.com/cameronfabbri/Underwater-Color-Correction}} All networks were trained from scratch on a GTX 1080 for 100 
+epochs. Inference on the GPU takes on average $ 0.0138s$, which is about 72 Frames Per Second (FPS). On a CPU (Intel Core 
+i7-5930K), inference takes on average $ 0.1244s$, which is about 8 FPS. In both cases, the input images have dimensions 
+$256\times 256\times 3$. We find both of these measures acceptable for underwater tasks.
+
 %Flippers of a human diver typically oscillate at frequencies between $1$ and $2$ Hz, which produces periodic intensity variations 
-in the image-space over time. These variations correspond to distinct signatures in the frequency-domain (high-amplitude spectra 
-at $1$-$2$Hz), which can be used for reliable detection.
+% in the image-space over time. These variations correspond to distinct signatures in the frequency-domain (high-amplitude spectra 
+% at $1$-$2$Hz), which can be used for reliable detection.

### 2017-09-16 files/paper/tex/introduction.tex
Minor edits.
paper complete, first full draft.

@@
 %TODO - talk about having to go back to the same location if you want to get good/bad pairs of the ``same'' image.\starnote{I 
-assume Cam will
-%do this?}
+%assume Cam will %do this?}
 Underwater robotics has been a steadily growing subfield of autonomous field robotics, assisted by the advent of novel platforms,
@@
 As color and illumination begin to change with the depth, vision-based algorithms must need to be very generalizable in order to 
-work within
-the depth ranges a robot may operate in. Because of the high cost and difficulty of acquiring a variety of underwater data to 
-train a visual
-system on, as well as the high amount of noise introduced, algorithms may (and do) perform poorly in these different
-domains. Figure~\ref{fig:samples} shows the high variability in visual scenes that may occur in
-underwater environments. A step towards a solution to this issue is to be able to restore the images such that they appear to be 
-above
-water, \emph{i.e.}, with colors corrected and suspended particles removed from the scene. By performing a many-to-one mapping of 
-these
-domains from underwater to not underwater (what the image would look like above water), algorithms that have difficulty performing 
-across
+work within the depth ranges a robot may operate in. Because of the high cost and difficulty of acquiring a variety of underwater 
+data to train a visual system on, as well as the high amount of noise introduced, algorithms may (and do) perform poorly in these 
+different domains. Figure~\ref{fig:samples} shows the high variability in visual scenes that may occur in underwater environments. 
+A step towards a solution to this issue is to be able to restore the images such that they appear to be above water, \emph{i.e.}, 
+with colors corrected and suspended particles removed from the scene. By performing a many-to-one mapping of these domains from 
+underwater to not underwater (what the image would look like above water), algorithms that have difficulty performing across 
 multiple forms of noise may be able to focus only one clean domain.
@@
 \begin{figure}
+\vspace{2mm}
 \centering
@@
    \includegraphics[width=0.8in]{n02607072_10395_f1} \\
-
 \end{tabular}
@@
 color varies between the different images.}
+\vspace{-5mm}
 \end{figure}
@@
 domain $X$ to another arbitrary domain $Y$ \textit{without} image pairs, as a way to generate a paired dataset.
-By letting $X$ be a set of undistorted underwater images\starnote{need to say where we find the undistorted ones}, and
+By letting $X$ be a set of undistorted underwater images\nostarnote{need to say where we find the undistorted ones}, and
 $Y$ be a set of distorted underwater images, we can generate an image that appears to be underwater while retaining

### 2017-09-16 files/paper/tex/methodology.tex
Editing stuff for final version.
paper complete, first full draft.

@@
 \subsection{Adversarial Networks}
+\label{sec:gans}
 \nostarnote{check this paragraph as I added some more text}In machine learning literature, Generative Adversarial Networks 
@@
 \label{fig:cgan_samples}
+\vspace{-5mm}
 \end{figure}
@@
 the discriminator improves, the gradient of the generator vanishes, making it difficult or impossible to train. Mode
-collapse occurs when the generator ``collapses'' onto a single point, fooling the discriminator with only one instance
-\starnote{Such as when you are training a GAN to generate digits from MNIST, but it only generates a 7, when in reality
-you'd want it to generate a diverse amount of all the digits. Not sure if we should expand more.}.
+collapse occurs when the generator ``collapses'' onto a single point, fooling the discriminator with only one instance.
+To illustrate the effect of mode collapse, imagine a GAN is being used to generate digits from the MNIST~\cite{lecun2010mnist} 
+dataset, but it only generated the same digit. In reality, the desired outcome would be to generate a diverse collection of all 
+the digits.
 There have been a number of recent methods which hypothesize a different loss function for the discriminator

### 2017-09-16 files/paper/tex/related.tex
paper complete, first full draft.

@@
 (GANs) as our generative model (see Section~\ref{sec:gans} for details). Much like the work of \cite{isola2016image}, we 
-use image pairs from two domains as input and ground truth. \starnote{Somewhere I think we should mention that unpaired image to 
+use image pairs from two domains as input and ground truth. \nostarnote{Somewhere I think we should mention that unpaired image 
+to 
 image translation is more difficult, and that CycleGAN is a good way to generate a dataset in such a way to do this with image 

### 2017-09-16 files/paper/tex/abstract.tex
removed underwater from the abstract's last line.

@@
 vision-driven behaviors further down the autonomy pipeline. Furthermore, we show how recently proposed methods are able to 
-generate a dataset for the purpose of such underwater image restoration\nostarnote{Reconstruction meaning what we are doing here, 
-right? So this is a contribution too, to show how CycleGAN is used to generate the dataset, correct?}. For any visually-guided 
-underwater robots, this improvement can result in increased safety and reliability through robust visual perception. To that 
-effect, we present quantitative and qualitative data which demonstrates that images corrected through the proposed approach 
-generate more visually appealing images, and also provide increased accuracy for an underwater diver tracking algorithm.
+generate a dataset for the purpose of such underwater image restoration. For any visually-guided underwater robots, this 
+improvement can result in increased safety and reliability through robust visual perception. To that effect, we present 
+quantitative and qualitative data which demonstrates that images corrected through the proposed approach generate more visually 
+appealing images, and also provide increased accuracy for a diver tracking algorithm.
 \end{abstract}
+
+\nostarnote{Reconstruction meaning what we are doing here, 
+right? So this is a contribution too, to show how CycleGAN is used to generate the dataset, correct?}

### 2017-09-16 files/paper/tex/experiments.tex
Final submitted version.

@@
 \end{tabular}
-\caption{Comparison of local image patches. Each patch was resized to $64 \times 64$.}
+\caption{Local image patches extracted for quantitative comparisons, shown in Tables~\ref{fig:gdl_tbl} and~\ref{fig:mean_tbl}. 
+Each patch was resized to $64 \times 64$, but shown enlarged for viewing ability.}
 \label{fig:zoom}
@@
 visibility. The generated images seem to restore these eroded intensity variations to some extent, causing much improved positive 
-detection for MDPM tracker.
+detection (a 350\% increase in correct detections) for the MDPM tracker.
 

### 2017-09-16 files/paper/tex/introduction.tex
Final submitted version.

@@
 sensors and propulsion mechanisms. While autonomous underwater vehicles are often equipped with a variety of sensors, visual 
-sensing is an
-attractive option because of its non-intrusive, passive, and energy efficient nature. The monitoring of coral reefs 
-\cite{shkurti2012multi},
-deep ocean exploration \cite{whitcomb2000advances}, and mapping of the seabed~\cite{bingham2010robotic} are a number of tasks 
-where
-visually-guided AUVs and ROVs (Remotely Operated Vehicles) have seen widespread use. Use of these robots ensures humans are not 
-exposed to
-the hazards of underwater exploration, as they no longer need to venture to the depths (which was how such tasks were carried out 
-in the
-past). Despite the advantages of using vision, underwater environments pose unique challenges to visual sensing, as phenomena such 
-as light
-refraction, absorption and scattering from suspended particles can greatly affect the optics of light. As an example, because red
-wavelengths are quickly absorbed by water, images tend to have a green or blue hue to them. As one goes deeper, this effect 
-worsens, as more
-and more red hue is absorbed. This distortion is extremely non-linear in nature, and is affected by a large number of factors, 
-such as the
-amount of light present (overcast versus sunny, operational depth), amount of particles in the water, time of day, and the camera 
-being
-used. This may cause difficulty in tasks such as segmentation, tracking, or classification due to their indirect or direct use of 
-color.
+sensing is an attractive option because of its non-intrusive, passive, and energy efficient nature. The monitoring of coral reefs 
+\cite{shkurti2012multi}, deep ocean exploration \cite{whitcomb2000advances}, and mapping of the seabed~\cite{bingham2010robotic} 
+are a number of tasks where visually-guided AUVs and ROVs (Remotely Operated Vehicles) have seen widespread use. Use of these 
+robots ensures humans are not exposed to the hazards of underwater exploration, as they no longer need to venture to the depths 
+(which was how such tasks were carried out in the past). Despite the advantages of using vision, underwater environments pose 
+unique challenges to visual sensing, as light refraction, absorption and scattering from suspended particles can greatly affect 
+optics. For example, because red wavelengths are quickly absorbed by water, images tend to have a green or blue hue to them. As 
+one goes deeper, this effect worsens, as more and more red hue is absorbed. This distortion is extremely non-linear in nature, and 
+is affected by a large number of factors, such as the amount of light present (overcast versus sunny, operational depth), amount 
+of particles in the water, time of day, and the camera being used. This may cause difficulty in tasks such as segmentation, 
+tracking, or classification due to their indirect or direct use of color.
 
-As color and illumination begin to change with the depth, vision-based algorithms must need to be very generalizable in order to 
-work within the depth ranges a robot may operate in. Because of the high cost and difficulty of acquiring a variety of underwater 
-data to train a visual system on, as well as the high amount of noise introduced, algorithms may (and do) perform poorly in these 
+As color and illumination begin to change with depth, vision-based algorithms need to be generalizable in order to work within 
+the depth ranges a robot may operate in. Because of the high cost and difficulty of acquiring a variety of underwater data to 
+train a visual system on, as well as the high amount of noise introduced, algorithms may (and do) perform poorly in these 
 different domains. Figure~\ref{fig:samples} shows the high variability in visual scenes that may occur in underwater environments. 
@@
 \caption{Sample underwater images with natural and man-made artifacts (which in this case is our underwater robot) displaying the 
-diversity of distortion that can occur. With the varying camera-to-object distances in the images, the distortion and loss of 
+diversity of distortions that can occur. With the varying camera-to-object distances in the images, the distortion and loss of 
 color varies between the different images.}

### 2017-09-16 files/paper/tex/methodology.tex
Final submitted version.

@@
 \label{sec:methodology}
-Underwater images distorted by color or circumstance lack ground truth, which is a necessity for previous colorization
+Underwater images distorted by color or other circumstances lack ground truth, which is a necessity for previous colorization
 approaches. Furthermore, the distortion present in an underwater image is highly nonlinear; simple methods such as
@@
 \rightarrow Y$. Figure~\ref{fig:cgan_samples} shows paired samples generated from CycleGAN. From this paired dataset we train a 
-generator $G$ to learn the function $f: I^D \rightarrow I^C$. It should be noted that during our data generation process, CycleGAN 
-simultaneously learns a mapping $G: Y \rightarrow X$, which is similar to $f$. In Section~\ref{sec:experiments}, we compare images 
-generated by CycleGAN with images generated through our approach.
+generator $G$ to learn the function $f: I^D \rightarrow I^C$. It should be noted that during the training process of CycleGAN, 
+it simultaneously learns a mapping $G: Y \rightarrow X$, which is similar to $f$. In Section~\ref{sec:experiments}, we compare 
+images generated by CycleGAN with images generated through our approach.
 
@@
 (GANs)~\cite{goodfellow2014generative} represent a class of generative models based on game theory in which a generator network 
-competes against an adversary. From a classification perspective, the generator network produces instances which actively attempt 
-to `fool' the discriminator network. The goal is for the discriminator network to be able to distinguish between `true' 
+competes against an adversary. From a classification perspective, the generator network $G$ produces instances which actively 
+attempt 
+to `fool' the discriminator network $D$. The goal is for the discriminator network to be able to distinguish between `true' 
 instances coming from the dataset and `false' instances produced by the generator network.
@@
 
-Note for simplicity in notation, we will further omit $I^C \sim p_{train}$ and $I^D \sim p_{gen}$. In this formulation, 
+Note for simplicity in notation, we will further omit $I^C \sim p_{train}(I^C)$ and $I^D \sim p_{gen}(I^D)$. In this formulation, 
 the discriminator is hypothesized as a classifier with a sigmoid cross-entropy loss function, which in practice may lead
@@
 dataset, but it only generated the same digit. In reality, the desired outcome would be to generate a diverse collection of all 
-the digits.
-There have been a number of recent methods which hypothesize a different loss function for the discriminator
+the digits. To this end, there have been a number of recent methods which hypothesize a different loss function for the 
+discriminator
 \cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}. We focus on the Wasserstein GAN
@@
 directly penalizing the differences of image gradient predictions in the generator, as proposed by
-\cite{mathieu2015deep}. Given a ground truth image $I^C$, predicted image $I^P = G(I^D)$, and $\alpha \geq 1$, the
-Gradient Difference Loss (GDL) is given by
+\cite{mathieu2015deep}. Given a ground truth image $I^C$, predicted image $I^P = G(I^D)$, and $\alpha$ which is an integer 
+greater than or equal to 1, the Gradient Difference Loss (GDL) is given by
 

### 2017-09-25 files/paper/tex_plain_version/experiments.tex
plain version added

--- 2017-09-16 files/paper/tex/experiments.tex
@@
 
-\begin{figure}[th]
+\begin{figure}[!ht]
 \centering
-\begin{tabular}{p{1.7cm} p{1.7cm} p{1.75cm}}
+\footnotesize
+\begin{tabular}{p{1.6cm} p{1.6cm} p{1.6cm}}
+   Original & \textbf{UGAN} & \textbf{UGAN-P} \\
+   \includegraphics[width=0.7in]{n01917289_4982_real} &
+   \includegraphics[width=0.7in]{n01917289_4982_gen_0} &
+   \includegraphics[width=0.7in]{n01917289_4982_gen_1} \\
 
-   ~\quad Original & ~\quad \textbf{UGAN} & \quad \textbf{UGAN-P} \\
+   \includegraphics[width=0.7in]{n01496331_16340_real} &
+   \includegraphics[width=0.7in]{n01496331_16340_gen_0} &
+   \includegraphics[width=0.7in]{n01496331_16340_gen_1} \\
 
-   \includegraphics[width=0.8in]{n01917289_4982_real} &
-   \includegraphics[width=0.8in]{n01917289_4982_gen_0} &
-   \includegraphics[width=0.8in]{n01917289_4982_gen_1} \\
+   \includegraphics[width=0.7in]{n01496331_22183_real} &
+   \includegraphics[width=0.7in]{n01496331_22183_gen_0} &
+   \includegraphics[width=0.7in]{n01496331_22183_gen_1} \\
 
-   \includegraphics[width=0.8in]{n01496331_16340_real} &
-   \includegraphics[width=0.8in]{n01496331_16340_gen_0} &
-   \includegraphics[width=0.8in]{n01496331_16340_gen_1} \\
+   \includegraphics[width=0.7in]{n01664065_29738_real} &
+   \includegraphics[width=0.7in]{n01664065_29738_gen_0} &
+   \includegraphics[width=0.7in]{n01664065_29738_gen_1} \\
 
-   \includegraphics[width=0.8in]{n01496331_22183_real} &
-   \includegraphics[width=0.8in]{n01496331_22183_gen_0} &
-   \includegraphics[width=0.8in]{n01496331_22183_gen_1} \\
+   \includegraphics[width=0.7in]{n01496331_11938_real} &
+   \includegraphics[width=0.7in]{n01496331_11938_gen_0} &
+   \includegraphics[width=0.7in]{n01496331_11938_gen_1} \\
 
-   \includegraphics[width=0.8in]{n01664065_29738_real} &
-   \includegraphics[width=0.8in]{n01664065_29738_gen_0} &
-   \includegraphics[width=0.8in]{n01664065_29738_gen_1} \\
+   \includegraphics[width=0.7in]{n02606052_2969_real} &
+   \includegraphics[width=0.7in]{n02606052_2969_gen_0} &
+   \includegraphics[width=0.7in]{n02606052_2969_gen_1} \\
 
-   \includegraphics[width=0.8in]{n01496331_11938_real} &
-   \includegraphics[width=0.8in]{n01496331_11938_gen_0} &
-   \includegraphics[width=0.8in]{n01496331_11938_gen_1} \\
+   \includegraphics[width=0.7in]{n01914609_1607_real} &
+   \includegraphics[width=0.7in]{n01914609_1607_gen_0} &
+   \includegraphics[width=0.7in]{n01914609_1607_gen_1} \\
 
-   \includegraphics[width=0.8in]{n02606052_2969_real} &
-   \includegraphics[width=0.8in]{n02606052_2969_gen_0} &
-   \includegraphics[width=0.8in]{n02606052_2969_gen_1} \\
-
-   \includegraphics[width=0.8in]{n01914609_1607_real} &
-   \includegraphics[width=0.8in]{n01914609_1607_gen_0} &
-   \includegraphics[width=0.8in]{n01914609_1607_gen_1} \\
-
-   \includegraphics[width=0.8in]{n02607072_6241_real} &
-   \includegraphics[width=0.8in]{n02607072_6241_gen_0} &
-   \includegraphics[width=0.8in]{n02607072_6241_gen_1} \\
+   \includegraphics[width=0.7in]{n02607072_6241_real} &
+   \includegraphics[width=0.7in]{n02607072_6241_gen_0} &
+   \includegraphics[width=0.7in]{n02607072_6241_gen_1} \\
 
@@
 \centering
+\footnotesize
 \caption{Distances in image space}
@@
 
-%\newpage
+\begin{figure}[!ht]
+\centering
+\footnotesize
+\begin{tabular}{p{1.6cm} p{1.6cm} p{1.6cm} p{1.6cm}}
+   Original & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\
+   \includegraphics[width=0.7in]{1_original} &
+   \includegraphics[width=0.7in]{1_cimg} &
+   \includegraphics[width=0.7in]{1_u0img} &
+   \includegraphics[width=0.7in]{1_u1img} \\ [-1ex]
+   \includegraphics[width=0.7in]{1_oedges} &
+   \includegraphics[width=0.7in]{1_cedges} &
+   \includegraphics[width=0.7in]{1_u0edges} &
+   \includegraphics[width=0.7in]{1_u1edges} \\
 
-% \begin{figure*}[h]
-% \centering
-% \begin{tabular}{p{.4cm} p{1.7cm} p{1.7cm} p{1.7cm} p{1.7cm}}
-%   
-%    Set & ~\quad Original & ~CycleGAN & ~\quad \textbf{UGAN} & \quad \textbf{UGAN-P} \\
-% 
-%    \multirow{2}{*}{A} & \includegraphics[width=0.8in]{1_original} &
-%    \includegraphics[width=0.8in]{1_cimg} &
-%    \includegraphics[width=0.8in]{1_u0img} &
-%    \includegraphics[width=0.8in]{1_u1img} \\ [-1ex]
-%    \includegraphics[width=0.8in]{1_oedges} &
-%    \includegraphics[width=0.8in]{1_cedges} &
-%    \includegraphics[width=0.8in]{1_u0edges} &
-%    \includegraphics[width=0.8in]{1_u1edges} \\
-% 
-%    \multirow{2}{*}{B} & \includegraphics[width=0.8in]{2_original} &
-%    \includegraphics[width=0.8in]{2_cimg} &
-%    \includegraphics[width=0.8in]{2_u0img} &
-%    \includegraphics[width=0.8in]{2_u1img} \\ [-1ex]
-%    \includegraphics[width=0.8in]{2_oedges} &
-%    \includegraphics[width=0.8in]{2_cedges} &
-%    \includegraphics[width=0.8in]{2_u0edges} &
-%    \includegraphics[width=0.8in]{2_u1edges} \\
-% 
-%    \multirow{2}{*}{C} & \includegraphics[width=0.8in]{3_original} &
-%    \includegraphics[width=0.8in]{3_cimg} &
-%    \includegraphics[width=0.8in]{3_u0img} &
-%    \includegraphics[width=0.8in]{3_u1img} \\ [-1ex]
-%    \includegraphics[width=0.8in]{3_oedges} &
-%    \includegraphics[width=0.8in]{3_cedges} &
-%    \includegraphics[width=0.8in]{3_u0edges} &
-%    \includegraphics[width=0.8in]{3_u1edges} \\
-%    
-%    \multirow{2}{*}{D} & \includegraphics[width=0.8in]{4_original} &
-%    \includegraphics[width=0.8in]{4_cimg} &
-%    \includegraphics[width=0.8in]{4_u0img} &
-%    \includegraphics[width=0.8in]{4_u1img} \\ [-1ex]
-%    \includegraphics[width=0.8in]{4_oedges} &
-%    \includegraphics[width=0.8in]{4_cedges} &
-%    \includegraphics[width=0.8in]{4_u0edges} &
-%    \includegraphics[width=0.8in]{4_u1edges} \\
-% 
-% \end{tabular}
-% \caption{Running the Canny Edge Detector on sample images. Both variants of UGAN contain less noise than CycleGAN,
-% and are closer in the image space to the original. For each pair, the top row is the input image, and bottom row
-% the result of the edge detector.}
-% \label{fig:canny_samples}
-% \end{figure*}
+   \includegraphics[width=0.7in]{2_original} &
+   \includegraphics[width=0.7in]{2_cimg} &
+   \includegraphics[width=0.7in]{2_u0img} &
+   \includegraphics[width=0.7in]{2_u1img} \\ [-1ex]
+   \includegraphics[width=0.7in]{2_oedges} &
+   \includegraphics[width=0.7in]{2_cedges} &
+   \includegraphics[width=0.7in]{2_u0edges} &
+   \includegraphics[width=0.7in]{2_u1edges} \\
 
-\begin{figure}[h]
-\centering
-\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.75cm}}
+   \includegraphics[width=0.7in]{3_original} &
+   \includegraphics[width=0.7in]{3_cimg} &
+   \includegraphics[width=0.7in]{3_u0img} &
+   \includegraphics[width=0.7in]{3_u1img} \\ [-1ex]
+   \includegraphics[width=0.7in]{3_oedges} &
+   \includegraphics[width=0.7in]{3_cedges} &
+   \includegraphics[width=0.7in]{3_u0edges} &
+   \includegraphics[width=0.7in]{3_u1edges} \\
 
-   ~\quad Original & ~CycleGAN & ~\quad \textbf{UGAN} & \quad \textbf{UGAN-P} \\
-
-   \includegraphics[width=0.8in]{1_original} &
-   \includegraphics[width=0.8in]{1_cimg} &
-   \includegraphics[width=0.8in]{1_u0img} &
-   \includegraphics[width=0.8in]{1_u1img} \\ [-1ex]
-   \includegraphics[width=0.8in]{1_oedges} &
-   \includegraphics[width=0.8in]{1_cedges} &
-   \includegraphics[width=0.8in]{1_u0edges} &
-   \includegraphics[width=0.8in]{1_u1edges} \\
-
-   \includegraphics[width=0.8in]{2_original} &
-   \includegraphics[width=0.8in]{2_cimg} &
-   \includegraphics[width=0.8in]{2_u0img} &
-   \includegraphics[width=0.8in]{2_u1img} \\ [-1ex]
-   \includegraphics[width=0.8in]{2_oedges} &
-   \includegraphics[width=0.8in]{2_cedges} &
-   \includegraphics[width=0.8in]{2_u0edges} &
-   \includegraphics[width=0.8in]{2_u1edges} \\
-
-   \includegraphics[width=0.8in]{3_original} &
-   \includegraphics[width=0.8in]{3_cimg} &
-   \includegraphics[width=0.8in]{3_u0img} &
-   \includegraphics[width=0.8in]{3_u1img} \\ [-1ex]
-   \includegraphics[width=0.8in]{3_oedges} &
-   \includegraphics[width=0.8in]{3_cedges} &
-   \includegraphics[width=0.8in]{3_u0edges} &
-   \includegraphics[width=0.8in]{3_u1edges} \\
-
-   \includegraphics[width=0.8in]{4_original} &
-   \includegraphics[width=0.8in]{4_cimg} &
-   \includegraphics[width=0.8in]{4_u0img} &
-   \includegraphics[width=0.8in]{4_u1img} \\ [-1ex]
-   \includegraphics[width=0.8in]{4_oedges} &
-   \includegraphics[width=0.8in]{4_cedges} &
-   \includegraphics[width=0.8in]{4_u0edges} &
-   \includegraphics[width=0.8in]{4_u1edges} \\
-
+   \includegraphics[width=0.7in]{4_original} &
+   \includegraphics[width=0.7in]{4_cimg} &
+   \includegraphics[width=0.7in]{4_u0img} &
+   \includegraphics[width=0.7in]{4_u1img} \\ [-1ex]
+   \includegraphics[width=0.7in]{4_oedges} &
+   \includegraphics[width=0.7in]{4_cedges} &
+   \includegraphics[width=0.7in]{4_u0edges} &
+   \includegraphics[width=0.7in]{4_u1edges} \\
 \end{tabular}
-\caption{Running the Canny Edge Detector on sample images. Both variants of UGAN contain less noise than CycleGAN,
+\vspace{-2mm}
+\caption{\small{Running the Canny Edge Detector on sample images. Both variants of UGAN contain less noise than CycleGAN,
 and are closer in the image space to the original. For each pair, the top row is the input image, and bottom row
 the result of the edge detector. The figure depicts four different sets of images, successively labeled A to D from top to 
-bottom. See Table~\ref{tab:one}.}
+bottom. See Table~\ref{tab:one}.}}
 \label{fig:canny_samples}
@@
 % TODO definitely need help with formatting, but content is there
-\begin{figure*}
+\begin{figure*}[!ht]
 \centering
@@
 
-\begin{figure*}
+\begin{figure*}[!ht]
 \begin{tabular}{p{1.8cm} p{1.85cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.9cm} }
@@
    \hline
-   \multicolumn{1}{|p{.7cm}|}{\centering Method/ \\ Patch} & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ \hline
+   Method/Patch & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ \hline
    Red    & 11.53 & 9.39 & 10.93  \\ \hline
@@
 
-\begin{table}[ht]
-\footnotesize
+\begin{table*}[ht]
 \centering
@@
    \hline
-   \multicolumn{1}{|p{.7cm}|}{\centering Method/ \\ Patch} & Original & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ 
+   Method/Patch & Original & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ 
 \hline
@@
 \label{fig:mean_tbl}
-\end{table}
+\end{table*}
 

### 2017-09-28 files/paper/PlainPaper.tex
plain version added
update

--- 2017-09-15 files/paper/paper.tex
@@
-\documentclass[letterpaper, 10pt, conference]{ieeeconf}
+\documentclass[11pt, twocolumn]{article}
 
@@
 \usepackage{hyperref} % JS: Remove this if you cannot compile.
+\usepackage{multirow}
 
@@
 
-\IEEEoverridecommandlockouts
-\overrideIEEEmargins
-
 % correct bad hyphenation here
@@
 
-\title{UGAN: Improving Underwater Image Quality using Generative Adversarial Networks}
+\title{Enhancing Underwater Imagery using Generative Adversarial Networks}
 \author{Cameron Fabbri$^{1}$, Md Jahidul Islam$^{2}$, and Junaed Sattar$^{3}$
 \thanks{				
-  The authors are with the Department of Computer Science and Engineering, University of Minnesota-Twin  Cities, MN 55455, USA. \newline
+  The authors are with the Department of Computer Science and Engineering, University of Minnesota-Twin  Cities, MN 55455, USA,
+  and the $^{1}$Air Force Research Laboratory, Rome, NY \newline
  {\tt\small\{$^{1}$fabbr013, $^{2}$islam034, $^{3}$junaed\}@umn.edu}
+ {\tt\small$^{1}$cameron.fabbri@us.af.mil}
 }
 }
-
-% \author{\IEEEauthorblockN{Cameron Fabbri$^{1}$}
-% \IEEEauthorblockA{Information Directorate\\
-% Air Force Research Laboratory \\
-% Rome, NY, USA.\\
-% cameron.fabbri@us.af.mil}
-% \and
-% \IEEEauthorblockN{Md Jahidul Islam \& Junaed Sattar}
-% \IEEEauthorblockA{Department of Computer Science and Engineering\\University of Minnesota- Twin Cities, MN, USA.\\
-% \{islam034, junaed\}@umn.edu }
-% \and
-% \IEEEauthorblockN{Junaed Sattar}
-% \IEEEauthorblockA{Department of Computer Science and Engineering\\University of Minnesota- Twin Cities,MN, USA.\\
-% junaed@umn.edu
-%}
 
@@
 \input{tex/abstract}
-\input{tex/introduction}
+\input{tex_plain_version/introduction}
 \input{tex/related}
-\input{tex/methodology.tex}
-\input{tex/experiments}
+\input{tex_plain_version/methodology.tex}
+\input{tex_plain_version/experiments}
 \input{tex/conclusions}
@@
 \bibliography{cambibs}
-\bibliographystyle{ieeetr}
+\bibliographystyle{plain}
 

### 2017-09-28 files/paper/_compile.sh

@@ -3,3 +3,11 @@ pdflatex paper
 bibtex paper
 bibtex paper
 pdflatex paper
+
+# arxiv version
+rm PlainPaper.aux PlainPaper.b* PlainPaper.log PlainPaper.pdf
+pdflatex PlainPaper
+bibtex PlainPaper
+bibtex PlainPaper
+pdflatex PlainPaper
+

### 2017-09-28 files/paper/PlainPaper.tex
update

@@
   and the $^{1}$Air Force Research Laboratory, Rome, NY \newline
- {\tt\small\{$^{1}$fabbr013, $^{2}$islam034, $^{3}$junaed\}@umn.edu}
- {\tt\small$^{1}$cameron.fabbri@us.af.mil}
+ {\tt\small\{$^{1}$cameron.fabbri@us.af.mil\}} \newline
+ %, fabbr013@umn.edu\}} \newline
+ {\tt\small\{$^{1}$fabbr013,$^{2}$islam034, $^{3}$junaed\}@umn.edu}
 }
@@
 \begin{document}
+%\twocolumn[{%
+%\renewcommand\twocolumn[1][]{#1}%
+%\maketitle
+%\begin{center}
+%    \centering
+%    \includegraphics[width=5in]{V8PYG3g}
+%\end{center}%
+%}]
+
 \maketitle

### 2017-10-25 files/paper/PlainPaper.tex
removed air force tag

@@
 \thanks{				
-  The authors are with the Department of Computer Science and Engineering, University of Minnesota-Twin  Cities, MN 55455, USA,
-  and the $^{1}$Air Force Research Laboratory, Rome, NY \newline
- {\tt\small\{$^{1}$cameron.fabbri@us.af.mil\}} \newline
+  The authors are with the Department of Computer Science and Engineering, University of Minnesota-Twin  Cities, MN 55455, USA.
+  %and the $^{1}$Air Force Research Laboratory, Rome, NY \newline
+ %{\tt\small\{$^{1}$cameron.fabbri@us.af.mil\}} \newline
  %, fabbr013@umn.edu\}} \newline

### 2017-11-03 files/paper/PlainPaper.tex
paper changes

@@
 \begin{document}
-%\twocolumn[{%
-%\renewcommand\twocolumn[1][]{#1}%
 %\maketitle
-%\begin{center}
-%    \centering
-%    \includegraphics[width=5in]{V8PYG3g}
-%\end{center}%
-%}]
 
+\twocolumn[
+\begin{@twocolumnfalse}
 	\maketitle
+	\begin{abstract}
+Autonomous underwater vehicles (AUVs) rely on a variety of sensors -- acoustic, inertial and visual -- for intelligent decision 
+making. Due to its non-intrusive, passive nature, and high information content, vision is an attractive sensing modality, 
+particularly at shallower depths. However, factors such as light refraction and absorption, suspended particles in the water, and 
+color distortion affect the quality of visual data, resulting in noisy and distorted images. AUVs that rely on visual sensing thus 
+face difficult challenges, and consequently exhibit poor performance on vision-driven tasks. This paper proposes a method to 
+improve the quality of visual underwater scenes using Generative Adversarial Networks (GANs), with the goal of improving input to 
+vision-driven behaviors further down the autonomy pipeline. Furthermore, we show how recently proposed methods are able to 
+generate a dataset for the purpose of such underwater image restoration. For any visually-guided underwater robots, this 
+improvement can result in increased safety and reliability through robust visual perception. To that effect, we present 
+quantitative and qualitative data which demonstrates that images corrected through the proposed approach generate more visually 
+appealing images, and also provide increased accuracy for a diver tracking algorithm.
+	\end{abstract}
+\end{@twocolumnfalse}
+]
 
-\input{tex/abstract}
+%\input{tex/abstract}
 \input{tex_plain_version/introduction}
